---
title: "CBPD Functional Network Results"
author: "Ursula Tooley"
date: "12/3/2020"
output:
  html_document:
    theme: united
    toc: yes
    toc_depth: 6
  pdf_document:
    toc: yes
    toc_depth: '6'
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(stats)
library(parallel)
library(lm.beta)
library(packrat)
library(summarytools)
library(visreg)
library(mgcv)
library(RLRsim)
library(GGally)
#load the .RDS file
pipeline='nogsr_spkreg_fd0.5dvars1.75_drpvls'
pipeline="nogsr_spkreg_fd1.25dvars2_drpvls"
pipeline='gsr_spkreg_fd0.5dvars1.75_drpvls'
network_dir=paste0("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/",pipeline)

load(paste0(network_dir,"/CBPD_n92_schaefer400_allruns.Rdata"))
```
## Data Descriptives

###Motion

We start with n= `r length(unique(main$ID))`. In these analyses, I used a stringent pipeline, censoring and interpolating over vols with > FD of 0.5 mm or DVARS > 1.75. Those are excluded from the timeseries used to calculate the networks used here. I excluded anyone with > 50% frames censored (following Yeo, 2011) or mean motion > 1 mm, or max motion over 10 mm, leaving us with `r length(unique(main_filt$ID))` participants, `r length(main_filt$run[main_filt$run=="run-02"])` of which have a second run. 

The dataframe below shows all runs for subjects who meet this criteria. At the moment, I'm just examining the first run, not averaging in those who have a second run.

```{r Filtered Motion Summary,echo=FALSE}
motion <- select(main_filt, age_scan, run, fd_mean,pctSpikesFD:relMaxRMSMotion)
print(dfSummary(motion), method = 'render')
```

###SES
```{r SES of Sample Summary,echo=FALSE, results='hold'}
ses <- select(main_unique, male, race2,ethnicity,has_diagnoses, parent1_edu:parent2_edu, income_median:monthslive_iflostincome, childaces_sum_ignorenan) %>% 
print(dfSummary(ses), method = 'render')
```

## Age and measures of network segregation

We find that overall, all measures of network segregation significantly increase with age in our dataset, with remarkable consistency. We examined within-network connectivity, between network connectivity, system segregation (as calculated in Chan et al. 2018), the modul_avgarity quality index, and the participation coefficient (summed across negative and positive weights). 

We controlled for sex, mean framewise displacement across both scans weighted by length of scan, the number of total volumes a participant had, and the average weight of the functional network across both scans (weighted by amount of good data per scan). We previously also controlled for the percent of volumes censored for FD spikes in the data, but Allyson suggested taking out 4.4.21.

```{r models of segregation, echo=FALSE, include=FALSE, results='hide'}
#look at mean within and between with age
#lm_within_sys_age <- lm(mean_within_sys~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet, data=main_unique)
lm_within_sys_age <- lm(mean_within_sys~age_scan+male+fd_mean_avg+avgweight+totalSizet, data=main_unique)
summary(lm_within_sys_age)
lm_between_sys_age <- lm(mean_between_sys~age_scan+male+fd_mean_avg+avgweight+totalSizet, data=main_unique)
summary(lm_between_sys_age)
lm_segreg_age<- lm(system_segreg~age_scan+male+fd_mean_avg+avgweight+totalSizet, data=main_unique)
summary(lm_segreg_age)
lm_modul_avg_age <- lm(modul_avg~age_scan+male+fd_mean_avg+avgweight+totalSizet, data=main_unique)
summary(lm_modul_avg_age)
lm_part_coef_age <- lm(part_coef~age_scan+male+fd_mean_avg+avgweight+totalSizet, data=main_unique)
summary(lm_part_coef_age)
lm_clust_co_age <- lm(avgclustco_both~age_scan+male+fd_mean_avg+avgweight+totalSizet, data=main_unique)
summary(lm_clust_co_age)
lm_num_comms_age <- lm(num_comms_modul_avg~age_scan+male+fd_mean_avg+avgweight+totalSizet, data=main_unique)
summary(lm_num_comms_age)

```

```{r plots of segregation, echo=FALSE, include=TRUE, results='hide'}
par(mfrow=c(2,3))
visreg(lm_between_sys_age,"age_scan", main="Mean between-system connectivity", ylab="", xlab="Age at scan (years)")
visreg(lm_within_sys_age,"age_scan", main= "Mean within-system connectivity", ylab="", xlab="Age at scan (years)")
visreg(lm_segreg_age,"age_scan", main="System segregation", ylab="", xlab="Age at scan (years)")
visreg(lm_modul_avg_age,"age_scan", main="Modularity quality index (Q)", ylab="", xlab="Age at scan (years)")
visreg(lm_part_coef_age,"age_scan", main="Average participation coefficient", ylab="", xlab="Age at scan (years)")
visreg(lm_clust_co_age,"age_scan", main="Average clustering coefficient", ylab="", xlab="Age at scan (years)")
visreg(lm_num_comms_age,"age_scan")
```

The number of communities detected using modul_avgarity maximization on this data does not significantly decrease with age (each subject ran 100x, averaged Q and *k*, range in k is `r range(main_unique$num_comms_modul_avg)`).

###Non-linear effects of age?

We also used restricted least ratio tests to test for the presence of non-linearity in our data. As you can see in the plots below, which use GAMs, most measures are linear and look no different from the linear models above.
```{r gam models of segregation, echo=FALSE, include=FALSE, results='hide'}
#look at mean within and between with age
gam_within_sys_age <- gam(mean_within_sys~s(age_scan)+male+fd_mean_avg+avgweight+totalSizet, data=main_unique)
model<- gamm(mean_within_sys~s(age_scan)+male+fd_mean+avgweight+size_t, data=main_unique, method = "REML")$lme
exactRLRT(model)
gam_between_sys_age <- gam(mean_between_sys~s(age_scan)+male+fd_mean+avgweight+size_t, data=main_unique)
model<- gamm(mean_between_sys~s(age_scan)+male+fd_mean+avgweight+size_t, data=main_unique)$lme
exactRLRT(model)
gam_segreg_age<- gam(system_segreg~s(age_scan)+male+fd_mean+avgweight+size_t, data=main_unique)
model<- gamm(system_segreg~s(age_scan)+male+fd_mean+avgweight+size_t, data=main_unique)$lme
exactRLRT(model)
gam_modul_avg_age <- gam(modul_avg~s(age_scan)+male+fd_mean+avgweight+size_t, data=main_unique)
model<- gamm(modul_avg~s(age_scan)+male+fd_mean+avgweight+size_t, data=main_unique)$lme
exactRLRT(model)
gam_part_coef_age <- gam(part_coef~s(age_scan)+male+fd_mean+avgweight+size_t, data=main_unique)
model<- gamm(part_coef~s(age_scan)+male+fd_mean+avgweight+size_t, data=main_unique)$lme
exactRLRT(model)
gam_clustco_age <- gam(avgclustco_both~s(age_scan)+male+fd_mean+avgweight+size_t, data=main_unique)
model<- gamm(part_coef~s(age_scan)+male+fd_mean+avgweight+size_t, data=main_unique)$lme
exactRLRT(model)
```

```{r gam plots of segregation, echo=FALSE, include=TRUE, results='hide'}
par(mfrow=c(2,3))
visreg(gam_between_sys_age,"age_scan",main=names(model.frame(gam_between_sys_age))[1])
visreg(gam_within_sys_age,"age_scan", main=names(model.frame(gam_within_sys_age))[1])
visreg(gam_segreg_age,"age_scan",  main=names(model.frame(gam_segreg_age))[1])
visreg(gam_modul_avg_age,"age_scan", main=names(model.frame(gam_modul_avg_age))[1])
visreg(gam_part_coef_age,"age_scan", main=names(model.frame(gam_part_coef_age))[1])
```

Tests of non-linearity confirmed that no non-linear effects are present. The wiggly participation coefficient line is just over-fitting.

## Which systems are driving this effect?

We fit the same model, controlling for sex, mean framewise displacement, the number of volumes a participant had, and the average weight of the functional network, to between- and within-system connectivity for each of the Yeo 7 systems. 

We find the strongest effects are in the default mode system, between default and attentional networks.
```{r lm plots, echo=FALSE, include=TRUE, results='hide',fig.show='hold', out.width='33.33%', fig.align='default'}
networks_age_pvals_fdr #FDR-corrected
main_unique_high <- main_unique %>% filter(ses_composite>0)
main_unique_low <- main_unique %>% filter(ses_composite<0)
lm_sys1to3_low<- lm(sys4to7~age_scan+male+fd_mean_avg+avgweight+totalSizet+ses_composite, data=main_unique_low)
lm_sys1to3_high<- lm(sys4to7~age_scan+male+fd_mean_avg+avgweight+totalSizet+ses_composite, data=main_unique_high)
lm_sys1to3<- lm(sys4to7~age_scan+male+fd_mean_avg+avgweight+totalSizet+age_scan*ses_composite, data=main_unique)
lm_sys3to7<- lm(sys3to7~age_scan+male+fd_mean_avg+avgweight+totalSizet+ses_composite, data=main_unique)
lm_sys4to7<- lm(sys4to7~age_scan+male+fd_mean_avg+avgweight+totalSizet+ses_composite, data=main_unique)
visreg(lm_sys1to3_low, "age_scan")
visreg(lm_sys1to3_high, "age_scan")

summary(lm_sys1to3);visreg(lm_sys1to3,"age_scan", by = "ses_composite", breaks=2)
summary(lm_sys3to7);visreg(lm_sys3to7,"age_scan", by = "ses_composite", overlay=T, breaks=2)
summary(lm_sys4to7);visreg(lm_sys4to7)

# ############## investigating plotting options #############
# crPlots(lm_sys4to7, "age_scan")
# plot(main_unique$age_scan, (lm_sys4to7$fitted.values))
# 
# library(car)
#avPlots(lm_sys4to7, "age_scan")
# sys4to7<- ((rstandard(lm(sys4to7~male+fd_mean+avgweight+pctSpikesFD+size_t, data=main_unique)))*rmse(lm_sys4to7, main_unique))+ mean(main_unique$sys4to7)
# age <- ((rstandard(lm(age_scan~male+fd_mean+avgweight+pctSpikesFD+size_t, data=main_unique)))*rmse(lm_sys4to7, main_unique)) + mean(main_unique$age_scan)
# xxx <- data.frame(sys4to7,age)
# l <- lm(sys4to7~age, data=xxx)
# visreg(l)
# plot(xxx$sys4to7~xxx$age)
# plot(lm_sys)
visreg(lm_sys1to3,"age_scan",main="VIS to DAN", ylab="", xlab="Age at scan (years)")
visreg(lm_sys3to7,"age_scan", main="DMN to DAN",ylab="", xlab="Age at scan (years)")
visreg(lm_sys4to7,"age_scan",  main="DMN to VAN",ylab="", xlab="Age at scan (years)")
# 
# crPlots(lm_sys4to7)
# visreg(lm_sys4to7,"age_scan",band=FALSE, gg=TRUE)+geom_smooth()+theme_classic()
```

### Plots for within-system connectivity
To scatter around the Yeo networks.
```{r lm plots within, echo=FALSE, include=TRUE, results='hide',fig.show='hold', out.width='33.33%', fig.align='default'}
networks <- dplyr::select(main_unique, sys1to1, sys2to2, sys3to3, sys4to4, sys5to5, sys6to6,sys7to7) %>% ungroup()
nets <- colnames(networks[-1])
#look at non-linear interaction between age and envSES 
for (net in nets){
  name<-paste0("lm_",net)
  formula<-formula(paste0(net, '~age_scan+male+fd_mean+avgweight+totalSizet'))
  assign(name, lm(formula, data=main_unique))
  #p_val[net] <- summary(name)$coefficients[2,4]
  summary(get(name))
  visreg(get(name),'age_scan', xlab = "Age (years)", ylab="")
} 
```

## System-level effects to creativity

Allyson asks whether the segregation of def vs. attn nets is associated with reduced pretend play, reduced (CFG-), or coded pretend play in PCIT.

```{r lm plots, echo=FALSE, include=TRUE, results='hide',fig.show='hold', out.width='33.33%', fig.align='default'}
networks_age_pvals_fdr #FDR-corrected

#Home literacy and numeracy questionnaire
lm_sys3to7<- lm(sys1to3~age_scan+male+fd_mean_avg+avgweight+totalSizet+litnum_freq_play_avg, data=main_unique)
lm_sys4to7<- lm(sys4to7~age_scan+male+fd_mean_avg+avgweight+totalSizet+litnum_freq_play_avg+ses_composite, data=main_unique)
summary(lm(litnum_freq_play_avg~age_behav.x+male+ses_composite, data=main_unique));visreg(lm(litnum_freq_play_avg~age_behav.x+male+ses_composite, data=main_unique))
summary(lm_sys3to7)
summary(lm_sys4to7)
visreg(lm_sys3to7)
visreg(lm_sys4to7)
       "litnum_freq_play_avg", main="DMN to VAN",ylab="", xlab="litnum_freq_play_avg")

#CFG measures
cfg_measures=main_unique %>% select(total.play.time:max.Δt...min.) %>% names();cfg_measures=cfg_measures[-1] #- baseID
cfg_measures
for (measure in cfg_measures){
  meas=main_unique %>% ungroup %>% select(measure) %>% pull()
  print(meas)
  hist(as.numeric(meas), main=measure)
  print(summary(meas))
}

#unique shapes
#u_united
#Home literacy and numeracy questionnaire
library()
lm_sys3to7<- rlm(unique.shapes~age_scan+male+fd_mean_avg+avgweight+totalSizet+sys4to7, data=main_unique)
lm_sys3to7<- lm(sys3to7~age_scan+male+fd_mean_avg+avgweight+totalSizet+U_united, data=main_unique)
summary(lm_sys3to7)
visreg(lm_sys3to7)
lm_sys3to7<- lm(sys4to7~age_scan+male+fd_mean_avg+avgweight+totalSizet+U__united, data=main_unique)
summary(lm_sys3to7)
visreg(lm_sys3to7)

lm_sys4to7<- lm(sys4to7~age_scan+male+fd_mean_avg+avgweight+totalSizet+u_united, data=main_unique)
summary(lm(litnum_freq_play_avg~age_scan+male, data=main_unique))
summary(lm_sys4to7)

#Julia re: PCIT coded pretend play, or start from child_persistence_seconds
#duration vs. instances
pcit_measures=main_unique %>%ungroup %>% select(kid_a_play_coder1:totalDuration.adult_p_play_avg) %>% names();
pcit_measures
for (measure in pcit_measures){
  meas=main_unique %>% ungroup %>% select(measure) %>% pull()
  print(meas)
  hist(as.numeric(meas), main=measure)
  print(summary(meas))
}

#Coded play during PCIT
summary(lm(kid_p_play_coder1~litnum_freq_play_avg+totalDuration.kid_p_play_avg, data=main_unique_play))
visreg(lm(kid_p_play_coder1~litnum_freq_play_avg+totalDuration.kid_p_play_avg, data=main_unique_play))
main_unique_play <- main_unique %>% filter(kid_p_play_coder1 <8)
#outlier over 8
lm_sys1to3<- lm(sys1to3~age_scan+male+fd_mean_avg+avgweight+totalSizet+kid_p_play_coder1+totalDuration.kid_p_play_avg, data=main_unique)
lm_sys3to7<- lm(sys3to7~age_scan+male+fd_mean_avg+avgweight+totalSizet+kid_p_play_coder1+totalDuration.kid_p_play_avg, data=main_unique)
lm_sys4to7<- lm(sys4to7~age_scan+male+fd_mean_avg+avgweight+totalSizet+kid_p_play_coder1+totalDuration.kid_p_play_avg, data=main_unique)
summary(lm(litnum_freq_play_avg~age_behav.x+male+ses_composite, data=main_unique));visreg(lm(litnum_freq_play_avg~age_behav.x+male+ses_composite, data=main_unique))
summary(lm_sys1to3)
summary(lm_sys3to7)
summary(lm_sys4to7)
visreg(lm_sys1to3)
visreg(lm_sys4to7)

#Question-asking 
qa <- read.csv("~/Box/Mackey_Lab/CBPD (825656)/Data/PCIT_Questionasking_Ursula/question_asking_three_coders_parent_qs_and_longitudinal_082020.csv", skip = 1) %>% rename(.,ID=record_id) %>% mutate(.,ID=paste0("sub-", ID))
main_qa <- left_join(main_unique,qa,by="ID")
main_qa$Total_q_kid_allpcit_average #only n=55

# crPlots(lm_sys4to7)
# visreg(lm_sys4to7,"age_scan",band=FALSE, gg=TRUE)+geom_smooth()+theme_classic()

#bootstrap or rlm these effects to make sure?
```

## VIS-DAN system-level effects to verbal


```{r lm plots, echo=FALSE, include=TRUE, results='hide',fig.show='hold', out.width='33.33%', fig.align='default'}
networks_age_pvals_fdr #FDR-corrected

main_unique$litnum_bed_read_freq
main_unique$wasi_vocab_raw
str(main_unique$wj_letterword_correct)
#WJ letterword age-regressed
main_unique$resid <- resid(lm(wj_letterword_correct~age_behav.x, data=main_unique, na.action=na.exclude))
lm_sys1to3<- lm(sys1to3~age_scan+male+fd_mean_avg+avgweight+totalSizet+resid, data=main_unique)
summary(lm_sys1to3)
visreg(lm_sys1to3)

lm_sys1to3<- lm(sys1to3~age_scan+male+fd_mean_avg+avgweight+totalSizet+wj_letterword_correct, data=main_unique)
summary(lm_sys1to3)
visreg(lm_sys1to3)

#WPPSI-WISC Info/Vocab--verbal comprehension
main_unique$info_vocab_both <- ifelse(is.na(main_unique$wppsi_info_scaled), ifelse(main_unique$wisc_vocab_valid==1, main_unique$wisc_vocab_scaled,NA),main_unique$wppsi_info_scaled) 
main_unique$info_vocab_raw <- ifelse(is.na(main_unique$wppsi_info_scaled), ifelse(main_unique$wisc_vocab_valid==1, main_unique$wisc_vocab_raw,NA),main_unique$wppsi_info_raw) 

main_unique$wppsi_info_valid;main_unique$wisc_vocab_valid
lm_sys1to3<- lm(info_vocab_both~age_scan+male+fd_mean_avg+avgweight+totalSizet+sys1to3+ses_composite, data=main_unique)
summary(lm_sys1to3)
visreg(lm_sys1to3,"sys1to3",main= "Information / Vocabulary \n (scaled score)",ylab="", xlab="VIS to DA connectivity")
lm_sys1to3<- lm(info_vocab_both~age_scan+male+fd_mean_avg+avgweight+totalSizet+sys1to3+ses_composite, data=main_unique)
summary(lm_sys1to3)

```

## All 3 systems to reasoning
- Add other measures of visuo-spatial integration to all 3 sets of networks
- Test reasoning (picture concepts and matrix reasoning) and working memory (picture memory, though Allyson says she's less confident about the wppsi/wisc combo there)
```{r lm plots, echo=FALSE, include=TRUE, results='hide',fig.show='hold', out.width='33.33%', fig.align='default'}
#Test all 3 systems with Info/Vocab
main_unique$wppsi_info_valid;main_unique$wisc_vocab_valid
lm_sys1to3<- lm(sys1to3~age_scan+male+fd_mean_avg+avgweight+totalSizet+info_vocab_both+ses_composite, data=main_unique)
lm_sys3to7<- lm(sys3to7~age_scan+male+fd_mean_avg+avgweight+totalSizet+info_vocab_both+ses_composite, data=main_unique)
lm_sys4to7<- lm(sys4to7~age_scan+male+fd_mean_avg+avgweight+totalSizet+info_vocab_both+ses_composite, data=main_unique)
summary(lm_sys1to3)
summary(lm_sys3to7)
summary(lm_sys4to7)
visreg(lm_sys3to7)
visreg(lm_sys1to3,"sys1to3",main= "Information / Vocabulary \n (scaled score)",ylab="", xlab="VIS to DA connectivity")

#Test all 3 systems with Reasoning-Picture Concepts & Matrix Reasoning
#Matrix Reasoning
n92_parcel_CT_data$matrix_reasoning_both <- ifelse(is.na(main_unique$wppsi_matrix_valid),main_unique$wisc_matrix_scaled,ifelse(main_unique$wppsi_matrix_valid==0,NA,main_unique$wppsi_matrix_scaled))
main_unique$matrix_reasoning_both_raw <- ifelse(is.na(main_unique$wppsi_matrix_valid),main_unique$wisc_matrix_raw,ifelse(main_unique$wppsi_matrix_valid==0,NA,main_unique$wppsi_matrix_raw))
main_unique$matrix_reasoning_both;main_unique$matrix_reasoning_both_raw
#Plot raw score
mr <- lm(matrix_reasoning_both~age_behav.x+male+ses_composite, data=main_unique)
summary(mr)
visreg(mr, "age_behav.x", main="Matrix Reasoning (raw)")
lm.beta(mr)
mr <- lm(wisc_matrix_raw~age_behav.x+male, data=main_unique)
summary(mr)
visreg(mr,"age_behav.x", main="Matrix Reasoning (raw), WISC")
lm.beta(mr)
mr <- lm(wppsi_matrix_raw~age_behav.x+male, data=main_unique)
summary(mr)
visreg(mr,"age_behav.x", main="Matrix Reasoning (raw)", ylab="Raw score", xlab="Age (years)")
lm.beta(mr)

matrix_reasoning_both_raw
main_unique$wppsi_matrix_valid;main_unique$wisc_matrix_valid
lm_sys1to3<- lm(matrix_reasoning_both~age_scan+male+fd_mean_avg+avgweight+totalSizet+sys1to3+as.factor(wppsi_admin)+ses_composite, data=main_unique)
lm_sys3to7<- lm(matrix_reasoning_both~age_scan+male+fd_mean_avg+avgweight+totalSizet+sys3to7+as.factor(wppsi_admin), data=main_unique)
lm_sys4to7<- lm(matrix_reasoning_both~age_scan+male+fd_mean_avg+avgweight+totalSizet+sys4to7+ses_composite, data=main_unique)
summary(lm_sys1to3)
summary(lm_sys3to7)
summary(lm_sys4to7)
visreg(lm_sys1to3, "sys1to3", main= "Matrix Reasoning (scaled score)", ylab="Scaled score", xlab="VIS to DA connectivity")
visreg(lm_sys3to7, "sys3to7", main= "Matrix Reasoning (scaled score)", ylab="Scaled score", xlab="DM to DA connectivity")
visreg(lm_sys4to7)

#main_unique$wppsi_picconc_raw;main_unique$wisc_picconcept_scaled

#Test all 3 systems with Working Memory-picture memory?
main_unique$working_mem_both <- ifelse(is.na(main_unique$wppsi_picmem_valid),main_unique$wisc_digit_scaled,ifelse(main_unique$wppsi_picmem_valid==0, NA, main_unique$wppsi_picmem_scaled))
main_unique$working_mem_raw <- ifelse(is.na(main_unique$wppsi_picmem_valid),main_unique$wisc_digit_raw,ifelse(main_unique$wppsi_picmem_valid==0, NA, main_unique$wppsi_picmem_raw))
main_unique$wisc_digit_scaled
main_unique$wppsi_picmem_scaled
main_unique$wisc_digit_scaled
main_unique$wisc_digit_valid;main_unique$wppsi_picmem_valid

lm_sys1to3<- lm(working_mem_both~age_scan+male+fd_mean_avg+avgweight+totalSizet+as.factor(wppsi_admin)+sys1to3+ses_composite, data=main_unique)
lm_sys3to7<- lm(working_mem_both~age_scan+male+fd_mean_avg+avgweight+totalSizet+as.factor(wppsi_admin)+sys3to7+ses_composite, data=main_unique)
lm_sys4to7<- lm(working_mem_both~age_scan+male+fd_mean_avg+avgweight+totalSizet+as.factor(wppsi_admin)+sys4to7+ses_composite, data=main_unique)
summary(lm_sys1to3)
summary(lm_sys3to7)
summary(lm_sys4to7)
visreg(lm_sys1to3, "sys1to3", main="Working Memory (scaled score)")

#Correct across
covariates="matrix_reasoning_both~ age_scan+male+fd_mean_avg+avgweight+totalSizet+"
#make a dataframe with no repeats of net comparisons
nets <- dplyr::select(main_unique, sys1to3,sys3to7,sys4to7) %>% ungroup %>% names();nets <- nets[-1]
#run and compare for multiple comparisons again
m <- mclapply(nets, function(sys) {as.formula(paste(covariates, sys,sep=""))},mc.cores=2)
networks_ses_pvals <- mclapply(m, function(sys) { summary(lm(formula = sys,data=main_unique))$coefficients[7,4]},mc.cores=1)
networks_ses_pvals <- as.data.frame(networks_ses_pvals)
networks_ses_pvals <- t(networks_ses_pvals)
networks_ses_pvals <- as.data.frame(networks_ses_pvals)
covariates="working_mem_both~ age_scan+male+fd_mean_avg+avgweight+totalSizet+"
m <- mclapply(nets, function(sys) {as.formula(paste(covariates, sys,sep=""))},mc.cores=2)
networks_ses_pvals_2 <- mclapply(m, function(sys) { summary(lm(formula = sys,data=main_unique))$coefficients[7,4]},mc.cores=1)
pvals <- data.frame(unlist(c(networks_ses_pvals$V1,networks_ses_pvals_2)))
#bonferroni correct
networks_ses_pvals_fdr <- p.adjust(pvals$unlist.c.networks_ses_pvals.V1..networks_ses_pvals_2.., method="fdr")
networks_ses_pvals_fdr <- data.frame(networks_ses_pvals_fdr,rep(nets,2))
colnames(networks_ses_pvals_fdr) <- c("pvalue", "network")
networks_ses_pvals_fdr #Corrected for 6 tests!

```

# VIS-DA reasoning and working memory to average subject CT

L hemi clusters 1=V1, cluster 2=lingual/below pericalcarine, 3=posterior parietal
R hemi clusters 1=V1/pericalcarine area, 2= lateral occipital 3=superior frontal
```{r VIS-DA to CT, echo=FALSE, include=TRUE, results='hide',fig.show='hold', out.width='33.33%', fig.align='default'}
lh <- read.table("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/lh_thickness_agesext1rating_n89/lh-Avg-thickness-age_scan-Cor/cache.th23.abs.y.ocn.dat")
rh <- read.table("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/rh_thickness_agesext1rating_n89/rh-Avg-thickness-age_scan-Cor/cache.th23.abs.y.ocn.dat")
subs <- read.table("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/qdec.agesext1rating.n89.table.dat", header = T) %>% select(fsid)
avg_age_parcel_ct <- cbind(subs,lh,rh);colnames(avg_age_parcel_ct) <- c("ID", "Lcluster1","Lcluster2","Lcluster3","Rcluster1","Rcluster2","Rcluster3")
avg_age_parcel_ct <- avg_age_parcel_ct %>% mutate(avgct_med_vis_clust=(Lcluster1+Rcluster1)/2, avgct_total_vis_clust=(Lcluster1+Lcluster2+Lcluster3+Rcluster1+Rcluster2)/5)
main_unique <- left_join(main_unique,avg_age_parcel_ct, by="ID")

#Matrix Reasoning
main_unique$matrix_reasoning_both <- ifelse(is.na(main_unique$wppsi_matrix_valid),main_unique$wisc_matrix_scaled,ifelse(main_unique$wppsi_matrix_valid==0,NA,main_unique$wppsi_matrix_scaled))
main_unique$matrix_reasoning_both_raw <- ifelse(is.na(main_unique$wppsi_matrix_valid),main_unique$wisc_matrix_raw,ifelse(main_unique$wppsi_matrix_valid==0,NA,main_unique$wppsi_matrix_raw))
main_unique$matrix_reasoning_both;main_unique$matrix_reasoning_both_raw

main_unique$wppsi_matrix_valid;main_unique$wisc_matrix_valid
lm_sys1to3<- lm(sys1to3~age_scan+male+fd_mean_avg+avgweight+totalSizet+avgct_total_vis_clust, data=main_unique)
summary(lm_sys1to3) #Matrix reasoning scaled score is not related to avgCT within the age-significant visual clusters

visreg(lm_sys1to3, "avgct_total_vis_clust", main= "VIS-DA Connectivity", ylab="Scaled score", xlab="VIS age cluster CT")

#Test CT with Working Memory
main_unique$working_mem_both <- ifelse(is.na(main_unique$wppsi_picmem_valid),main_unique$wisc_digit_scaled,ifelse(main_unique$wppsi_picmem_valid==0, NA, main_unique$wppsi_picmem_scaled))

lm_sys1to3<- lm(sys1to3~age_scan+male+fd_mean_avg+avgweight+totalSizet+Lcluster2, data=main_unique)
summary(lm_sys1to3) #Matrix reasoning scaled score is not related to avgCT within the age-significant visual clusters
```

### CT within the Yeo7 Visual Mask

```{r VIS-DA to CT, echo=FALSE, include=TRUE, results='hide',fig.show='hold', out.width='33.33%', fig.align='default'}
#t1 data
lh <- read.delim("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/schaefer400_lh_thickness_stats.txt") %>% rename(.,ID=Measure.mean) %>% select(-Background.FreeSurfer_Defined_Medial_Wall);rh <- read.delim("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/schaefer400_rh_thickness_stats.txt") %>% rename(.,ID=Measure.mean) %>% select(-Background.FreeSurfer_Defined_Medial_Wall);
#t2
lh2 <- read.delim("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t2/schaefer400_lh_thickness_stats.txt") %>% rename(.,ID=Measure.mean) %>% select(-Background.FreeSurfer_Defined_Medial_Wall)%>% mutate(ID=paste0(ID,"2"));rh2 <- read.delim("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t2/schaefer400_rh_thickness_stats.txt") %>% rename(.,ID=Measure.mean) %>% select(-Background.FreeSurfer_Defined_Medial_Wall)%>% mutate(ID=paste0(ID,"2"));
#t2
lh3 <- read.delim("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t3/schaefer400_lh_thickness_stats.txt") %>% rename(.,ID=Measure.mean) %>% select(-Background.FreeSurfer_Defined_Medial_Wall)%>% mutate(ID=paste0(ID,"3"));rh3 <- read.delim("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t3/schaefer400_rh_thickness_stats.txt") %>% rename(.,ID=Measure.mean) %>% select(-Background.FreeSurfer_Defined_Medial_Wall)%>% mutate(ID=paste0(ID,"3"));
lh <- rbind(lh,lh2,lh3)
rh <- rbind(rh,rh2,rh3)
#meanCT
n92_parcel_CT_data <- left_join(main_unique,lh, by= "ID")
n92_parcel_CT_data <- left_join(n92_parcel_CT_data,rh, by= "ID")

names(n92_parcel_CT_data[,1661:2060])
n92_parcel_CT_data$mean_vis_CT_left <- n92_parcel_CT_data[,1661:2060] %>% select(contains("LH_Vis_")) %>% rowMeans()
n92_parcel_CT_data$mean_vis_CT_right <- n92_parcel_CT_data[,1661:2060] %>% select(contains("RH_Vis_")) %>% rowMeans()
n92_parcel_CT_data$mean_vis_CT<- n92_parcel_CT_data[,1661:2060] %>% select(contains("_Vis_")) %>% rowMeans()
#Matrix Reasoning
n92_parcel_CT_data$matrix_reasoning_both <- ifelse(is.na(n92_parcel_CT_data$wppsi_matrix_valid),n92_parcel_CT_data$wisc_matrix_scaled,ifelse(n92_parcel_CT_data$wppsi_matrix_valid==0,NA,n92_parcel_CT_data$wppsi_matrix_scaled))
n92_parcel_CT_data$matrix_reasoning_both_raw <- ifelse(is.na(n92_parcel_CT_data$wppsi_matrix_valid),n92_parcel_CT_data$wisc_matrix_raw,ifelse(n92_parcel_CT_data$wppsi_matrix_valid==0,NA,n92_parcel_CT_data$wppsi_matrix_raw))
n92_parcel_CT_data$matrix_reasoning_both;n92_parcel_CT_data$matrix_reasoning_both_raw

n92_parcel_CT_data$wppsi_matrix_valid;n92_parcel_CT_data$wisc_matrix_valid
lm_sys1to3<- lm(matrix_reasoning_both~male+mean_vis_CT+sys1to3+ses_composite, data=n92_parcel_CT_data)
summary(lm_sys1to3) #Matrix reasoning scaled score is not related to avgCT within the age-significant visual clusters
visreg(lm_sys1to3, "mean_vis_CT", main= "VIS community CT", ylab="MR Scaled score", xlab="VIS community CT")

#Test CT with Working Memory
n92_parcel_CT_data$working_mem_both <- ifelse(is.na(n92_parcel_CT_data$wppsi_picmem_valid),n92_parcel_CT_data$wisc_digit_scaled,ifelse(n92_parcel_CT_data$wppsi_picmem_valid==0, NA, n92_parcel_CT_data$wppsi_picmem_scaled))

lm_sys1to3<- lm(working_mem_both~age_scan+male+fd_mean_avg+avgweight+totalSizet+mean_vis_CT+sys1to3, data=n92_parcel_CT_data)
summary(lm_sys1to3) #Matrix reasoning scaled score is not related to avgCT within the age-significant visual clusters


#Do it with the age significant areas only
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/parcel_CT_age_n92.Rdata")
parcel_CT <- n92_parcel_CT_data[,1646:2045]
n92_parcel_CT_data$avg_age_sig_parcel_CT <- parcel_CT[,parcel_CT_pvals_fdr[,2]<0.05] %>% rowMeans()
 
lm_sys1to3<- lm(matrix_reasoning_both~male+t1_rating_avg+avg_age_sig_parcel_CT, data=n92_parcel_CT_data)
summary(lm_sys1to3) #Matrix reasoning scaled score is not related to avgCT within the age-significant visual clusters
visreg(lm_sys1to3, "mean_vis_CT", main= "VIS community CT", ylab="MR Scaled score", xlab="VIS community CT")

lm_sys1to3<- lm(working_mem_both~male+t1_rating_avg+avg_age_sig_parcel_CT, data=n92_parcel_CT_data)
summary(lm_sys1to3) #Matrix reasoning scaled score is not related to avgCT within the age-significant visual clusters
```
None of these showed significantly non-linear effects, either. 

```{r system level FDR-corrected effects}
# Look at each column and correct for multiple comparisons
covariates="~ age_scan+male+fd_mean_avg+avgweight+totalSizet"

#make a dataframe with no repeats of net comparisons
main_unique <- dplyr::select(main_unique, -c(sys2to1,sys3to1,sys3to2,sys4to1,sys4to2,sys4to3,sys5to1,sys5to2,sys5to3,sys5to4,sys6to1,sys6to2,sys6to3,sys6to4,sys6to5,sys7to1,sys7to2,sys7to3,sys7to4,sys7to5,sys7to6))
#run and compare for multiple comparisons again
m <- mclapply(names((dplyr::select(ungroup(main_unique),sys1to1:sys7to7))), function(sys) {as.formula(paste(sys, covariates, sep=""))},mc.cores=2)
networks_Age_pvals <- mclapply(m, function(sys) { summary(lm(formula = sys,data=main_unique))$coefficients[2,4]},mc.cores=1)
networks_Age_pvals <- as.data.frame(networks_Age_pvals)
networks_Age_pvals <- t(networks_Age_pvals)
networks_Age_pvals <- as.data.frame(networks_Age_pvals)
#bonferroni correct
networks_Age_pvals_fdr <- p.adjust(networks_Age_pvals$V1, method="fdr")
networks_age_pvals_fdr <- data.frame(networks_Age_pvals_fdr,names((dplyr::select(ungroup(main_unique),sys1to1:sys7to7))))
colnames(networks_age_pvals_fdr) <- c("pvalue", "network")
#FDR correction shows DMN to attentional networks and visual to dorsal attention is marginal.
print(networks_age_pvals_fdr)

```

Effects on default mode connectivity survive FDR correction across the tests conducted, with DMN-VAN *p_fdr*=`r networks_age_pvals_fdr$pvalue[networks_age_pvals_fdr$network=="sys3to7"]` and DMN-DAN *p_fdr*= `r networks_age_pvals_fdr$pvalue[networks_age_pvals_fdr$network=="sys4to7"]`. Vis-DAN *p_fdr*= `r networks_age_pvals_fdr$pvalue[networks_age_pvals_fdr$network=="sys1to3"]`.

## Longitudinal data

### Longitudinal data descriptives

We have `r sum(main_filt$longitudinal_visit_num==2)` 
```{r longitudinal descriptives}
#melt data
main_filt_long <- dplyr::select(main_filt, c(ID:record_id.y,date_scan, date_behav, age_scan,male,fd_mean_avg,avgweight,pctVolsCensored,totalSizet,race2,ethnicity, longitudinal_visit_num,base_ID, part_coef))
#need to filter out only the first datapoint from each timepoint, since the network data is repeated across multiple runs at each timepoint
#to see why -> main_filt %>% select(base_ID,longitudinal_visit_num,sys1to1)
main_long_only <- main_filt_long %>% group_by(base_ID, longitudinal_visit_num) %>% filter(row_number() == 1)
main_long_only %>% select(base_ID,longitudinal_visit_num,sys1to1) #now has one set of network stats from each timepoint for each subject
table(main_long_only$longitudinal_visit_num)

#get gaps between visits
main_long_only<- main_long_only %>% group_by(base_ID) %>% mutate(diffageT1toT2=nth(age_scan,2)-first(age_scan),
                                                diffageT2toT3=nth(age_scan,3)-nth(age_scan,2)) %>% ungroup()
#Summary in months
main_long_only %>% select(diffageT1toT2) %>%  summarise(.,min=min(diffageT1toT2*12, na.rm=T), max=max(diffageT1toT2*12, na.rm=T))
main_long_only %>% select(diffageT2toT3) %>%  summarise(.,min=min(diffageT2toT3*12, na.rm=T), max=max(diffageT2toT3*12, na.rm=T))
```

We have `r sum(main_long_only$longitudinal_visit_num==2)` T2 visits and `r sum(main_long_only$longitudinal_visit_num==3)` T3 visits.

```{r longitudinal global effects with age}
library(nlme)
library(lme4)
library(lmerTest) #this will provide p-values

measures=c("mean_within_sys","mean_between_sys", "system_segreg", "modul_avg", "part_coef", "avgclustco_both")
for (meas in measures){
  print(meas)
  name<-paste0("lm_", meas,"_age")
  formula<-formula(paste0(meas,'~scale(age_scan)+male+scale(fd_mean_avg)+scale(avgweight)+scale(totalSizet)+scale(pctVolsCensored)+(1|base_ID)'))
  assign(name, lmer(formula,data=main_long_only))
  print(summary(get(name)))
  print(get(name))
}
#within, between, system segreg and part coef are singular, use lm instead 
#clustco and modul are not singular
  
#Without the random effect for subject, for those models that don't converge, the fixed effects with lm are the same as those using lmer, Bart suggests using lm instead
lm_within_sys_age <- lm(mean_within_sys~age_scan+male+fd_mean+avgweight+pctVolsCensored+totalSizet, data=main_long_only)
summary(lm_within_sys_age) 
lm_within_sys_age

lm_between_sys_age <- lm(mean_between_sys~age_scan+male+fd_mean+avgweight+pctVolsCensored+totalSizet, data=main_long_only)
summary(lm_between_sys_age)
lm.beta(lm_between_sys_age)

lm_system_segreg_age <- lm(system_segreg~age_scan+male+fd_mean+avgweight+pctVolsCensored+totalSizet, data=main_long_only)
summary(lm_system_segreg_age)
lm.beta(lm_system_segreg_age)
```

### System-level effects
```{r longitudinal system-level effects with age}
lm_sys4to7_age <- lmer(sys4to7~scale(age_scan)+male+scale(fd_mean_avg)+scale(avgweight)+scale(totalSizet)+scale(pctVolsCensored)+(1|base_ID), data=main_long_only)
summary(lm_sys4to7_age)
lm_sys4to7_age 

#1to3 and 3to7 are singular, use lm
lm_sys1to3_age <- lm(sys1to3~age_scan+male+fd_mean+avgweight+pctVolsCensored+totalSizet, data=main_long_only)
summary(lm_sys1to3_age)
lm.beta(lm_sys1to3_age)

lm_sys3to7_age <- lm(sys3to7~age_scan+male+fd_mean+avgweight+pctVolsCensored+totalSizet, data=main_long_only)
summary(lm_sys3to7_age)
lm.beta(lm_sys3to7_age)
```

### Playing with plotting mixed effects
```{r plotting mixed effects}
#with sjplot
library(sjPlot)
plot_model(lm_within_sys_age,terms=c("age_scan"), type = "pred", pred.type = "re", show.data = T)

#Using ggplot to recreate 
fm2 <- lme(mean_within_sys~scale(age_scan)+male+scale(fd_mean_avg)+scale(avgweight)+scale(totalSizet)+scale(pctVolsCensored), data = main_long_only, random = ~ 1|base_ID)
summary(fm2)
fm2

fm2 <- lme(sys4to7~age_scan+male+fd_mean_avg+avgweight+totalSizet+pctVolsCensored, data = main_long_only, random = ~ 1|base_ID)

newdat <- expand.grid(male=unique(main_long_only$male),
                  age_scan=c(min(main_long_only$age_scan),
                            max(main_long_only$age_scan)),
                  fd_mean_avg=c(min(main_long_only$fd_mean_avg),
                                max(main_long_only$fd_mean_avg)),
                  avgweight=c(min(main_long_only$avgweight),
                                max(main_long_only$avgweight)),
                  totalSizet=c(min(main_long_only$totalSizet),
                                max(main_long_only$totalSizet)),
                  pctVolsCensored=c(min(main_long_only$pctVolsCensored),
                                max(main_long_only$pctVolsCensored)))
p <- ggplot(main_long_only, aes(x=age_scan, y=predict(fm2)))+
  geom_point(size=3) +
  geom_line(aes(y=predict(fm2), group=base_ID, size="Subjects")) +
  geom_line(data=newdat, aes(y=predict(fm2, level=0, newdata=newdat), size="Population")) +
  scale_size_manual(name="Predictions", values=c("Subjects"=0.5, "Population"=3)) +
  theme_bw(base_size=22)
p

tab_model(lm_within_sys_age)

#try bayesian approach?
stan_glmer

#plotting
library(lattice)
xyplot(mean_within_sys ~ age_scan | base_ID, main_long_only, aspect = "xy",
            type = c("g", "p", "r"), subset = )
       
       index.cond = function(x,y) coef(lm(y ~ x))[1])

#Using ggplot to plot the predicted datapoints (controlling)
lm_sys4to7_age <- lmer(sys4to7~age_scan+male+fd_mean+avgweight+pctVolsCensored+totalSizet+(1|base_ID), data=main_long_only)
main_long_only$pred_sys4to7 <- predict(lm_sys4to7_age)
ggplot(data=main_long_only, aes(x=age_scan, y=pred_sys4to7, group=factor(base_ID), colour="gray"), legend=FALSE) +
  geom_smooth(method=lm, se=F, fullrange=F, lty=1, size=.5, color="gray60") +
  geom_smooth(aes(group=1), method=lm, se=FALSE, fullrange=FALSE, lty=1, size=2, color="black") +
  geom_point(aes(x=age_scan,y=pred_sys4to7))+
  xlab("Age at Scan (years)") + ylab("Predicted time brushing (sec)") +
  theme_classic() +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5))
```

## Environment and Measures of Network Segregation

```{r recode race to use way Cassidy did in molar eruption paper-5-category}
main_unique$race_factor <- ifelse(main_unique$race_americanindian==1, "Multiracial_Other", ifelse(main_unique$race_asian == 1, "Asian", ifelse(main_unique$race_hawaiian==1,"Multiracial_Other", ifelse(main_unique$race_other==1, "Multiracial_Other",(ifelse(main_unique$race_black==1,  "AABlack", ifelse(main_unique$race_white==1, "White", ifelse(main_unique$race_americanindian+main_unique$race_asian+main_unique$race_black+main_unique$race_hawaiian+main_unique$race_white > 1,  "Multiracial_Other", NA))))))))
main_unique$race_factor[which(main_unique$ethnicity == "Hispanic or Latino")] <- "Hispanic"

main_replicate_unique$race_factor <- ifelse(main_replicate_unique$race_americanindian==1, "Multiracial_Other", ifelse(main_replicate_unique$race_asian == 1, "Asian", ifelse(main_replicate_unique$race_hawaiian==1,"Multiracial_Other", ifelse(main_replicate_unique$race_other==1, "Multiracial_Other",(ifelse(main_replicate_unique$race_black==1,  "AABlack", ifelse(main_replicate_unique$race_white==1, "White", ifelse(main_replicate_unique$race_americanindian+main_replicate_unique$race_asian+main_replicate_unique$race_black+main_replicate_unique$race_hawaiian+main_replicate_unique$race_white > 1,  "Multiracial_Other", NA))))))))
main_replicate_unique$race_factor[which(main_replicate_unique$ethnicity == "Hispanic or Latino")] <- "Hispanic"
```

Race: There are small significant effects of race on within- and between-system connectivity such that white and Asian kids tend to have higher within and lower between system connectivity than Black kids.

SES: No significant effects of SES (median income, ses composite of income and parental education, or parent1 education) on measures of segregation (controlling for race or not).

ACES sum: No significant effects of ACES sum on measures of segregation. However, didn't examine 3-category ACES.

For future reference, the estimates and p-values for other covariates (excluding the intercept) don't change based on the reference level of a factor (re: Allyson's concerns in Black vs. White ref category).

```{r models of segregation with ses, echo=FALSE, include=FALSE, results='hide'}
lm_within_sys_age <- lm(mean_within_sys~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+race_factor, data=main_unique)
summary(lm_within_sys_age)
lm_between_sys_age <- lm(mean_between_sys~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+race_factor, data=main_unique)
summary(lm_between_sys_age)
lm_segreg_age<- lm(system_segreg~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+race_factor, data=main_unique)
summary(lm_segreg_age)
lm_modul_avg_age <- lm(modul_avg~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+race_factor, data=main_unique)
summary(lm_modul_avg_age)
lm_part_coef_age <- lm(part_coef~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+race_factor, data=main_unique)
summary(lm_part_coef_age)

#swap out race2 for income_median, parent1_edu, ses_composite, or childaces_sum_ignorenan
lm_within_sys_age <- lm(mean_within_sys~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+race_factor+parent1_edu, data=main_unique)
summary(lm_within_sys_age)
lm_between_sys_age <- lm(mean_between_sys~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+race_factor+parent1_edu, data=main_unique)
summary(lm_between_sys_age)
lm_segreg_age<- lm(system_segreg~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+race_factor+parent1_edu, data=main_unique)
summary(lm_segreg_age)
lm_modul_avg_age <- lm(modul_avg~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+race_factor+parent1_edu, data=main_unique)
summary(lm_modul_avg_age)
lm_part_coef_age <- lm(part_coef~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+race_factor+parent1_edu, data=main_unique)
summary(lm_part_coef_age)

#childaces_sum_ignorenan
lm_within_sys_age <- lm(mean_within_sys~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+childaces_sum_ignorenan, data=main_unique)
summary(lm_within_sys_age)
lm_between_sys_age <- lm(mean_between_sys~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+childaces_sum_ignorenan, data=main_unique)
summary(lm_between_sys_age)
lm_segreg_age<- lm(system_segreg~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+childaces_sum_ignorenan, data=main_unique)
summary(lm_segreg_age)
lm_modul_avg_age <- lm(modul_avg~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+childaces_sum_ignorenan, data=main_unique)
summary(lm_modul_avg_age)
lm_part_coef_age <- lm(part_coef~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+childaces_sum_ignorenan, data=main_unique)
summary(lm_part_coef_age)
```

However, there are effects of the binned ACES (into 0-1, 2, or 3+) on within- and between-network connectivity as well as the participation coefficient. We see that 2 ACES is associated with significantly less within- and more between-network connectivity and lower system segregation.

```{r main effect aces on segregation plots, echo=FALSE, include=TRUE, results='hide',fig.show='hold', out.width='33.33%', fig.align='default'}
lm_within_sys_age <- lm(mean_within_sys~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+aces3category+ses_composite, data=main_unique)
summary(lm_within_sys_age)
lm_between_sys_age <- lm(mean_between_sys~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+aces3category+ses_composite, data=main_unique)
summary(lm_between_sys_age)
lm_segreg_age<- lm(system_segreg~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+aces3category+ses_composite, data=main_unique)
lm_part_coef_age <- lm(part_coef~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+aces3category+ses_composite, data=main_unique)
visreg(lm_within_sys_age,"age_scan",by="aces3category", overlay=TRUE)
visreg(lm_between_sys_age,"age_scan",by="aces3category", overlay=TRUE)
visreg(lm_part_coef_age,"age_scan",by="aces3category", overlay=TRUE)
```

## Questions, Notes, & Future Directions

* There are also sometimes outliers on some of the measures that flatten out age or environment trends, I have been looking into using robust regression to examine these trends instead, but did not go through all the trouble to bootstrap p-values for this time around. However, I think it's possible that robust regression might be a more defensible choice.

## Plot average functional connectivity matrices

We can also compare these to the PNC adolescent matrix and see how it differs.

ggcorrplot

ggcorr is better

What if we add the two runs for subjects who have more than one, what does that buy us? 
```{r plot matrices,  echo=FALSE, include=TRUE,fig.show='hold', out.width='100%'}
library(mdpeer)
network_dir=paste0("~/Desktop/cluster/jux/mackey_group/Ursula/projects/in_progress/within_between_network_conn_CBPD/data/imageData/",pipeline)
avg_matrix <- read.csv(paste0(network_dir,""), header = FALSE)
#reorder by yeo labels
#read in schaefer to yeo labels
#put labels on top and bottom
#subject_clustco_yeo_system<-l %>% arrange(labels) %>% summarize_all(mean)

avgmatrix <- as.matrix(avg_matrix)
# palf <- colorRampPalette(c("red","white", "blue")) 
# heatmap(avgmatrix, Rowv = NA, Colv = NA, col = palf(20))
plot(vizu.mat(avgmatrix, fill.scale.limits = c(-1.3, 1.3), x.lab=pipeline))

```

# Supplemental Analyses

## Replication parcellation: Schaefer200

```{r replication in Schaefer200}
#Use main_replicate_unique instead



networks_age_pvals_fdr_replicate
```

### Age and measures of network segregation

We used Schaefer200 as the replication parcellation, since it has nice correspondence to Schaefer400 and the Yeo7 systems. 

```{r replicate models of segregation, echo=FALSE, include=FALSE, results='hide'}
#look at mean within and between with age
lm_within_sys_age <- lm(mean_within_sys~age_scan+male+fd_mean+avgweight+pctSpikesFD+size_t, data=main_replicate_unique)
lm_between_sys_age <- lm(mean_between_sys~age_scan+male+fd_mean+avgweight+pctSpikesFD+size_t, data=main_replicate_unique)

lm_segreg_age<- lm(system_segreg~age_scan+male+fd_mean+avgweight+pctSpikesFD+size_t, data=main_replicate_unique)

lm_modul_avg_age <- lm(modul_avg~age_scan+male+fd_mean+avgweight+pctSpikesFD+size_t, data=main_replicate_unique)

lm_part_coef_age <- lm(part_coef~age_scan+male+fd_mean+avgweight+pctSpikesFD+size_t, data=main_replicate_unique)
lm_num_comms_age <- lm(num_comms_modul_avg~age_scan+male+fd_mean+avgweight+pctSpikesFD+size_t, data=main_replicate_unique)

```

```{r replicate plots of segregation, echo=FALSE, include=TRUE, results='hide'}
par(mfrow=c(2,3))
visreg(lm_between_sys_age,"age_scan")
visreg(lm_within_sys_age,"age_scan")
visreg(lm_segreg_age,"age_scan")
visreg(lm_modul_avg_age,"age_scan")
visreg(lm_part_coef_age,"age_scan")
visreg(lm_num_comms_age,"age_scan")
```

All previous findings significant increases in network segregation with age hold in our replication parcellation! The only finding that is inconsistent is the number of communities detected using modul_avgarity maximization decreasing with age, which was likely spurious anyways.

As a reminder, we controlled for sex, mean framewise displacement, percent of FD spikes in the data, the number of volumes a participant had, and the average weight of the functional network.

Also, no non-linear effects of age.

### System-level effects
Again, we find the strongest effects in Vis-DAN, DMN-DAN, and DMN-VAN, which are the only effects that pass *fdr* correction.

```{r lm replicate plots, echo=FALSE, include=TRUE, results='hide', fig.show='hold', out.width='33.33%', fig.align='default'}
networks_age_pvals_fdr_replicate
lm_sys1to3<- lm(sys1to3~age_scan+male+fd_mean+avgweight+pctSpikesFD+size_t, data=main_replicate_unique)
lm_sys3to7<- lm(sys3to7~age_scan+male+fd_mean+avgweight+pctSpikesFD+size_t, data=main_replicate_unique)
lm_sys4to7<- lm(sys4to7~age_scan+male+fd_mean+avgweight+pctSpikesFD+size_t, data=main_replicate_unique)

visreg(lm_sys1to3,"age_scan",main="Vis to DAN")
visreg(lm_sys3to7,"age_scan", main="DMN to DAN")
visreg(lm_sys4to7,"age_scan",  main="DMN to VAN")
```

All three effects survive FDR correction across the tests conducted, with DMN-VAN *p_fdr*=`r networks_age_pvals_fdr_replicate$pvalue[networks_age_pvals_fdr_replicate$network=="sys3to7"]`, DMN-DAN *p_fdr*= `r networks_age_pvals_fdr_replicate$pvalue[networks_age_pvals_fdr_replicate$network=="sys4to7"]`, Vis-DAN *p_fdr*= `r networks_age_pvals_fdr_replicate$pvalue[networks_age_pvals_fdr_replicate$network=="sys1to3"]`.

## Replication with a pipeline without GSR

```{r replication without GSR}
#load the .RDS file
pipeline='nogsr_spkreg_fd0.5dvars1.75_drpvls'
network_dir=paste0("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/",pipeline)
load(paste0(network_dir,"/CBPD_n90_schaefer400_allruns.Rdata"))


```

## Test-retest reliability of network metrics

Using both Pearson's correlation and the ICC. Noble et al. 2019 in their review on TRT of functional connectivity metrics suggest using ICC(1,1), or single_raters_absolute, which is used to estimate agreement in exact values when sources of error are unspecified. However, they acknowledge that using ICC(1,2) (averaging across two runs) yields an estimate of how much reliability improves when averaging across multiple sessions.

"Absolute agreement of connectivity derived from a single session (k=1) is necessarily lower than that averaged over two sessions (k=2), and this k=2 estimate may be used to estimate how much reliability improves when averaging over multiple measurements (e.g., repeated sessions), assuming they are interchangeable."

Tozzi et al. 2019 also looked at individual edges reliability, but they used ICC(3,1), which will always result in a higher value! Both papers find individual edges generally have poor reliability (< 0.4).
```{r TRT of net metrics,  echo=FALSE, include=TRUE,fig.show='hold', out.width='100%'}
pipelines=c("nogsr_spkreg_fd1.25dvars2_drpvls", 'nogsr_spkreg_fd0.5dvars1.75_drpvls', "gsr_censor_5contig_fd1.25dvars2_drpvls",'gsr_spkreg_fd0.5dvars1.75_drpvls', "gsr_censor_5contig_fd0.5dvars1.75_drpvls")
for (pipeline in pipelines){
network_dir=paste0("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/",pipeline)
load(paste0(network_dir,"/CBPD_n74_schaefer400.Rdata"))
#filter for only participants with more than 2 runs
dim(main)
#### examine the number of good vols in run1 vs run2####
l <- main_filt %>% group_by(ID) %>% filter(n() >= 2) %>% filter(run=="run-01")
hist(l$nVolCensored, main = "run 1= red, run 2 = blue, n Vols Censored", col=rgb(1,0,0,0.5))
l2 <- main_filt %>% group_by(ID) %>% filter(n() >= 2) %>% filter(run=="run-02")
hist(l2$nVolCensored,col=rgb(0,0,1,0.5), add=T)
### Test ret-test ####
trt <- main_filt %>% group_by(ID) %>% filter(n() >= 2) %>% dplyr::select(.,ID:pctSpikesFD_avg)
#rename 150 run 3 to run 2 so it goes in the right column
trt$run[trt$ID=="sub-CBPD0150" & trt$run=="run-03"] <- "run-02"
cols <- trt %>% ungroup() %>% dplyr::select(.,avgweight:sys7to7) %>%  colnames()
trt <- dcast(setDT(trt), ID~run, value.var = cols)
colnames(trt) <- make.names(colnames(trt)) #reshaped column names have - in them which is prohibited, then we can have a dataframe
trt <- as.data.frame(trt)
for (column in cols){
  temp <- trt %>% dplyr::select(.,matches(paste0("^",column)))
  assign(paste0(column, "_trt_corr"),cor.test(temp[,1], temp[,2])) #correlation
  assign(paste0(column, "_trt_icc"), ICC(temp, lmer = FALSE))
}
print(pipeline)
avgweight_trt_corr
modul_avg_trt_corr
mean_within_sys_trt_corr
mean_between_sys_trt_corr
system_segreg_trt_corr
avgweight_trt_icc
modul_avg_trt_icc
mean_within_sys_trt_icc
mean_between_sys_trt_icc
system_segreg_trt_icc
```
