---
title: "CBPD Results from Freesurfer"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(stats)
library(parallel)
library(lm.beta)
library(packrat)
library(summarytools)
library(visreg)
library(mgcv)
library(RLRsim)
library(GGally)
library(stringr)
library(tidyverse)
library(data.table)
library(bigmemory)
library(biglm)
#load the .RDS file
pipeline='nogsr_spkreg_fd0.5dvars1.75_drpvls'
pipeline="nogsr_spkreg_fd1.25dvars2_drpvls"
pipeline='gsr_spkreg_fd0.5dvars1.75_drpvls'
network_dir=paste0("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/",pipeline)

load(paste0(network_dir,"/CBPD_n92_schaefer400_allruns.Rdata"))
```

```{r brain plotting setup, include=FALSE, echo=FALSE}
library(fsbrain) #this may not work if you're editing the script directly on the cluster...
library(freesurferformats)
#rearrange the order of the brains in the T9 view of fsbrain
source("~/Documents/tools/fsbrain_fix_t9.R")
environment(brainview.t9) <- asNamespace('fsbrain')
assignInNamespace("brainview.t9", brainview.t9, ns = "fsbrain")
subjects_dir = "/Users/utooley/Documents/tools/CBIG/stable_projects/brain_parcellation/Schaefer2018_LocalGlobal/Parcellations/FreeSurfer5.3/";
subject_id = 'fsaverage';       # for functions which use one subject only
atlas='Schaefer2018_400Parcels_7Networks_order'

#Get the Schaefer atlas region names
schaefer_atlas_region_names_lh = get.atlas.region.names(atlas, template_subjects_dir = subjects_dir,template_subject=subject_id, hemi="lh");
schaefer_atlas_region_names_rh = get.atlas.region.names(atlas, template_subjects_dir = subjects_dir,template_subject=subject_id, hemi="rh");

#set output dir for saving images
output_image_directory="~/Documents/projects/in_progress/within_between_network_conn_CBPD/output/figures/brains/"
  
#Set RGL defaults, larger window and how to make snapshots!
rgloptions=list("windowRect"=c(50,50,1000,1000));

# ## Make subjlist for qdec analyses
# subid <- n126_parcel_SA_data$ID
# age_scan <- scale(n126_parcel_SA_data$age_scan, center=T, scale = T)
# sex <- ifelse(n126_parcel_SA_data$male==0,0,1)
# t1_rating <- scale(n126_parcel_SA_data$t1_rating_avg, center=T, scale = T)
# n126_agesex_ursula_data <- cbind(subid,age_scan,sex,t1_rating)
# colnames(n126_agesex_ursula_data) <- c("fsid","age_scan","sex","t1_rating")
# #Make the sex column 0-1 to not lose df
# write.table(n126_agesex_ursula_data, file = paste("~/Downloads/qdec.agesext1rating.n126.table.dat", sep=""), row.names = F, quote=F)
# 
# subid <- main_unique$ID
# age_scan <- scale(main_unique$age_scan, center=T, scale = T)
# sex <- ifelse(main_unique$male=="Male", 1, 0)
# t1_rating <- scale(main_unique$t1_rating_avg, center=T, scale = T)
# n92_agesex_ursula_data <- cbind(subid,age_scan,sex,t1_rating)
# colnames(n92_agesex_ursula_data) <- c("fsid","age_scan","sex","t1_rating")
# #Make the sex column 0-1 to not lose df
# write.table(x, file = paste("~/Downloads/qdec.agesext1rating.n89.table.dat", sep=""), row.names = F, quote=F)
# x <- read.table("~/Downloads/qdec.agesext1rating.n89.table.dat")
```

## Load data
```{r load SA and CT parcel data, include=FALSE, echo=FALSE}

#age on CT
lh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/lh_thickness_agesext1rating_n89/lh-Avg-thickness-age_scan-Cor/cache.th23.abs.sig.voxel.mgh")
rh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/rh_thickness_agesext1rating_n89/rh-Avg-thickness-age_scan-Cor/cache.th23.abs.sig.voxel.mgh")

??freesurfer.formats
summary(lh);length(lh)
hist(lh)
summary(rh);length(rh)
hist(rh)

rglactions=list("snapshot_png"=paste0(output_image_directory,"age_CT_map.png"), 'shift_hemis_apart'=TRUE)
colFn_diverging = colorRampPalette(c(rev(RColorBrewer::brewer.pal(9, name="Blues"))));makecmap_options=list('colFn'=colFn_diverging)
vis.data.on.fsaverage(subjects_dir, 'fsaverage',surface = "inflated",lh, rh, makecmap_options = makecmap_options, draw_colorbar = T, 
                       views="t9", rgloptions = rgloptions, rglactions = NULL)

vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  lh, 
                             rh, makecmap_options = makecmap_options, "inflated", views="t9", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)

#Age on SA data
lh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/lh_area_agesext1rating_fwhm10/lh-Avg-area-age_scan-Cor/cache.th23.abs.sig.masked.mgh")
rh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/rh_area_agesext1rating_fwhm10/rh-Avg-area-age_scan-Cor/cache.th23.abs.sig.masked.mgh")


rglactions=list("snapshot_png"=paste0(output_image_directory,"age_SA_map.png"), 'shift_hemis_apart'=TRUE)
colFn_diverging = colorRampPalette(c(rev(RColorBrewer::brewer.pal(9, name="RdBu"))));makecmap_options=list('colFn'=colFn_diverging)
vis.data.on.fsaverage(subjects_dir, 'fsaverage',surface = "inflated",lh, rh, makecmap_options = makecmap_options, draw_colorbar = T, 
                       views="t9", rgloptions = rgloptions, rglactions = rglactions)

vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  lh, 
                             rh, makecmap_options = makecmap_options, "inflated", views="t9", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)
```

## Examine shape of plot from age linear on CT in Freesurfer
```{plot ocn CT linear age effect}
lh <- read.table("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/lh_thickness_agesext1rating_n89/lh-Avg-thickness-age_scan-Cor/cache.th23.abs.y.ocn.dat")
rh <- read.table("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/rh_thickness_agesext1rating_n89/rh-Avg-thickness-age_scan-Cor/cache.th23.abs.y.ocn.dat")
subs <- read.table("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/qdec.agesext1rating.n89.table.dat", header = T) %>% select(fsid)
avg_agesq_parcel_sa <- cbind(subs,lh,rh);colnames(avg_agesq_parcel_sa) <- c("ID", "Lcluster1","Lcluster2","Lcluster3", "Rcluster1", "Rcluster2","Rcluster3")
avg_age_parcel_ct <- avg_agesq_parcel_sa %>% mutate(avgct_med_vis_clust=(Lcluster1+Rcluster1)/2, avgct_total_vis_clust=(Lcluster1+Lcluster2+Lcluster3+Rcluster1+Rcluster2+Rcluster3)/5)
main_unique <- left_join(main_unique,avg_age_parcel_ct, by="ID")

lm_sasq<- lm(avgct_total_vis_clust~age_scan+male+t1_rating_avg, data=main_unique)
summary(lm_sasq)
visreg(lm_sasq)
```

## CT linear age effect by network, plot and statistical test

```{CT linear age effect by community}
source("~/Documents/tools/raincloud.R")
#age on CT
lh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/lh_thickness_agesext1rating_n89/lh-Avg-thickness-age_scan-Cor/cache.th23.abs.sig.masked.mgh")
rh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/rh_thickness_agesext1rating_n89/rh-Avg-thickness-age_scan-Cor/cache.th23.abs.sig.masked.mgh")
#load schaefer parcellation at fsaverage res and remap parcel edge data to vertices?
schaefer_lh <-subject.annot(subjects_dir = subjects_dir,subject_id =subject_id, hemi="lh", atlas = atlas)
schaefer_rh <-subject.annot(subjects_dir = subjects_dir,subject_id =subject_id, hemi="rh", atlas = atlas)
communities_lh <- str_remove_all(schaefer_lh$label_names, "7Networks_.H_");communities_lh <- sub("_.*", "", communities_lh)
communities_rh <- str_remove_all(schaefer_rh$label_names, "7Networks_.H_");communities_rh <- sub("_.*", "", communities_rh)
longdata <- data.frame(c(lh,rh),c(communities_lh,communities_rh));colnames(longdata) <- c("value","community")
longdata$community <- factor(longdata$community, levels=c("Background+FreeSurfer","Vis","SomMot","DorsAttn","SalVentAttn", "Limbic","Cont","Default"))
#stats
kruskal.test(value~community, data = longdata)
pairwise.wilcox.test(longdata$value, longdata$community,
                     p.adjust.method = "bonferroni")
summary(lm(value~Var2,data=longdata))
longdata$value[longdata$value==0] <- NA

#Plot it
g <- ggplot(data = longdata, aes(y = value, x = community, fill=community)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .5) +
  geom_point(aes(y = value, color = community), position = position_jitter(width = .15), size = .3, alpha = 0.1) +
  geom_boxplot(width = .2, guides = FALSE, outlier.shape = NA, alpha = 0.8) +
  #ylim(c(-7,0)) +
  guides(fill = FALSE) +
  guides(color = FALSE) +
  # scale_color_manual(values=c("#4669dc","pink","purple")) +
  #scale_color_distiller(palette="Blues", direction = 1) +
  #scale_fill_distiller(palette="Blues", direction = 1) +
  scale_color_manual(values=c("gray","#7B287E", "#5CA1C8", "#0A9045","#C33AF8", "#B6C988", "#EF9C23", "#E34A53")) +
  scale_fill_manual(values= c("gray","#7B287E", "#5CA1C8", "#0A9045","#C33AF8", "#B6C988", "#EF9C23", "#E34A53")) +
  #scale_color_gradient2(low="#FFFFFF",mid= "#FB6A4A", high="#67000D", midpoint= 0.475, aesthetics = c("color", "fill")) +
  theme_bw() +
  raincloud_theme
print(g)
```

# Load CT data from age-squared in Freesurfer

```{age_squared CT FS}
lh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/lh_thickness_ageagesqt1ratingsex_fwhm10_n89/lh-Avg-thickness-age_sq-Cor/cache.th23.abs.sig.masked.mgh")
rh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/rh_thickness_ageagesqt1ratingsex_fwhm10_n89/rh-Avg-thickness-age_sq-Cor/cache.th23.abs.sig.masked.mgh") 
#Nothing
```

#Load SA data from Age-squared in Freesurfer
```{age_squared FS}

lh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/lh_area_agesq_age_sex_t1rating_fwhm10_n89/lh-Avg-area-age_sq-Cor/cache.th23.abs.sig.masked.mgh")
rh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/rh_area_ageagesqsext1rating_fwhm10_n89/rh-Avg-area-age_sq-Cor/cache.th23.abs.sig.masked.mgh")

rglactions=list("snapshot_png"=paste0(output_image_directory,"age_SAsq_map.png"), 'shift_hemis_apart'=TRUE)
colFn_diverging = colorRampPalette(c(rev(RColorBrewer::brewer.pal(9, name="Blues"))));makecmap_options=list('colFn'=colFn_diverging)
vis.data.on.fsaverage(subjects_dir, 'fsaverage',surface = "inflated",lh, rh, makecmap_options = makecmap_options, draw_colorbar = T, 
                       views="t9", rgloptions = rgloptions, rglactions = rglactions)

#Using the buttons in qdec instead of mri_glmfit
lh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/lh_area_agesq_age_sex_t1rating_fwhm10_n89/lh-Avg-area-age_sq-Cor/mc-z.abs.th23.sig.cluster.mgh")
rh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/rh_area_ageagesqsext1rating_fwhm10_n89/rh-Avg-area-age_sq-Cor/mc-z.abs.th23.sig.cluster.mgh")
rglactions=list("snapshot_png"=paste0(output_image_directory,"age_SAsq_qdecmc_map.png"), 'shift_hemis_apart'=TRUE)
colFn_diverging = colorRampPalette(c(rev(RColorBrewer::brewer.pal(9, name="RdBu"))));makecmap_options=list('colFn'=colFn_diverging, 'symm'=TRUE)
vis.data.on.fsaverage(subjects_dir, 'fsaverage',surface = "inflated",lh, rh, makecmap_options = makecmap_options, draw_colorbar = T, 
                       views="t9", rgloptions = rgloptions, rglactions = rglactions)

```

## Examine shape of plot from age-squared on SA in Freesurfer

```{age-squared SA in FS}
lh <- read.table("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/lh_area_agesq_age_sex_t1rating_fwhm10_n89/lh-Avg-area-age_sq-Cor/cache.th23.abs.y.ocn.dat")
rh <- read.table("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/rh_area_ageagesqsext1rating_fwhm10_n89/rh-Avg-area-age_sq-Cor/mc-z.abs.th23.pdf.dat")
subs <- read.table("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/qdec.agesext1rating.n89.table.dat", header = T) %>% select(fsid)
avg_agesq_parcel_sa <- cbind(subs,lh);colnames(avg_agesq_parcel_sa) <- c("ID", "Lcluster1")
# avg_age_parcel_ct <- avg_agesq_parcel_sa %>% mutate(avgct_med_vis_clust=(Lcluster1+Rcluster1)/2, avgct_total_vis_clust=(Lcluster1+Lcluster2+Lcluster3+Rcluster1+Rcluster2)/5)
main_unique <- left_join(main_unique,avg_agesq_parcel_sa, by="ID")

lm_sasq<- gam(Lcluster1~s(age_scan, k=4)+male+t1_rating_avg, data=main_unique)
summary(lm_sasq)
visreg(lm_sasq)

```

## SA age-sq effect by network, plot and statistical test

```{CT linear age effect by community}
#age on CT
lh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/lh_area_agesq_age_sex_t1rating_fwhm10_n89/lh-Avg-area-age_sq-Cor/cache.th23.abs.sig.masked.mgh")
rh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/rh_area_ageagesqsext1rating_fwhm10_n89/rh-Avg-area-age_sq-Cor/cache.th23.abs.sig.masked.mgh")
#load schaefer parcellation at fsaverage res and remap parcel edge data to vertices?
schaefer_lh <-subject.annot(subjects_dir = subjects_dir,subject_id =subject_id, hemi="lh", atlas = atlas)
schaefer_rh <-subject.annot(subjects_dir = subjects_dir,subject_id =subject_id, hemi="rh", atlas = atlas)
communities_lh <- str_remove_all(schaefer_lh$label_names, "7Networks_.H_");communities_lh <- sub("_.*", "", communities_lh)
communities_rh <- str_remove_all(schaefer_rh$label_names, "7Networks_.H_");communities_rh <- sub("_.*", "", communities_rh)
longdata <- data.frame(c(lh,rh),c(communities_lh,communities_rh));colnames(longdata) <- c("value","community")
longdata$community <- factor(longdata$community, levels=c("Background+FreeSurfer","Vis","SomMot","DorsAttn","SalVentAttn", "Limbic","Cont","Default"))
#stats
kruskal.test(value~community, data = longdata)
pairwise.wilcox.test(longdata$value, longdata$community,
                     p.adjust.method = "bonferroni")
summary(lm(value~Var2,data=longdata))
longdata$value[longdata$value==0] <- NA

#Plot it
g <- ggplot(data = longdata, aes(y = value, x = community, fill=community)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .5) +
  geom_point(aes(y = value, color = community), position = position_jitter(width = .15), size = .3, alpha = 0.1) +
  geom_boxplot(width = .2, guides = FALSE, outlier.shape = NA, alpha = 0.8) +
  ylim(c(-7,0)) +
  guides(fill = FALSE) +
  guides(color = FALSE) +
  # scale_color_manual(values=c("#4669dc","pink","purple")) +
  #scale_color_distiller(palette="Blues", direction = 1) +
  #scale_fill_distiller(palette="Blues", direction = 1) +
  scale_color_manual(values=c("gray","#7B287E", "#5CA1C8", "#0A9045","#C33AF8", "#B6C988", "#EF9C23", "#E34A53")) +
  scale_fill_manual(values= c("gray","#7B287E", "#5CA1C8", "#0A9045","#C33AF8", "#B6C988", "#EF9C23", "#E34A53")) +
  #scale_color_gradient2(low="#FFFFFF",mid= "#FB6A4A", high="#67000D", midpoint= 0.475, aesthetics = c("color", "fill")) +
  theme_bw() +
  raincloud_theme
print(g)
```
#Load SA data from n=126 in Freesurfer
```{age_squared FS}

lh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/lh_area_agesq_age_sex_t1rating_fwhm10_n89/lh-Avg-area-age_sq-Cor/mc-z.abs.th23.sig.cluster.mgh",drop_empty_dims = T);lh <- lh[,1]
rh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/rh_area_agesqagesext1rating_fwhm10_n89/rh-Avg-area-age_sq-Cor/mc-z.abs.th23.sig.cluster.mgh",drop_empty_dims = T);rh <- rh[,1]

rglactions=list('shift_hemis_apart'=TRUE)
colFn_diverging = colorRampPalette(c(rev(RColorBrewer::brewer.pal(9, name="Blues")),"white"));makecmap_options=list('colFn'=colFn_diverging, range=c(-4,0))
vis.data.on.fsaverage(subjects_dir, 'fsaverage',surface = "inflated",lh, rh, makecmap_options = makecmap_options, draw_colorbar = T, 
                       views="t9", rgloptions = rgloptions, rglactions = rglactions)
```

# Spin tests

If you want to do vertex-wise spin tests, look at https://github.com/spin-test/spin-test
For parcel-wise spin tests i used the Vasa code, from here: https://github.com/frantisekvasa/rotate_parcellation

## Age on CT from Freesurfer--masked significant clusters, by parcel
```{age on CT linear}
source("~/Documents/tools/rotate_parcellation/R/rotate.parcellation.R")
source("~/Documents/tools/rotate_parcellation/R/perm.sphere.p.R")
library(matrixStats) #otherwise get rowMins error
#read in centroids of the Schaefer400 parcels
lh_centroids <- as.matrix(read.csv("~/Documents/tools/parcellations/lh.Schaefer400_7Nets_fsaverage6.centroids.csv", header = F));rh_centroids <- as.matrix(read.csv("~/Documents/tools/parcellations/rh.Schaefer400_7Nets_fsaverage6.centroids.csv", header = F))
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/rotations_schaefer400_fsaverage6_10000x.Rdata")
#SHOULD BE MASKING OUT MEDIAL WALL? Assuming that is first centroid for each
lh_centroids <- lh_centroids[-1,];rh_centroids <- rh_centroids[-1,];
#load age on CT from FS
lh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/lh_thickness_agesext1rating_n89/lh-Avg-thickness-age_scan-Cor/cache.th23.abs.sig.masked.mgh") #voxel-wise corrected?
#load schaefer parcellation at fsaverage res and average by parcel
detach("package:plyr", unload=TRUE)
schaefer_lh <-subject.annot(subjects_dir = subjects_dir,subject_id =subject_id, hemi="lh", atlas = atlas)
d <- data.frame(lh, schaefer_lh$label_names) %>% rename(schaefer_atlas_region_names_lh=schaefer_lh.label_names) %>% group_by(schaefer_atlas_region_names_lh) %>% summarise(mean=mean(lh));
lh_parcels_CT <- left_join(data.frame(schaefer_atlas_region_names_lh),d, by= "schaefer_atlas_region_names_lh")
schaefer_rh <-subject.annot(subjects_dir = subjects_dir,subject_id =subject_id, hemi="rh", atlas = atlas)
rh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/rh_thickness_agesext1rating_n89/rh-Avg-thickness-age_scan-Cor/cache.th23.abs.sig.masked.mgh")
d <- data.frame(rh, schaefer_rh$label_names) %>% rename(schaefer_atlas_region_names_rh=schaefer_rh.label_names) %>% group_by(schaefer_atlas_region_names_rh) %>% summarise(mean=mean(rh));rh_parcels_CT <- left_join(data.frame(schaefer_atlas_region_names_rh),d, by= "schaefer_atlas_region_names_rh")

#load back in edge age effects
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/edgewise_age_effects_all_cov_n92.Rdata")
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400)
edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1] #take uncorrected p-values for now
edge_age_pvals_mat <- t(edge_age_pvals_mat)#copy lower triangle to upper triangle
pos_edges <- edge_age_pvals_mat;pos_edges[edge_age_betas_mat<0] <- NA
neg_edges <- edge_age_pvals_mat;neg_edges[edge_age_betas_mat>0] <- NA

pvalues=c(0.05,0.01,0.001,0.0001)
for (pvalue in pvalues){
  print(pvalue)
indices <- which(edge_age_pvals_mat<pvalue, arr.ind = T) #indices of edges that have age effects  below a pval
l <- data.frame(table(indices)) #for each parcel, how many age-significant edges does it have at a given pval thresh
values <- vector(mode = "double", 400)
for (i in 1:400){
values[as.numeric(as.character(l$indices[i]))] <- l$Freq[i]#replace the indices in values with the num of sig edges from that parcel in the table
}
#maps to compare
edge_vector=values

#other map of CT
#parcel_CT_pvals_thresh <- ifelse(parcel_CT_pvals_fdr[,1]<0.05,parcel_CT_pvals_fdr[,1],0)
#CT_betas_vector=ifelse(parcel_CT_pvals_fdr[,1]<0.05, parcel_CT_betas,0)
#CT_vector=1-parcel_CT_pvals_fdr[,1] #parcel_SA_pvals uncorrected, or thresholded p-values
CT_vector= -c(lh_parcels_CT$mean, rh_parcels_CT$mean)[-c(1,202)]

#rotations<- rotate.parcellation(lh_centroids,rh_centroids,1000)
print(perm.sphere.p(edge_vector,CT_vector, rotations, "pearson"))
#print(perm.sphere.p(edge_vector,parcel_CT_pvals_thresh, rotations, "pearson"))
#print(perm.sphere.p(edge_vector,parcel_CT_betas, rotations, "pearson"))
#print(perm.sphere.p(edge_vector,CT_betas_vector, rotations, "pearson"))
}

#Plot the two
num_of_sig_age_edges_lh=as.list(setNames(c(NA, c(lh_parcels_SA$mean, lh_parcels_SA$mean)[-c(1,202)][1:200]), schaefer_atlas_region_names_lh))
num_of_sig_age_edges_rh=as.list(setNames(c(NA, c(lh_parcels_CT$mean, rh_parcels_CT$mean)[-c(1,202)][201:400]), schaefer_atlas_region_names_rh))
num_of_sig_age_edges_lh=as.list(setNames(c(NA,edge_vector[1:200]), schaefer_atlas_region_names_lh))
num_of_sig_age_edges_rh=as.list(setNames(c(NA, edge_vector[201:400]), schaefer_atlas_region_names_rh))
#colormap
colFn_diverging = colorRampPalette((c("white","lightblue", "blue")));makecmap_options=list('colFn'=colFn_diverging)
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  num_of_sig_age_edges_lh, 
                             num_of_sig_age_edges_rh, makecmap_options = makecmap_options, "inflated", views="t4", draw_colorbar = T, rgloptions = rgloptions, rglactions = NULL)

```

## Age on CT from Freesurfer--masked significant clusters, by vertex
```{age on CT linear by vertex}
source("~/Documents/tools/rotate_parcellation/R/rotate.parcellation.R")
source("~/Documents/tools/rotate_parcellation/R/perm.sphere.p.R")
library(matrixStats) #otherwise get rowMins error
#read in centroids of the Schaefer400 parcels
lh_centroids <- as.matrix(read.csv("~/Documents/tools/parcellations/lh.Schaefer400_7Nets_fsaverage6.centroids.csv", header = F));rh_centroids <- as.matrix(read.csv("~/Documents/tools/parcellations/rh.Schaefer400_7Nets_fsaverage6.centroids.csv", header = F))
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/rotations_schaefer400_fsaverage6_10000x.Rdata")
#SHOULD BE MASKING OUT MEDIAL WALL? Assuming that is first centroid for each
lh_centroids <- lh_centroids[-1,];rh_centroids <- rh_centroids[-1,];
#load age on CT from FS
lh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/lh_thickness_agesext1rating_n89/lh-Avg-thickness-age_scan-Cor/cache.th23.abs.sig.masked.mgh") #voxel-wise corrected?
rh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/rh_thickness_agesext1rating_n89/rh-Avg-thickness-age_scan-Cor/cache.th23.abs.sig.masked.mgh")
#write to csv for matlab
write.csv(lh,"~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/spin_tests/lh_age_linear_on_CT_from_FS.csv");write.csv(rh,"~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/spin_tests/rh_age_linear_on_CT_from_FS.csv")

#load schaefer parcellation at fsaverage res and remap parcel edge data to vertices?
schaefer_lh <-subject.annot(subjects_dir = subjects_dir,subject_id =subject_id, hemi="lh", atlas = atlas)
schaefer_rh <-subject.annot(subjects_dir = subjects_dir,subject_id =subject_id, hemi="rh", atlas = atlas)

#load back in edge age effects
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/edgewise_age_effects_all_cov_n92.Rdata")
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400)
edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1] #take uncorrected p-values for now
edge_age_pvals_mat <- t(edge_age_pvals_mat)#copy lower triangle to upper triangle
pos_edges <- edge_age_pvals_mat;pos_edges[edge_age_betas_mat<0] <- NA
neg_edges <- edge_age_pvals_mat;neg_edges[edge_age_betas_mat>0] <- NA

pvalues=c(0.05,0.01,0.001,0.0001)
for (pvalue in pvalues){
  print(pvalue)
indices <- which(neg_edges<pvalue, arr.ind = T) #indices of edges that have age effects  below a pval
l <- data.frame(table(indices)) #for each parcel, how many age-significant edges does it have at a given pval thresh
values <- vector(mode = "double", 400)
for (i in 1:400){
values[as.numeric(as.character(l$indices[i]))] <- l$Freq[i]#replace the indices in values with the num of sig edges from that parcel in the table
}
#maps to compare
edge_vector=values
#map this vector to vertices using schaefer parcellation in fsaverage space
lh_edge_vector=vector(length = length(schaefer_lh$label_names))
rh_edge_vector=vector(length = length(schaefer_rh$label_names))
for (i in 2:201){
  lh_edge_vector <- ifelse(schaefer_lh$label_names==schaefer_lh$colortable$struct_names[i], edge_vector[i-1], lh_edge_vector)
}
for (i in 2:201){
  rh_edge_vector <- ifelse(schaefer_rh$label_names==schaefer_rh$colortable$struct_names[i], edge_vector[i+199], rh_edge_vector)
}
lh_edge_vector;rh_edge_vector
#write out
write.csv(x = -lh_edge_vector, file =paste0("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/spin_tests/lh_age_neg_sig_edges_",pvalue,"_rev.csv"))
write.csv(x = -rh_edge_vector, file =paste0("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/spin_tests/rh_age_neg_sig_edges_",pvalue,"_rev.csv"))
}
#Plot to be sure
rh <- read.csv("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/spin_tests/rh_age_linear_on_CT_from_FS.csv") %>% pull(x);lh <- read.csv("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/spin_tests/lh_age_linear_on_CT_from_FS.csv") %>% pull(x)
rglactions=list('shift_hemis_apart'=TRUE)
colFn_diverging = colorRampPalette(c(rev(RColorBrewer::brewer.pal(9, name="Blues")),"white"));makecmap_options=list('colFn'=colFn_diverging)
vis.data.on.fsaverage(subjects_dir, 'fsaverage',surface = "inflated",lh, rh, makecmap_options = makecmap_options, draw_colorbar = T, 
                       views="t9", rgloptions = rgloptions, rglactions = rglactions)

#Then run the code spin_test_vertex_wise.m!
```

## Age-sq on SA from Freesurfer to negative (and positive) edges--masked significant clusters, by parcel

```{Age-sq on SA from Freesurfer}
source("~/Documents/tools/rotate_parcellation/R/rotate.parcellation.R")
source("~/Documents/tools/rotate_parcellation/R/perm.sphere.p.R")
library(matrixStats) #otherwise get rowMins error
#read in centroids of the Schaefer400 parcels
lh_centroids <- as.matrix(read.csv("~/Documents/tools/parcellations/lh.Schaefer400_7Nets_fsaverage6.centroids.csv", header = F));rh_centroids <- as.matrix(read.csv("~/Documents/tools/parcellations/rh.Schaefer400_7Nets_fsaverage6.centroids.csv", header = F))
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/rotations_schaefer400_fsaverage6_10000x.Rdata")
#SHOULD BE MASKING OUT MEDIAL WALL? Assuming that is first centroid for each
lh_centroids <- lh_centroids[-1,];rh_centroids <- rh_centroids[-1,];
#load age on CT from FS
lh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/lh_area_agesq_age_sex_t1rating_fwhm10_n89/lh-Avg-area-age_sq-Cor/cache.th23.abs.sig.masked.mgh") #voxel-wise corrected?
#load schaefer parcellation at fsaverage res and average by parcel
schaefer_lh <-subject.annot(subjects_dir = subjects_dir,subject_id =subject_id, hemi="lh", atlas = atlas)
d <- data.frame(lh, schaefer_lh$label_names) %>% rename(schaefer_atlas_region_names_lh=schaefer_lh.label_names) %>% group_by(schaefer_atlas_region_names_lh) %>% summarise(mean=mean(lh));lh_parcels_SA <- left_join(data.frame(schaefer_atlas_region_names_lh),d, by= "schaefer_atlas_region_names_lh")
schaefer_rh <-subject.annot(subjects_dir = subjects_dir,subject_id =subject_id, hemi="rh", atlas = atlas)
rh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/rh_area_ageagesqsext1rating_fwhm10_n89/rh-Avg-area-age_sq-Cor/cache.th23.abs.sig.masked.mgh")
d <- data.frame(rh, schaefer_rh$label_names) %>% rename(schaefer_atlas_region_names_rh=schaefer_rh.label_names) %>% group_by(schaefer_atlas_region_names_rh) %>% summarise(mean=mean(rh));rh_parcels_SA <- left_join(data.frame(schaefer_atlas_region_names_rh),d, by= "schaefer_atlas_region_names_rh")

#load back in edge age effects
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/edgewise_age_effects_all_cov_n92.Rdata")
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400)
edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1] #take uncorrected p-values for now
edge_age_pvals_mat <- t(edge_age_pvals_mat)#copy lower triangle to upper triangle
pos_edges <- edge_age_pvals_mat;pos_edges[edge_age_betas_mat<0] <- NA
neg_edges <- edge_age_pvals_mat;neg_edges[edge_age_betas_mat>0] <- NA

pvalues=c(0.05,0.01,0.001,0.0001)
for (pvalue in pvalues){
  print(pvalue)
indices <- which(edge_age_pvals_mat<pvalue, arr.ind = T) #indices of edges that have age effects  below a pval
l <- data.frame(table(indices)) #for each parcel, how many age-significant edges does it have at a given pval thresh
values <- vector(mode = "double", 400)
for (i in 1:400){
values[as.numeric(as.character(l$indices[i]))] <- l$Freq[i]#replace the indices in values with the num of sig edges from that parcel in the table
}
#maps to compare
edge_vector=values

#other map of CT
#parcel_CT_pvals_thresh <- ifelse(parcel_CT_pvals_fdr[,1]<0.05,parcel_CT_pvals_fdr[,1],0)
#CT_betas_vector=ifelse(parcel_CT_pvals_fdr[,1]<0.05, parcel_CT_betas,0)
#CT_vector=1-parcel_CT_pvals_fdr[,1] #parcel_SA_pvals uncorrected, or thresholded p-values
CT_vector= -c(lh_parcels_SA$mean, rh_parcels_SA$mean)[-c(1,202)]

#rotations<- rotate.parcellation(lh_centroids,rh_centroids,1000)
print(perm.sphere.p(edge_vector,CT_vector, rotations, "pearson"))
#print(perm.sphere.p(edge_vector,parcel_CT_pvals_thresh, rotations, "pearson"))
#print(perm.sphere.p(edge_vector,parcel_CT_betas, rotations, "pearson"))
#print(perm.sphere.p(edge_vector,CT_betas_vector, rotations, "pearson"))
}

#Plot the two
num_of_sig_age_edges_lh=as.list(setNames(c(NA, c(lh_parcels_SA$mean, rh_parcels_SA$mean)[-c(1,202)][1:200]), schaefer_atlas_region_names_lh))
num_of_sig_age_edges_rh=as.list(setNames(c(NA, c(lh_parcels_SA$mean, rh_parcels_SA$mean)[-c(1,202)][201:400]), schaefer_atlas_region_names_rh))
num_of_sig_age_edges_lh=as.list(setNames(c(NA,edge_vector[1:200]), schaefer_atlas_region_names_lh))
num_of_sig_age_edges_rh=as.list(setNames(c(NA, edge_vector[201:400]), schaefer_atlas_region_names_rh))
#colormap
colFn_diverging = colorRampPalette(rev(c("white","orange", "red")));makecmap_options=list('colFn'=colFn_diverging)
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  num_of_sig_age_edges_lh, 
                             num_of_sig_age_edges_rh, makecmap_options = makecmap_options, "inflated", views="t4", draw_colorbar = T, rgloptions = rgloptions, rglactions = NULL)
```


## Age-squared on SA from Freesurfer--masked significant clusters, by vertex
```{age on SA quadratic by vertex}
#load age on CT from FS
lh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/lh_area_agesq_age_sex_t1rating_fwhm10_n89/lh-Avg-area-age_sq-Cor/cache.th23.abs.sig.masked.mgh") #voxel-wise corrected?
rh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/rh_area_ageagesqsext1rating_fwhm10_n89/rh-Avg-area-age_sq-Cor/cache.th23.abs.sig.masked.mgh")
#write to csv for matlab
write.csv(lh,"~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/spin_tests/lh_age_sq_on_SA_from_FS.csv");write.csv(rh,"~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/spin_tests/rh_age_sq_on_SA_from_FS.csv")

#Then run the script spin_test_vertex_wise.m!
```
