---
title: "CBPD Variability"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(matrixStats)
library(stats)
library(parallel)
library(lm.beta)
library(packrat)
library(summarytools)
library(visreg)
library(mgcv)
library(RLRsim)
library(GGally)
library(stringr)
library(tidyverse)
library(data.table)
library(psych)
#load the .RDS file
pipeline='nogsr_spkreg_fd0.5dvars1.75_drpvls'
pipeline="nogsr_spkreg_fd1.25dvars2_drpvls"
pipeline='gsr_spkreg_fd0.5dvars1.75_drpvls'
network_dir=paste0("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/",pipeline)

load(paste0(network_dir,"/CBPD_n92_schaefer400_allruns.Rdata"))
```

```{r brain plotting setup, include=FALSE, echo=FALSE}
library(fsbrain) #this may not work if you're editing the script directly on the cluster...
library(freesurferformats)
#rearrange the order of the brains in the T9 view of fsbrain
source("~/Documents/tools/fsbrain_fix_t9.R")
environment(brainview.t9) <- asNamespace('fsbrain')
assignInNamespace("brainview.t9", brainview.t9, ns = "fsbrain")
subjects_dir = "/Users/utooley/Documents/tools/CBIG/stable_projects/brain_parcellation/Schaefer2018_LocalGlobal/Parcellations/FreeSurfer5.3/";
subject_id = 'fsaverage';       # for functions which use one subject only
atlas='Schaefer2018_400Parcels_7Networks_order'

#Get the Schaefer atlas region names
schaefer_atlas_region_names_lh = get.atlas.region.names(atlas, template_subjects_dir = subjects_dir,template_subject=subject_id, hemi="lh");
schaefer_atlas_region_names_rh = get.atlas.region.names(atlas, template_subjects_dir = subjects_dir,template_subject=subject_id, hemi="rh");

#set output dir for saving images
output_image_directory="~/Documents/projects/in_progress/within_between_network_conn_CBPD/output/figures/brains/"
  
#Set RGL defaults, larger window and how to make snapshots!
rgloptions=list("windowRect"=c(50,50,1000,1000));
```

## Load data
```{r load parcel data, include=FALSE, echo=FALSE}
sub_parcel_ts <- list()
timeseries_dir=paste0("/cbica/projects/cbpd_main_data/CBPD_bids_crosssectional/derivatives/xcpEngine_", pipeline,"/")
#make a huge dataframe of subjects x edges
#except should pull only usable runs!! And need to calculate across runs to account for the averaged matrix across runs!
list <- main_filt %>% filter(ID %in% main_unique$ID) %>% select(ID,base_ID,run,longitudinal) #pull all runs from only kids who are in the unique main sample (1 timepoint/kid)
for (subject in list$ID){
  print(subject)
  runs <- list[list$ID==subject,"run"]
  x <- matrix(NA,nrow=1,ncol = 400)
  for (run in runs){
    tsfile=paste0(timeseries_dir,subject,"/",run,"/fcon/schaefer400/",subject,"_",run,"_schaefer400_ts.1D")
   if(file.exists(tsfile)){
    x <- rbind(x,as.matrix(read.table(file =tsfile, header = F)))
   }
   else{
    tsfile=paste0(timeseries_dir,subject,"/",run,"/fcon/schaefer400x7/",subject,"_",run,"_schaefer400x7_ts.1D")
     x <- rbind(x,as.matrix(read.table(file =tsfile, header = F)))
   }
  }
sub_parcel_ts[[subject]] <- na.omit(x)
}
#now have a list with each subject functional timeseries across runs saved as x timepoints by 400 parcels.
save(sub_parcel_ts,file = "~/Dropbox/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/n92_schaefer400_timeseries_across_runs.Rdata")#save it out
load("~/Dropbox/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/n92_schaefer400_timeseries_across_runs.Rdata")#load it
```


## Estimate a parcelwise variability metric
```{r calculate a metric, include=FALSE, echo=FALSE}
name="mssd"
metric= #Change this to examine different metrics
myfun <- function(x) {  
  apply(x,2,mssd)
}
subjectwise_sd <- t(sapply(sub_parcel_ts, myfun))
#plot mean
median_sd <- apply(subjectwise_sd,2,median)
median_lh=as.list(setNames(c(NA,median_sd[1:200]), schaefer_atlas_region_names_lh));median_rh=as.list(setNames(c(NA,median_sd[201:400]), schaefer_atlas_region_names_rh))
colormap= colorRampPalette(RColorBrewer::brewer.pal(9, name="PuOr"));makecmap_options=list('colFn'=colormap)
rglactions=list("snapshot_png"=paste0(output_image_directory,"median_",name,".png"), "trans_fun"=limit_fun(0,400)) #this limits the range of data displayed to 10-1000
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  median_lh, 
                            median_rh, makecmap_options = makecmap_options, "inflated", views="t4", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)
#look at relationship with age
#whole-brain average
subjectwise_sd=data.frame(subjectwise_sd,rowMeans(subjectwise_sd)) %>% rename(.,"mean_sd"="rowMeans.subjectwise_sd.")
subjectwise_sd$ID <- dimnames(subjectwise_sd)[[1]]
subjectwise_sd<- left_join(main_unique,subjectwise_sd, by= "ID")
summary(lm(mean_sd~age_scan+male+fd_mean_avg+avgweight+totalSizet, data=subjectwise_sd))
visreg(lm(mean_sd~age_scan+male+fd_mean_avg+avgweight+totalSizet, data=subjectwise_sd))
exactRLRT(gamm(mean_sd~s(age_scan)+male+fd_mean_avg+avgweight+totalSizet, data=subjectwise_sd, method = "REML")$lme)
visreg(gam(mean_sd~s(age_scan)+male+fd_mean_avg+avgweight+totalSizet, data=subjectwise_sd, method = "REML"))
#parcelwise
parcel_sd_pvals<- lapply(names(subjectwise_sd[,1646:2045]), function(x) { summary(lm(as.formula(paste0(x,"~age_scan+male+fd_mean_avg+avgweight+totalSizet")), data=subjectwise_sd))$coef[2,4]})
parcel_sd_pvals <- unlist(parcel_sd_pvals)
parcel_sd_pvals_fdr <- cbind(parcel_sd_pvals,p.adjust(parcel_sd_pvals,method = "fdr"))
#get age betas
parcel_sd_betas<- lapply(names(subjectwise_sd[,1646:2045]), function(x) { lm.beta(lm(as.formula(paste0(x,"~age_scan+male+fd_mean_avg+avgweight+totalSizet")), data=subjectwise_sd))$standardized.coefficients[[2]]})
parcel_sd_betas <- unlist(parcel_sd_betas)

save(subjectwise_sd, parcel_sd_pvals_fdr,parcel_sd_betas, file=paste0("~/Dropbox/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/n92_parcel_",name,".Rdata"))
```

## Metrics plot
```{r plot a metric, include=FALSE, echo=FALSE}
name="parcel_mssd_pvals"
to_plot=parcel_sd_pvals_fdr[,2] #Change this to plot different things
to_plot=ifelse(parcel_sd_pvals_fdr[,1] <0.05,parcel_sd_betas,NA)

lh=as.list(setNames(c(NA,to_plot[1:200]), schaefer_atlas_region_names_lh)) #this has the medial wall in it.
rh=as.list(setNames(c(NA,to_plot[201:400]), schaefer_atlas_region_names_rh))
#colormap
colFn_diverging = colorRampPalette(rev(RColorBrewer::brewer.pal(9, name="RdBu")));makecmap_options=list('colFn'=colFn_diverging)
rglactions=list("snapshot_png"=paste0(output_image_directory,name,".png"))
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  lh, 
                             rh, makecmap_options = makecmap_options, "inflated", views="t4", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)

```

## Entropy
Not sure if the Hurst exponent can be succesfully applied to our censored data--Dani thinks not since relies on frequency information.

The timeseries data in the networks is the length of the scan - the number of censored timepoints. The timepoints are interpolated prior to bandpass filtering, and then removed again from the timeseries (therefore there are discontinuities in the timeseries).
```{r Entropy, include=FALSE, echo=FALSE}
library(pracma)
library(parallel)
x <- sub_parcel_ts$`sub-CBPD0002`
l <- sample_entropy(x[,1],edim=2, r=0.7)
name="sample entropy"
metric= #Change this to examine different metrics
myfun <- function(x) {  
  apply(x,2,sample_entropy, edim=2, r=2, tau=1)
}
# subjectwise_metric <- mclapply(sub_parcel_ts, myfun, mc.cores = 3)
# subjectwise_metric <- do.call("rbind", subjectwise_metric)

save(subjectwise_metric,file = "~/Dropbox/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/n92_schaefer400_sample_entropy_m2_r2_t1.Rdata")#save it out
#load it
load("~/Dropbox/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/n92_schaefer400_sample_entropy_m2_r2_t1.Rdata")

#take out the Infs in the dataframe, replace with NA, so that there aren't huge outliers when plotting
subjectwise_metric[] <- apply(subjectwise_metric, 2, FUN =  function(i) if(is.numeric(i)) ifelse(is.infinite(i), NA, i) else i)
#Plot parcelwise median
median_sd <- apply(subjectwise_metric,2,median, na.rm=T);hist(median_sd)
median_lh=as.list(setNames(c(NA,median_sd[1:200]), schaefer_atlas_region_names_lh));median_rh=as.list(setNames(c(NA,median_sd[201:400]), schaefer_atlas_region_names_rh))
colormap= colorRampPalette(RColorBrewer::brewer.pal(9, name="PuOr"));makecmap_options=list('colFn'=colormap)
rglactions=list("snapshot_png"=paste0(output_image_directory,"median_",name,".png"), "trans_fun"=limit_fun(0,400)) #this limits the range of data displayed to 10-1000
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  median_lh, 
                            median_rh, makecmap_options = makecmap_options, "inflated", views="t4", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)
#look at relationship with age
#subjectwise_metric <- subjectwise_metric %>% mutate(global_mean_metric=rowMedians(as.matrix(.),na.rm=T))#make whole-brain subjectwise average
subjectwise_metric <- data.frame(subjectwise_metric,rowMedians(subjectwise_metric, na.rm = T)) %>% rename(global_mean_metric=rowMedians.subjectwise_metric..na.rm...T.)
hist(subjectwise_metric$global_mean_metric)
#take out the 2 outliers
#subjectwise_metric_filt <- subjectwise_metric %>% filter(.,global_mean_metric>1)
subjectwise_metric$ID <- dimnames(subjectwise_metric)[[1]]
subjectwise_metric<- left_join(main_unique,subjectwise_metric, by= "ID")
summary(lm(global_mean_metric~age_scan+male+fd_mean_avg+avgweight+totalSizet, data=subjectwise_metric))
visreg(lm(global_mean_metric~age_scan+male+fd_mean_avg+avgweight+totalSizet, data=subjectwise_metric))
exactRLRT(gamm(global_mean_metric~s(age_scan)+male+fd_mean_avg+avgweight+totalSizet, data=subjectwise_metric, method = "REML")$lme)
visreg(gam(global_mean_metric~s(age_scan)+male+fd_mean_avg+avgweight+totalSizet, data=subjectwise_metric, method = "REML"))
#parcelwise
parcel_sd_pvals<- lapply(names(subjectwise_metric[,1646:2045]), function(x) { summary(lm(as.formula(paste0(x,"~age_scan+male+fd_mean_avg+avgweight+totalSizet")), data=subjectwise_metric))$coef[2,4]})
parcel_sd_pvals <- unlist(parcel_sd_pvals)
parcel_sd_pvals_fdr <- cbind(parcel_sd_pvals,p.adjust(parcel_sd_pvals,method = "fdr"))
#get age betas
parcel_sd_betas<- lapply(names(subjectwise_metric[,1646:2045]), function(x) { lm.beta(lm(as.formula(paste0(x,"~age_scan+male+fd_mean_avg+avgweight+totalSizet")), data=subjectwise_metric))$standardized.coefficients[[2]]})
parcel_sd_betas <- unlist(parcel_sd_betas)

save(subjectwise_metric, parcel_sd_pvals_fdr,parcel_sd_betas, file=paste0("~/Dropbox/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/n92_parcel_",name,".Rdata"))

```

## Entropy plot age pvals
```{r plot sample entropy metric, include=FALSE, echo=FALSE}
name="parcel_sampEn_pvals"
to_plot=parcel_sd_pvals_fdr[,1] #Change this to plot different things
to_plot=ifelse(parcel_sd_pvals_fdr[,2] <0.05,parcel_sd_betas,NA)

lh=as.list(setNames(c(NA,to_plot[1:200]), schaefer_atlas_region_names_lh)) #this has the medial wall in it.
rh=as.list(setNames(c(NA,to_plot[201:400]), schaefer_atlas_region_names_rh))
#colormap
#colFn_diverging = colorRampPalette(rev(c("white","white","pink","red")));makecmap_options=list('colFn'=colFn_diverging)
colFn_diverging = colorRampPalette(rev(RColorBrewer::brewer.pal(9, name="RdBu")));makecmap_options=list('colFn'=colFn_diverging)
rglactions=list("snapshot_png"=paste0(output_image_directory,name,".png"), 'shift_hemis_apart'=TRUE)
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  lh, 
                             rh, makecmap_options = makecmap_options, "inflated", views="t9", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)

```

## Spin test of the entropy and edge age effect maps

Before running this code block, use the MATLAB function `centroid_extraction_sphere.m` to get the centroid coordinates on the Freesurfer sphere of each of the parcels in the Schaefer400 parcellation. That is needed as input to these functions.

```{r spin test edge and entropy age effects}
source("~/Documents/tools/rotate_parcellation/R/rotate.parcellation.R")
source("~/Documents/tools/rotate_parcellation/R/perm.sphere.p.R")
library(matrixStats) #otherwise get rowMins error
#read in centroids of the Schaefer400 parcels
lh_centroids <- as.matrix(read.csv("~/Documents/tools/parcellations/lh.Schaefer400_7Nets_fsaverage6.centroids.csv", header = F));rh_centroids <- as.matrix(read.csv("~/Documents/tools/parcellations/rh.Schaefer400_7Nets_fsaverage6.centroids.csv", header = F))
#SHOULD BE MASKING OUT MEDIAL WALL? Assuming that is first centroid for each
lh_centroids <- lh_centroids[-1,];rh_centroids <- rh_centroids[-1,];

#load back in edge age effects
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/edgewise_age_effects_all_cov.Rdata")
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400)
edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1] #take uncorrected p-values for now
edge_age_pvals_mat <- t(edge_age_pvals_mat)#copy lower triangle to upper triangle
#load rotations
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/rotations_schaefer400_fsaverage6_10000x.Rdata")
#load the sample entropy pvals
load("~/Dropbox/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/n90_parcel_sample entropy.Rdata")

#Spin tests
pvalues=c(0.01,0.001,0.0001)
for (pvalue in pvalues){
  print(pvalue)
indices <- which(edge_age_pvals_mat<pvalue, arr.ind = T) #indices of edges that have age effects  below a pval
l <- data.frame(table(indices)) #for each parcel, how many age-significant edges does it have at a given pval thresh
values <- vector(mode = "double", 400)
for (i in 1:400){
values[as.numeric(as.character(l$indices[i]))] <- l$Freq[i]#replace the indices in values with the num of sig edges from that parcel in the table
}
#maps to compare
edge_vector=values
#other map of entropy values or pvals
parcel_metric_pvals_thresh <- ifelse(parcel_sd_pvals_fdr[,1]<0.05,1-parcel_sd_pvals_fdr[,1],0)
metric_vector=1-parcel_sd_pvals_fdr[,1] #all the pvalues
#SA_vector=round(SA_vector,2) #need to round?

#rotations<- rotate.parcellation(lh_centroids,rh_centroids,10000)
print("median SampEn")
print(perm.sphere.p(edge_vector,as.numeric(median_sd), rotations, "pearson"))
print("metric pvals vector")
print(perm.sphere.p(edge_vector,metric_vector, rotations, "pearson"))
print("metric pvals thresholded")
print(perm.sphere.p(edge_vector,parcel_metric_pvals_thresh, rotations, "pearson"))
}
#save rotations so don't have to do
save(rotations,file= "~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/rotations_schaefer400_fsaverage6_10000x.Rdata")
```

## Multiscale entropy?
```{multiscale entropy calculation}
library(CGManalyzer)
library(viridis)
#load timeseries across runs
load("~/Dropbox/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/n90_schaefer400_timeseries_across_runs.Rdata")#load it
x <- sub_parcel_ts$`sub-CBPD0002`
l <- MSEbyC.fn(x[,1], rMin = 0.15, rMax = 1)
#MSEplot.fn(Scale = c(1:10), l, MSE = l, )
ggplot(data = l, mapping = aes(x=Scale, y=SampleEntropy,group=as.factor(r), color=as.factor(r)))+geom_point()+geom_line()+scale_color_viridis_d()


name="sample entropy"
metric= #Change this to examine different metrics
myfun <- function(x) {  
  apply(x,2,sample_entropy, edim=2, r=2, tau=1)
}
sampleEntropy()
	
MSMVSampEn()
```

## State analysis?

Maybe need to winsorize timeseries to 4 SD above mean--ask Max, along with subject inclusion criteria?

## Intrinsic timescales of BOLD
Done in MATLAB, MATLAB scripts called parcel_intrinsic_timescale.
Code below is to write out a subject list for use in MATLAB. 

```{intrinsic timescales subject list}
pipeline='gsr_spkreg_fd0.5dvars1.75_drpvls'
network_dir=paste0("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/",pipeline)
load(paste0(network_dir,"/CBPD_n92_schaefer400_allruns.Rdata"))
#pull only usable runs and calculate across runs to account for the averaged matrix across runs!
list <- main_filt %>% filter(ID %in% main_unique$ID) %>% select(ID,base_ID,run,longitudinal) #pull all runs from only kids who are in the unique main sample (1 timepoint/kid)
write.csv(list, file ="~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/subjectData/n92_subjlist_for_timescales.csv")
write.csv(list, file ="/cbica/home/tooleyu/projects/in_progress/within_between_network_conn_CBPD/data/subjectLists/n92_subjlist_for_timescales.csv")
```

```{intrinsic timescale plot + analyse}
library(R.matlab)#load parcel average
x <- readMat(paste0(network_dir,"/n92_schaefer400_timescales_censor_block_parcel_group.mat"));parcel_timescale <- x$hwhm
name="intrinsic_timescale_censor_block"
#Plot parcelwise mean
median_sd <- parcel_timescale
median_lh=as.list(setNames(c(NA,median_sd[1:200]), schaefer_atlas_region_names_lh));median_rh=as.list(setNames(c(NA,median_sd[201:400]), schaefer_atlas_region_names_rh))
colormap= colorRampPalette(RColorBrewer::brewer.pal(9, name="PuOr"));makecmap_options=list('colFn'=colormap)
colormap= colorRampPalette(c("#00007F", "blue", "#007FFF", "cyan","#7FFF7F", "yellow", "#FF7F00", "red", "#7F0000"));makecmap_options=list('colFn'=colormap)
rglactions=list("snapshot_png"=paste0(output_image_directory,"median_",name,".png")) #this limits the range of data displayed to 10-1000
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  median_lh, 
                            median_rh, makecmap_options = makecmap_options, "inflated", views="t4", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)

#look at relationship with age
subjectwise_metric <- read.csv(paste0(network_dir,"/n92_schaefer400_timescales_censor_block_parcel_subjectwise.csv")); colnames(subjectwise_metric) <- c("ID",paste0("V",rep(1:400)))
subjectwise_metric <- data.frame(subjectwise_metric) %>% mutate(global_mean_metric = select(., -matches("ID")) %>% rowMeans(.))#make whole-brain subjectwise average
hist(subjectwise_metric$global_mean_metric)
#load age data
load(paste0(network_dir,"/CBPD_n92_schaefer400_allruns.Rdata"))
subjectwise_metric$ID <- trimws(subjectwise_metric$ID) #issues merging because MATLAB added whitespace
subjectwise_metric<- left_join(main_unique,subjectwise_metric, by= "ID")
summary(lm(global_mean_metric~age_scan+male+fd_mean_avg+avgweight+totalSizet, data=subjectwise_metric))
visreg(lm(global_mean_metric~age_scan+male+fd_mean_avg+avgweight+totalSizet, data=subjectwise_metric))
exactRLRT(gamm(global_mean_metric~s(age_scan)+male+fd_mean_avg+avgweight+totalSizet, data=subjectwise_metric, method = "REML")$lme)
visreg(gam(global_mean_metric~s(age_scan)+male+fd_mean_avg+avgweight+totalSizet, data=subjectwise_metric, method = "REML"))
#parcelwise
parcel_timescale_pvals<- lapply(names(subjectwise_metric[,793:1192]), function(x) { summary(lm(as.formula(paste0(x,"~age_scan+male+fd_mean_avg+avgweight+totalSizet")), data=subjectwise_metric))$coef[2,4]})
parcel_timescale_pvals <- unlist(parcel_timescale_pvals)
parcel_timescale_pvals_fdr <- cbind(parcel_timescale_pvals,p.adjust(parcel_timescale_pvals,method = "fdr"))
#get age betas
parcel_timescale_betas<- lapply(names(subjectwise_metric[,793:1192]), function(x) { lm.beta(lm(as.formula(paste0(x,"~age_scan+male+fd_mean_avg+avgweight+totalSizet")), data=subjectwise_metric))$standardized.coefficients[[2]]})
parcel_timescale_betas <- unlist(parcel_timescale_betas)

save(subjectwise_metric, parcel_timescale_pvals_fdr,parcel_timescale_betas, file=paste0("~/Dropbox/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/n92_parcel_",name,".Rdata"))
name="parcel_timescale_censor_block_pvals_fdr"
to_plot=parcel_timescale_pvals_fdr[,1] #Change this to plot different things
to_plot=ifelse(parcel_timescale_pvals_fdr[,1] <0.05,parcel_timescale_betas,NA)

lh=as.list(setNames(c(NA,to_plot[1:200]), schaefer_atlas_region_names_lh)) #this has the medial wall in it.
rh=as.list(setNames(c(NA,to_plot[201:400]), schaefer_atlas_region_names_rh))
#colormap
colFn_diverging = colorRampPalette(rev(RColorBrewer::brewer.pal(9, name="RdBu")));makecmap_options=list('colFn'=colFn_diverging,'symm'=TRUE)
rglactions=list("snapshot_png"=paste0(output_image_directory,"/",name,",_age_pvals.png"))
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  lh, 
                             rh, makecmap_options = makecmap_options, "inflated", views="t4", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)
```