---
title: "CBPD Functional Network Results"
author: "Ursula Tooley"
date: "12/3/2020"
output:
  html_document:
    theme: united
    toc: yes
    toc_depth: 6
  pdf_document:
    toc: yes
    toc_depth: '6'
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(stats)
library(parallel)
library(lm.beta)
library(packrat)
library(summarytools)
library(visreg)
library(mgcv)
library(RLRsim)
library(GGally)
#load the .RDS file
pipeline='nogsr_spkreg_fd0.5dvars1.75_drpvls'
pipeline="nogsr_spkreg_fd1.25dvars2_drpvls"
pipeline='gsr_spkreg_fd0.5dvars1.75_drpvls'
network_dir=paste0("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/",pipeline)

load(paste0(network_dir,"/CBPD_n92_schaefer400_allruns.Rdata"))
```
## Data Descriptives

###Motion

We start with n= `r length(unique(main$ID))`. In these analyses, I used a stringent pipeline, censoring and interpolating over vols with > FD of 0.5 mm or DVARS > 1.75. Those are excluded from the timeseries used to calculate the networks used here. I excluded anyone with > 50% frames censored (following Yeo, 2011) or mean motion > 1 mm, or max motion over 10 mm, leaving us with `r length(unique(main_filt$ID))` participants, `r length(main_filt$run[main_filt$run=="run-02"])` of which have a second run. 

The dataframe below shows all runs for subjects who meet this criteria. At the moment, I'm just examining the first run, not averaging in those who have a second run.

```{r Filtered Motion Summary,echo=FALSE}
motion <- select(main_filt, age_scan, run, fd_mean,pctSpikesFD:relMaxRMSMotion)
print(dfSummary(motion), method = 'render')
```

###SES
```{r SES of Sample Summary,echo=FALSE, results='hold'}
ses <- select(main_unique, male, race2,ethnicity,has_diagnoses, parent1_edu:parent2_edu, income_median:monthslive_iflostincome, childaces_sum_ignorenan) %>% 
print(dfSummary(ses), method = 'render')
```

## Age and measures of network segregation

We find that overall, all measures of network segregation significantly increase with age in our dataset, with remarkable consistency. We examined within-network connectivity, between network connectivity, system segregation (as calculated in Chan et al. 2018), the modul_avgarity quality index, and the participation coefficient (summed across negative and positive weights). 

We controlled for sex, mean framewise displacement across both scans weighted by length of scan, the number of total volumes a participant had, and the average weight of the functional network across both scans (weighted by amount of good data per scan). We previously also controlled for the percent of volumes censored for FD spikes in the data, but Allyson suggested taking out 4.4.21.

```{r models of segregation, echo=FALSE, include=FALSE, results='hide'}
#look at mean within and between with age
#lm_within_sys_age <- lm(mean_within_sys~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet, data=main_unique)
lm_within_sys_age <- lm(mean_within_sys~age_scan+male+fd_mean_avg+avgweight+totalSizet, data=main_unique)
summary(lm_within_sys_age)
lm_between_sys_age <- lm(mean_between_sys~age_scan+male+fd_mean_avg+avgweight+totalSizet, data=main_unique)
summary(lm_between_sys_age)
lm_segreg_age<- lm(system_segreg~age_scan+male+fd_mean_avg+avgweight+totalSizet, data=main_unique)
summary(lm_segreg_age)
lm_modul_avg_age <- lm(modul_avg~age_scan+male+fd_mean_avg+avgweight+totalSizet, data=main_unique)
summary(lm_modul_avg_age)
lm_part_coef_age <- lm(part_coef~age_scan+male+fd_mean_avg+avgweight+totalSizet, data=main_unique)
summary(lm_part_coef_age)
lm_num_comms_age <- lm(num_comms_modul_avg~age_scan+male+fd_mean_avg+avgweight+totalSizet, data=main_unique)
summary(lm_num_comms_age)

```

```{r plots of segregation, echo=FALSE, include=TRUE, results='hide'}
par(mfrow=c(2,3))
visreg(lm_between_sys_age,"age_scan", main="Mean between-system connectivity", ylab="", xlab="Age at scan (years)")
visreg(lm_within_sys_age,"age_scan", main= "Mean within-system connectivity", ylab="", xlab="Age at scan (years)")
visreg(lm_segreg_age,"age_scan", main="Average segregation", ylab="", xlab="Age at scan (years)")
visreg(lm_modul_avg_age,"age_scan", main="Modularity quality index Q", ylab="", xlab="Age at scan (years)")
visreg(lm_part_coef_age,"age_scan", main="Average participation coefficient", ylab="", xlab="Age at scan (years)")
visreg(lm_num_comms_age,"age_scan")
```

The number of communities detected using modul_avgarity maximization on this data does not significantly decrease with age (each subject ran 100x, averaged Q and *k*, range in k is `r range(main_unique$num_comms_modul_avg)`).

###Non-linear effects of age?

We also used restricted least ratio tests to test for the presence of non-linearity in our data. As you can see in the plots below, which use GAMs, most measures are linear and look no different from the linear models above.
```{r gam models of segregation, echo=FALSE, include=FALSE, results='hide'}
#look at mean within and between with age
gam_within_sys_age <- gam(mean_within_sys~s(age_scan)+male+fd_mean_avg+avgweight+totalSizet, data=main_unique)
model<- gamm(mean_within_sys~s(age_scan)+male+fd_mean+avgweight+size_t, data=main_unique, method = "REML")$lme
exactRLRT(model)
gam_between_sys_age <- gam(mean_between_sys~s(age_scan)+male+fd_mean+avgweight+size_t, data=main_unique)
model<- gamm(mean_between_sys~s(age_scan)+male+fd_mean+avgweight+size_t, data=main_unique)$lme
exactRLRT(model)
gam_segreg_age<- gam(system_segreg~s(age_scan)+male+fd_mean+avgweight+size_t, data=main_unique)
model<- gamm(system_segreg~s(age_scan)+male+fd_mean+avgweight+size_t, data=main_unique)$lme
exactRLRT(model)
gam_modul_avg_age <- gam(modul_avg~s(age_scan)+male+fd_mean+avgweight+size_t, data=main_unique)
model<- gamm(modul_avg~s(age_scan)+male+fd_mean+avgweight+size_t, data=main_unique)$lme
exactRLRT(model)
gam_part_coef_age <- gam(part_coef~s(age_scan)+male+fd_mean+avgweight+size_t, data=main_unique)
model<- gamm(part_coef~s(age_scan)+male+fd_mean+avgweight+size_t, data=main_unique)$lme
exactRLRT(model)
gam_clustco_age <- gam(avgclustco_both~s(age_scan)+male+fd_mean+avgweight+size_t, data=main_unique)
model<- gamm(part_coef~s(age_scan)+male+fd_mean+avgweight+size_t, data=main_unique)$lme
exactRLRT(model)
```

```{r gam plots of segregation, echo=FALSE, include=TRUE, results='hide'}
par(mfrow=c(2,3))
visreg(gam_between_sys_age,"age_scan",main=names(model.frame(gam_between_sys_age))[1])
visreg(gam_within_sys_age,"age_scan", main=names(model.frame(gam_within_sys_age))[1])
visreg(gam_segreg_age,"age_scan",  main=names(model.frame(gam_segreg_age))[1])
visreg(gam_modul_avg_age,"age_scan", main=names(model.frame(gam_modul_avg_age))[1])
visreg(gam_part_coef_age,"age_scan", main=names(model.frame(gam_part_coef_age))[1])
```

Tests of non-linearity confirmed that no non-linear effects are present. The wiggly participation coefficient line is just over-fitting.

## Which systems are driving this effect?

We fit the same model, controlling for sex, mean framewise displacement, the number of volumes a participant had, and the average weight of the functional network, to between- and within-system connectivity for each of the Yeo 7 systems. 

We find the strongest effects are in the default mode system, between default and attentional networks.
```{r lm plots, echo=FALSE, include=TRUE, results='hide',fig.show='hold', out.width='33.33%', fig.align='default'}
networks_age_pvals_fdr #FDR-corrected
lm_sys1to3<- lm(sys1to3~age_scan+male+fd_mean_avg+avgweight+totalSizet, data=main_unique)
lm_sys3to7<- lm(sys3to7~age_scan+male+fd_mean_avg+avgweight+totalSizet, data=main_unique)
lm_sys4to7<- lm(sys4to7~age_scan+male+fd_mean_avg+avgweight+totalSizet, data=main_unique)
# ############## investigating plotting options #############
# crPlots(lm_sys4to7, "age_scan")
# plot(main_unique$age_scan, (lm_sys4to7$fitted.values))
# 
# library(car)
#avPlots(lm_sys4to7, "age_scan")
# sys4to7<- ((rstandard(lm(sys4to7~male+fd_mean+avgweight+pctSpikesFD+size_t, data=main_unique)))*rmse(lm_sys4to7, main_unique))+ mean(main_unique$sys4to7)
# age <- ((rstandard(lm(age_scan~male+fd_mean+avgweight+pctSpikesFD+size_t, data=main_unique)))*rmse(lm_sys4to7, main_unique)) + mean(main_unique$age_scan)
# xxx <- data.frame(sys4to7,age)
# l <- lm(sys4to7~age, data=xxx)
# visreg(l)
# plot(xxx$sys4to7~xxx$age)
# plot(lm_sys)
visreg(lm_sys1to3,"age_scan",main="VIS to DAN", ylab="", xlab="Age at scan (years)")
visreg(lm_sys3to7,"age_scan", main="DMN to DAN",ylab="", xlab="Age at scan (years)")
visreg(lm_sys4to7,"age_scan",  main="DMN to VAN",ylab="", xlab="Age at scan (years)")
# 
# crPlots(lm_sys4to7)
# visreg(lm_sys4to7,"age_scan",band=FALSE, gg=TRUE)+geom_smooth()+theme_classic()
```

### Plots for within-system connectivity
To scatter around the Yeo networks.
```{r lm plots within, echo=FALSE, include=TRUE, results='hide',fig.show='hold', out.width='33.33%', fig.align='default'}
networks <- dplyr::select(main_unique, sys1to1, sys2to2, sys3to3, sys4to4, sys5to5, sys6to6,sys7to7) %>% ungroup()
nets <- colnames(networks[-1])
#look at non-linear interaction between age and envSES 
for (net in nets){
  name<-paste0("lm_",net)
  formula<-formula(paste0(net, '~age_scan+male+fd_mean+avgweight+totalSizet'))
  assign(name, lm(formula, data=main_unique))
  #p_val[net] <- summary(name)$coefficients[2,4]
  summary(get(name))
  visreg(get(name),'age_scan', xlab = "Age (years)", ylab="")
} 
```

## System-level effects to creativity

Allyson asks whether the segregation of def vs. attn nets is associated with reduced pretend play, reduced (CFG-), or coded pretend play in PCIT.

```{r lm plots, echo=FALSE, include=TRUE, results='hide',fig.show='hold', out.width='33.33%', fig.align='default'}
networks_age_pvals_fdr #FDR-corrected

#Home literacy and numeracy questionnaire
lm_sys3to7<- lm(sys3to7~age_scan+male+fd_mean_avg+avgweight+totalSizet+litnum_freq_play_avg, data=main_unique)
lm_sys4to7<- lm(sys4to7~age_scan+male+fd_mean_avg+avgweight+totalSizet+litnum_freq_play_avg, data=main_unique)
summary(lm(litnum_freq_play_avg~age_scan+male, data=main_unique))
summary(lm_sys3to7)
summary(lm_sys4to7)
visreg(lm_sys3to7,"litnum_freq_play_avg", main="DMN to DAN",ylab="", xlab="litnum_freq_play_avg")

lm_sys3to7<- lm(sys3to7~age_scan+male+fd_mean_avg+avgweight+totalSizet+litnum_freq_pretend_avg, data=main_unique)
lm_sys4to7<- lm(sys4to7~age_scan+male+fd_mean_avg+avgweight+totalSizet+litnum_freq_pretend_avg, data=main_unique)
summary(lm(litnum_freq_pretend_avg~age_scan+male, data=main_unique))
summary(lm_sys3to7)
summary(lm_sys4to7)#litnum freq play and freq pretend play is associated with 3 to 7
visreg(lm_sys3to7,"litnum_freq_pretend_avg", main="DMN to DAN",ylab="", xlab="litnum_freq_pretend_avg")


#CFG measures
cfg_measures=main_unique %>% select(total.play.time:max.Δt...min.) %>% names();cfg_measures=cfg_measures[-1] #- baseID
cfg_measures
for (measure in cfg_measures){
  meas=main_unique %>% ungroup %>% select(measure) %>% pull()
  print(meas)
  hist(as.numeric(meas), main=measure)
  print(summary(meas))
}

#Julia re: PCIT coded pretend play, or start from child_persistence_seconds
pcit_measures=main_unique %>%ungroup %>% select(kid_a_play_coder1:totalDuration.adult_p_play_avg) %>% names();
pcit_measures
for (measure in pcit_measures){
  meas=main_unique %>% ungroup %>% select(measure) %>% pull()
  print(meas)
  hist(as.numeric(meas), main=measure)
  print(summary(meas))
}


# crPlots(lm_sys4to7)
# visreg(lm_sys4to7,"age_scan",band=FALSE, gg=TRUE)+geom_smooth()+theme_classic()

#bootstrap or rlm these effects to make sure?
```
None of these showed significantly non-linear effects, either. 

```{r system level FDR-corrected effects}
# Look at each column and correct for multiple comparisons
covariates="~ age_scan+male+fd_mean_avg+avgweight+totalSizet"

#make a dataframe with no repeats of net comparisons
main_unique <- dplyr::select(main_unique, -c(sys2to1,sys3to1,sys3to2,sys4to1,sys4to2,sys4to3,sys5to1,sys5to2,sys5to3,sys5to4,sys6to1,sys6to2,sys6to3,sys6to4,sys6to5,sys7to1,sys7to2,sys7to3,sys7to4,sys7to5,sys7to6))
#run and compare for multiple comparisons again
m <- mclapply(names((dplyr::select(ungroup(main_unique),sys1to1:sys7to7))), function(sys) {as.formula(paste(sys, covariates, sep=""))},mc.cores=2)
networks_Age_pvals <- mclapply(m, function(sys) { summary(lm(formula = sys,data=main_unique))$coefficients[2,4]},mc.cores=1)
networks_Age_pvals <- as.data.frame(networks_Age_pvals)
networks_Age_pvals <- t(networks_Age_pvals)
networks_Age_pvals <- as.data.frame(networks_Age_pvals)
#bonferroni correct
networks_Age_pvals_fdr <- p.adjust(networks_Age_pvals$V1, method="fdr")
networks_age_pvals_fdr <- data.frame(networks_Age_pvals_fdr,names((dplyr::select(ungroup(main_unique),sys1to1:sys7to7))))
colnames(networks_age_pvals_fdr) <- c("pvalue", "network")
#FDR correction shows DMN to attentional networks and visual to dorsal attention is marginal.
print(networks_age_pvals_fdr)

```

Effects on default mode connectivity survive FDR correction across the tests conducted, with DMN-VAN *p_fdr*=`r networks_age_pvals_fdr$pvalue[networks_age_pvals_fdr$network=="sys3to7"]` and DMN-DAN *p_fdr*= `r networks_age_pvals_fdr$pvalue[networks_age_pvals_fdr$network=="sys4to7"]`. Vis-DAN *p_fdr*= `r networks_age_pvals_fdr$pvalue[networks_age_pvals_fdr$network=="sys1to3"]`.

## Longitudinal data

### Longitudinal data descriptives

We have `r sum(main_filt$longitudinal_visit_num==2)` 
```{r longitudinal descriptives}
#melt data
main_filt_long <- dplyr::select(main_filt, c(ID:record_id.y,date_scan, date_behav, age_scan,male,fd_mean_avg,avgweight,pctVolsCensored,totalSizet,race2,ethnicity, longitudinal_visit_num,base_ID, part_coef))
#need to filter out only the first datapoint from each timepoint, since the network data is repeated across multiple runs at each timepoint
#to see why -> main_filt %>% select(base_ID,longitudinal_visit_num,sys1to1)
main_long_only <- main_filt_long %>% group_by(base_ID, longitudinal_visit_num) %>% filter(row_number() == 1)
main_long_only %>% select(base_ID,longitudinal_visit_num,sys1to1) #now has one set of network stats from each timepoint for each subject
table(main_long_only$longitudinal_visit_num)

#get gaps between visits
main_long_only<- main_long_only %>% group_by(base_ID) %>% mutate(diffageT1toT2=nth(age_scan,2)-first(age_scan),
                                                diffageT2toT3=nth(age_scan,3)-nth(age_scan,2)) %>% ungroup()
#Summary in months
main_long_only %>% select(diffageT1toT2) %>%  summarise(.,min=min(diffageT1toT2*12, na.rm=T), max=max(diffageT1toT2*12, na.rm=T))
main_long_only %>% select(diffageT2toT3) %>%  summarise(.,min=min(diffageT2toT3*12, na.rm=T), max=max(diffageT2toT3*12, na.rm=T))
```

We have `r sum(main_long_only$longitudinal_visit_num==2)` T2 visits and `r sum(main_long_only$longitudinal_visit_num==3)` T3 visits.

```{r longitudinal global effects with age}
library(nlme)
library(lme4)
library(lmerTest) #this will provide p-values

measures=c("mean_within_sys","mean_between_sys", "system_segreg", "modul_avg", "part_coef", "avgclustco_both")
for (meas in measures){
  print(meas)
  name<-paste0("lm_", meas,"_age")
  formula<-formula(paste0(meas,'~scale(age_scan)+male+scale(fd_mean_avg)+scale(avgweight)+scale(totalSizet)+scale(pctVolsCensored)+(1|base_ID)'))
  assign(name, lmer(formula,data=main_long_only))
  print(summary(get(name)))
  print(get(name))
}
#within, between, system segreg and part coef are singular, use lm instead 
#clustco and modul are not singular
  
#Without the random effect for subject, for those models that don't converge, the fixed effects with lm are the same as those using lmer, Bart suggests using lm instead
lm_within_sys_age <- lm(mean_within_sys~age_scan+male+fd_mean+avgweight+pctVolsCensored+totalSizet, data=main_long_only)
summary(lm_within_sys_age) 
lm_within_sys_age

lm_between_sys_age <- lm(mean_between_sys~age_scan+male+fd_mean+avgweight+pctVolsCensored+totalSizet, data=main_long_only)
summary(lm_between_sys_age)
lm.beta(lm_between_sys_age)

lm_system_segreg_age <- lm(system_segreg~age_scan+male+fd_mean+avgweight+pctVolsCensored+totalSizet, data=main_long_only)
summary(lm_system_segreg_age)
lm.beta(lm_system_segreg_age)
```

### System-level effects
```{r longitudinal system-level effects with age}
lm_sys4to7_age <- lmer(sys4to7~scale(age_scan)+male+scale(fd_mean_avg)+scale(avgweight)+scale(totalSizet)+scale(pctVolsCensored)+(1|base_ID), data=main_long_only)
summary(lm_sys4to7_age)
lm_sys4to7_age 

#1to3 and 3to7 are singular, use lm
lm_sys1to3_age <- lm(sys1to3~age_scan+male+fd_mean+avgweight+pctVolsCensored+totalSizet, data=main_long_only)
summary(lm_sys1to3_age)
lm.beta(lm_sys1to3_age)

lm_sys3to7_age <- lm(sys3to7~age_scan+male+fd_mean+avgweight+pctVolsCensored+totalSizet, data=main_long_only)
summary(lm_sys3to7_age)
lm.beta(lm_sys3to7_age)
```

### Playing with plotting mixed effects
```{r plotting mixed effects}
#with sjplot
library(sjPlot)
plot_model(lm_within_sys_age,terms=c("age_scan"), type = "pred", pred.type = "re", show.data = T)

#Using ggplot to recreate 
fm2 <- lme(mean_within_sys~scale(age_scan)+male+scale(fd_mean_avg)+scale(avgweight)+scale(totalSizet)+scale(pctVolsCensored), data = main_long_only, random = ~ 1|base_ID)
summary(fm2)
fm2

fm2 <- lme(sys4to7~age_scan+male+fd_mean_avg+avgweight+totalSizet+pctVolsCensored, data = main_long_only, random = ~ 1|base_ID)

newdat <- expand.grid(male=unique(main_long_only$male),
                  age_scan=c(min(main_long_only$age_scan),
                            max(main_long_only$age_scan)),
                  fd_mean_avg=c(min(main_long_only$fd_mean_avg),
                                max(main_long_only$fd_mean_avg)),
                  avgweight=c(min(main_long_only$avgweight),
                                max(main_long_only$avgweight)),
                  totalSizet=c(min(main_long_only$totalSizet),
                                max(main_long_only$totalSizet)),
                  pctVolsCensored=c(min(main_long_only$pctVolsCensored),
                                max(main_long_only$pctVolsCensored)))
p <- ggplot(main_long_only, aes(x=age_scan, y=predict(fm2)))+
  geom_point(size=3) +
  geom_line(aes(y=predict(fm2), group=base_ID, size="Subjects")) +
  geom_line(data=newdat, aes(y=predict(fm2, level=0, newdata=newdat), size="Population")) +
  scale_size_manual(name="Predictions", values=c("Subjects"=0.5, "Population"=3)) +
  theme_bw(base_size=22)
p

tab_model(lm_within_sys_age)

#try bayesian approach?
stan_glmer

#plotting
library(lattice)
xyplot(mean_within_sys ~ age_scan | base_ID, main_long_only, aspect = "xy",
            type = c("g", "p", "r"), subset = )
       
       index.cond = function(x,y) coef(lm(y ~ x))[1])

#Using ggplot to plot the predicted datapoints (controlling)
lm_sys4to7_age <- lmer(sys4to7~age_scan+male+fd_mean+avgweight+pctVolsCensored+totalSizet+(1|base_ID), data=main_long_only)
main_long_only$pred_sys4to7 <- predict(lm_sys4to7_age)
ggplot(data=main_long_only, aes(x=age_scan, y=pred_sys4to7, group=factor(base_ID), colour="gray"), legend=FALSE) +
  geom_smooth(method=lm, se=F, fullrange=F, lty=1, size=.5, color="gray60") +
  geom_smooth(aes(group=1), method=lm, se=FALSE, fullrange=FALSE, lty=1, size=2, color="black") +
  geom_point(aes(x=age_scan,y=pred_sys4to7))+
  xlab("Age at Scan (years)") + ylab("Predicted time brushing (sec)") +
  theme_classic() +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5))
```

## Environment and Measures of Network Segregation

```{r recode race to use way Cassidy did in molar eruption paper-5-category}
main_unique$race_factor <- ifelse(main_unique$race_americanindian==1, "Multiracial_Other", ifelse(main_unique$race_asian == 1, "Asian", ifelse(main_unique$race_hawaiian==1,"Multiracial_Other", ifelse(main_unique$race_other==1, "Multiracial_Other",(ifelse(main_unique$race_black==1,  "AABlack", ifelse(main_unique$race_white==1, "White", ifelse(main_unique$race_americanindian+main_unique$race_asian+main_unique$race_black+main_unique$race_hawaiian+main_unique$race_white > 1,  "Multiracial_Other", NA))))))))
main_unique$race_factor[which(main_unique$ethnicity == "Hispanic or Latino")] <- "Hispanic"

main_replicate_unique$race_factor <- ifelse(main_replicate_unique$race_americanindian==1, "Multiracial_Other", ifelse(main_replicate_unique$race_asian == 1, "Asian", ifelse(main_replicate_unique$race_hawaiian==1,"Multiracial_Other", ifelse(main_replicate_unique$race_other==1, "Multiracial_Other",(ifelse(main_replicate_unique$race_black==1,  "AABlack", ifelse(main_replicate_unique$race_white==1, "White", ifelse(main_replicate_unique$race_americanindian+main_replicate_unique$race_asian+main_replicate_unique$race_black+main_replicate_unique$race_hawaiian+main_replicate_unique$race_white > 1,  "Multiracial_Other", NA))))))))
main_replicate_unique$race_factor[which(main_replicate_unique$ethnicity == "Hispanic or Latino")] <- "Hispanic"
```

Race: There are small significant effects of race on within- and between-system connectivity such that white and Asian kids tend to have higher within and lower between system connectivity than Black kids.

SES: No significant effects of SES (median income, ses composite of income and parental education, or parent1 education) on measures of segregation (controlling for race or not).

ACES sum: No significant effects of ACES sum on measures of segregation. However, didn't examine 3-category ACES.

For future reference, the estimates and p-values for other covariates (excluding the intercept) don't change based on the reference level of a factor (re: Allyson's concerns in Black vs. White ref category).

```{r models of segregation with ses, echo=FALSE, include=FALSE, results='hide'}
lm_within_sys_age <- lm(mean_within_sys~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+race_factor, data=main_unique)
summary(lm_within_sys_age)
lm_between_sys_age <- lm(mean_between_sys~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+race_factor, data=main_unique)
summary(lm_between_sys_age)
lm_segreg_age<- lm(system_segreg~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+race_factor, data=main_unique)
summary(lm_segreg_age)
lm_modul_avg_age <- lm(modul_avg~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+race_factor, data=main_unique)
summary(lm_modul_avg_age)
lm_part_coef_age <- lm(part_coef~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+race_factor, data=main_unique)
summary(lm_part_coef_age)

#swap out race2 for income_median, parent1_edu, ses_composite, or childaces_sum_ignorenan
lm_within_sys_age <- lm(mean_within_sys~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+race_factor+parent1_edu, data=main_unique)
summary(lm_within_sys_age)
lm_between_sys_age <- lm(mean_between_sys~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+race_factor+parent1_edu, data=main_unique)
summary(lm_between_sys_age)
lm_segreg_age<- lm(system_segreg~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+race_factor+parent1_edu, data=main_unique)
summary(lm_segreg_age)
lm_modul_avg_age <- lm(modul_avg~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+race_factor+parent1_edu, data=main_unique)
summary(lm_modul_avg_age)
lm_part_coef_age <- lm(part_coef~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+race_factor+parent1_edu, data=main_unique)
summary(lm_part_coef_age)

#childaces_sum_ignorenan
lm_within_sys_age <- lm(mean_within_sys~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+childaces_sum_ignorenan, data=main_unique)
summary(lm_within_sys_age)
lm_between_sys_age <- lm(mean_between_sys~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+childaces_sum_ignorenan, data=main_unique)
summary(lm_between_sys_age)
lm_segreg_age<- lm(system_segreg~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+childaces_sum_ignorenan, data=main_unique)
summary(lm_segreg_age)
lm_modul_avg_age <- lm(modul_avg~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+childaces_sum_ignorenan, data=main_unique)
summary(lm_modul_avg_age)
lm_part_coef_age <- lm(part_coef~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+childaces_sum_ignorenan, data=main_unique)
summary(lm_part_coef_age)
```

However, there are effects of the binned ACES (into 0-1, 2, or 3+) on within- and between-network connectivity as well as the participation coefficient. We see that 2 ACES is associated with significantly less within- and more between-network connectivity and lower system segregation.

```{r main effect aces on segregation plots, echo=FALSE, include=TRUE, results='hide',fig.show='hold', out.width='33.33%', fig.align='default'}
lm_within_sys_age <- lm(mean_within_sys~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+aces3category+ses_composite, data=main_unique)
summary(lm_within_sys_age)
lm_between_sys_age <- lm(mean_between_sys~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+aces3category+ses_composite, data=main_unique)
summary(lm_between_sys_age)
lm_segreg_age<- lm(system_segreg~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+aces3category+ses_composite, data=main_unique)
lm_part_coef_age <- lm(part_coef~age_scan+male+fd_mean_avg+avgweight+pctVolsCensored+totalSizet+aces3category+ses_composite, data=main_unique)
visreg(lm_within_sys_age,"age_scan",by="aces3category", overlay=TRUE)
visreg(lm_between_sys_age,"age_scan",by="aces3category", overlay=TRUE)
visreg(lm_part_coef_age,"age_scan",by="aces3category", overlay=TRUE)
```

## Questions, Notes, & Future Directions

* There are also sometimes outliers on some of the measures that flatten out age or environment trends, I have been looking into using robust regression to examine these trends instead, but did not go through all the trouble to bootstrap p-values for this time around. However, I think it's possible that robust regression might be a more defensible choice.

## Plot average functional connectivity matrices

We can also compare these to the PNC adolescent matrix and see how it differs.

ggcorrplot

ggcorr is better

What if we add the two runs for subjects who have more than one, what does that buy us? 
```{r plot matrices,  echo=FALSE, include=TRUE,fig.show='hold', out.width='100%'}
library(mdpeer)
network_dir=paste0("~/Desktop/cluster/jux/mackey_group/Ursula/projects/in_progress/within_between_network_conn_CBPD/data/imageData/",pipeline)
avg_matrix <- read.csv(paste0(network_dir,""), header = FALSE)
#reorder by yeo labels
#read in schaefer to yeo labels
#put labels on top and bottom
#subject_clustco_yeo_system<-l %>% arrange(labels) %>% summarize_all(mean)

avgmatrix <- as.matrix(avg_matrix)
# palf <- colorRampPalette(c("red","white", "blue")) 
# heatmap(avgmatrix, Rowv = NA, Colv = NA, col = palf(20))
plot(vizu.mat(avgmatrix, fill.scale.limits = c(-1.3, 1.3), x.lab=pipeline))

```

# Supplemental Analyses

## Replication parcellation: Schaefer200

```{r replication in Schaefer200}
#Use main_replicate_unique instead



networks_age_pvals_fdr_replicate
```

### Age and measures of network segregation

We used Schaefer200 as the replication parcellation, since it has nice correspondence to Schaefer400 and the Yeo7 systems. 

```{r replicate models of segregation, echo=FALSE, include=FALSE, results='hide'}
#look at mean within and between with age
lm_within_sys_age <- lm(mean_within_sys~age_scan+male+fd_mean+avgweight+pctSpikesFD+size_t, data=main_replicate_unique)
lm_between_sys_age <- lm(mean_between_sys~age_scan+male+fd_mean+avgweight+pctSpikesFD+size_t, data=main_replicate_unique)

lm_segreg_age<- lm(system_segreg~age_scan+male+fd_mean+avgweight+pctSpikesFD+size_t, data=main_replicate_unique)

lm_modul_avg_age <- lm(modul_avg~age_scan+male+fd_mean+avgweight+pctSpikesFD+size_t, data=main_replicate_unique)

lm_part_coef_age <- lm(part_coef~age_scan+male+fd_mean+avgweight+pctSpikesFD+size_t, data=main_replicate_unique)
lm_num_comms_age <- lm(num_comms_modul_avg~age_scan+male+fd_mean+avgweight+pctSpikesFD+size_t, data=main_replicate_unique)

```

```{r replicate plots of segregation, echo=FALSE, include=TRUE, results='hide'}
par(mfrow=c(2,3))
visreg(lm_between_sys_age,"age_scan")
visreg(lm_within_sys_age,"age_scan")
visreg(lm_segreg_age,"age_scan")
visreg(lm_modul_avg_age,"age_scan")
visreg(lm_part_coef_age,"age_scan")
visreg(lm_num_comms_age,"age_scan")
```

All previous findings significant increases in network segregation with age hold in our replication parcellation! The only finding that is inconsistent is the number of communities detected using modul_avgarity maximization decreasing with age, which was likely spurious anyways.

As a reminder, we controlled for sex, mean framewise displacement, percent of FD spikes in the data, the number of volumes a participant had, and the average weight of the functional network.

Also, no non-linear effects of age.

### System-level effects
Again, we find the strongest effects in Vis-DAN, DMN-DAN, and DMN-VAN, which are the only effects that pass *fdr* correction.

```{r lm replicate plots, echo=FALSE, include=TRUE, results='hide', fig.show='hold', out.width='33.33%', fig.align='default'}
networks_age_pvals_fdr_replicate
lm_sys1to3<- lm(sys1to3~age_scan+male+fd_mean+avgweight+pctSpikesFD+size_t, data=main_replicate_unique)
lm_sys3to7<- lm(sys3to7~age_scan+male+fd_mean+avgweight+pctSpikesFD+size_t, data=main_replicate_unique)
lm_sys4to7<- lm(sys4to7~age_scan+male+fd_mean+avgweight+pctSpikesFD+size_t, data=main_replicate_unique)

visreg(lm_sys1to3,"age_scan",main="Vis to DAN")
visreg(lm_sys3to7,"age_scan", main="DMN to DAN")
visreg(lm_sys4to7,"age_scan",  main="DMN to VAN")
```

All three effects survive FDR correction across the tests conducted, with DMN-VAN *p_fdr*=`r networks_age_pvals_fdr_replicate$pvalue[networks_age_pvals_fdr_replicate$network=="sys3to7"]`, DMN-DAN *p_fdr*= `r networks_age_pvals_fdr_replicate$pvalue[networks_age_pvals_fdr_replicate$network=="sys4to7"]`, Vis-DAN *p_fdr*= `r networks_age_pvals_fdr_replicate$pvalue[networks_age_pvals_fdr_replicate$network=="sys1to3"]`.

## Replication with a pipeline without GSR

```{r replication without GSR}
#load the .RDS file
pipeline='nogsr_spkreg_fd0.5dvars1.75_drpvls'
network_dir=paste0("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/",pipeline)
load(paste0(network_dir,"/CBPD_n90_schaefer400_allruns.Rdata"))


```

## Test-retest reliability of network metrics

Using both Pearson's correlation and the ICC. Noble et al. 2019 in their review on TRT of functional connectivity metrics suggest using ICC(1,1), or single_raters_absolute, which is used to estimate agreement in exact values when sources of error are unspecified. However, they acknowledge that using ICC(1,2) (averaging across two runs) yields an estimate of how much reliability improves when averaging across multiple sessions.

"Absolute agreement of connectivity derived from a single session (k=1) is necessarily lower than that averaged over two sessions (k=2), and this k=2 estimate may be used to estimate how much reliability improves when averaging over multiple measurements (e.g., repeated sessions), assuming they are interchangeable."

Tozzi et al. 2019 also looked at individual edges reliability, but they used ICC(3,1), which will always result in a higher value! Both papers find individual edges generally have poor reliability (< 0.4).
```{r TRT of net metrics,  echo=FALSE, include=TRUE,fig.show='hold', out.width='100%'}
pipelines=c("nogsr_spkreg_fd1.25dvars2_drpvls", 'nogsr_spkreg_fd0.5dvars1.75_drpvls', "gsr_censor_5contig_fd1.25dvars2_drpvls",'gsr_spkreg_fd0.5dvars1.75_drpvls', "gsr_censor_5contig_fd0.5dvars1.75_drpvls")
for (pipeline in pipelines){
network_dir=paste0("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/",pipeline)
load(paste0(network_dir,"/CBPD_n74_schaefer400.Rdata"))
#filter for only participants with more than 2 runs
dim(main)
#### examine the number of good vols in run1 vs run2####
l <- main_filt %>% group_by(ID) %>% filter(n() >= 2) %>% filter(run=="run-01")
hist(l$nVolCensored, main = "run 1= red, run 2 = blue, n Vols Censored", col=rgb(1,0,0,0.5))
l2 <- main_filt %>% group_by(ID) %>% filter(n() >= 2) %>% filter(run=="run-02")
hist(l2$nVolCensored,col=rgb(0,0,1,0.5), add=T)
### Test ret-test ####
trt <- main_filt %>% group_by(ID) %>% filter(n() >= 2) %>% dplyr::select(.,ID:pctSpikesFD_avg)
#rename 150 run 3 to run 2 so it goes in the right column
trt$run[trt$ID=="sub-CBPD0150" & trt$run=="run-03"] <- "run-02"
cols <- trt %>% ungroup() %>% dplyr::select(.,avgweight:sys7to7) %>%  colnames()
trt <- dcast(setDT(trt), ID~run, value.var = cols)
colnames(trt) <- make.names(colnames(trt)) #reshaped column names have - in them which is prohibited, then we can have a dataframe
trt <- as.data.frame(trt)
for (column in cols){
  temp <- trt %>% dplyr::select(.,matches(paste0("^",column)))
  assign(paste0(column, "_trt_corr"),cor.test(temp[,1], temp[,2])) #correlation
  assign(paste0(column, "_trt_icc"), ICC(temp, lmer = FALSE))
}
print(pipeline)
avgweight_trt_corr
modul_avg_trt_corr
mean_within_sys_trt_corr
mean_between_sys_trt_corr
system_segreg_trt_corr
avgweight_trt_icc
modul_avg_trt_icc
mean_within_sys_trt_icc
mean_between_sys_trt_icc
system_segreg_trt_icc
```
