---
title: "CBPD Parcel-Level Restuls"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(stats)
library(parallel)
library(lm.beta)
library(packrat)
library(summarytools)
library(visreg)
library(mgcv)
library(RLRsim)
library(GGally)
library(stringr)
library(tidyverse)
library(data.table)
library(bigmemory)
library(biglm)
#load the .RDS file
pipeline='nogsr_spkreg_fd0.5dvars1.75_drpvls'
pipeline="nogsr_spkreg_fd1.25dvars2_drpvls"
pipeline='gsr_spkreg_fd0.5dvars1.75_drpvls'
network_dir=paste0("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/",pipeline)

load(paste0(network_dir,"/CBPD_n92_schaefer400_allruns.Rdata"))
```

```{r brain plotting setup, include=FALSE, echo=FALSE}
library(fsbrain) #this may not work if you're editing the script directly on the cluster...
library(freesurferformats)
#rearrange the order of the brains in the T9 view of fsbrain
source("~/Documents/tools/fsbrain_fix_t9.R")
environment(brainview.t9) <- asNamespace('fsbrain')
assignInNamespace("brainview.t9", brainview.t9, ns = "fsbrain")
subjects_dir = "/Users/utooley/Documents/tools/CBIG/stable_projects/brain_parcellation/Schaefer2018_LocalGlobal/Parcellations/FreeSurfer5.3/";
subject_id = 'fsaverage';       # for functions which use one subject only
atlas='Schaefer2018_400Parcels_7Networks_order'

#Get the Schaefer atlas region names
schaefer_atlas_region_names_lh = get.atlas.region.names(atlas, template_subjects_dir = subjects_dir,template_subject=subject_id, hemi="lh");
schaefer_atlas_region_names_rh = get.atlas.region.names(atlas, template_subjects_dir = subjects_dir,template_subject=subject_id, hemi="rh");

output_image_directory="~/Documents/projects/in_progress/within_between_network_conn_CBPD/output/figures/brains/"
rgloptions=list("windowRect"=c(50,50,1000,1000));
```

## Load data
```{r load parcel data, include=FALSE, echo=FALSE}
pipeline='gsr_spkreg_fd0.5dvars1.75_drpvls'
edges_dir=paste0("/cbica/home/tooleyu/projects/in_progress/within_between_network_conn_CBPD/data/imageData/",pipeline,"/schaefer400zNetworks_avg/")
#make a huge dataframe of subjects x edges

# files <- data.frame(list.files(edges_dir)) %>% filter( list.files.edges_dir. %in% paste0(main_unique$ID, "_schaefer400MNI_zavgnetwork.txt")); files$list.files.edges_dir. <- paste0(edges_dir,files$list.files.edges_dir.)
# vect <- matrix(nrow = dim(main_unique)[1], ncol = 79801)
# for (i in 1:dim(main_unique)[1]){
# mat <- data.frame(read_csv(file =paste0(edges_dir,main_unique$ID[i], "_schaefer400MNI_zavgnetwork.txt"), col_names = F))
# vect[i,2:79801]<-mat[lower.tri(mat)] #read out the lower triangle from matrix by row
# }
# 
# #code to read back into a 400 x 400 matrix! This works correctly.
# vec<- mat[lower.tri(mat)]
# goback <- matrix(nrow = 400, ncol=400)
# goback[lower.tri(goback, diag=FALSE)] <- vec
# goback <- t(goback)
# goback
# 
# saveRDS(vect,"~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/n92_all_edges.Rdata")

#Read back in the matrix of edges, so you don't create every time.
#n90_all_edges<- readRDS("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/n90_all_edges.Rds");n90_all_edges <- n90_all_edges[,-1]
n92_all_edges<- readRDS("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/n92_all_edges.RData");n92_all_edges <- n92_all_edges[,-1]
```

## Run edgwise linear models for SES
Run linear models on edges, controlling for age, sex and average motion.
```{r edgewise linear models}
#multi-core apply the linear model across the matrix of edges, get age pvals 
edgewise_ses_pvals<- mclapply(1:79800, function(x) { summary(lm(n92_all_edges[,x]~main_unique$ses_composite+main_unique$age_scan+main_unique$male+main_unique$fd_mean_avg+main_unique$avgweight+main_unique$totalSizet))$coef[2,4]}, mc.cores = 4)
edgewise_ses_pvals <- unlist(edgewise_ses_pvals)
edgewise_ses_pvals_fdr <- cbind(edgewise_ses_pvals,p.adjust(edgewise_ses_pvals,method = "fdr"))

#get age betas
edgewise_ses_betas<- mclapply(1:79800, function(x) { lm.beta(lm(n92_all_edges[,x]~main_unique$ses_composite+main_unique$age_scan+main_unique$male+main_unique$fd_mean_avg+main_unique$avgweight+main_unique$totalSizet))$standardized.coefficients[[2]]}, mc.cores = 4)
edgewise_ses_betas <- unlist(edgewise_ses_betas)
#save for reloading in future
save(edgewise_ses_pvals_fdr, edgewise_ses_betas,file= "~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/edgewise_ses_effects_all_cov_n92.Rdata")

#load back in edge effects
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/edgewise_ses_effects_all_cov_n92.Rdata")

#code to read back into a 400 x 400 matrix! This works correctly.
# vec<- mat[lower.tri(mat)]
edge_ses_pvals_mat <- matrix(nrow = 400, ncol=400)
edge_ses_pvals_mat[lower.tri(edge_ses_pvals_mat, diag=FALSE)] <- edgewise_ses_pvals_fdr[,1] #take uncorrected p-values for now
#copy lower triangle to upper triangle
edge_ses_pvals_mat[upper.tri(edge_ses_pvals_mat)] <- t(edge_ses_pvals_mat)[upper.tri(edge_ses_pvals_mat)]
edge_ses_betas_mat <- matrix(nrow = 400, ncol=400)
edge_ses_betas_mat[lower.tri(edge_ses_betas_mat, diag=FALSE)] <- edgewise_ses_betas
edge_ses_betas_mat[upper.tri( edge_ses_betas_mat)] <- t(edge_ses_betas_mat)[upper.tri( edge_ses_betas_mat)]
```

## Plot pvals on brain.

```{r brain plotting initial, include=FALSE, echo=FALSE}
#Use different pval thresholds and plot parcels that have age-sig edges at that threshold
pvalues=c(0.01,0.001,0.0001,0.00001)
pvalue=0.001
#Use different pval thresholds and plot parcels that have age-nonlin-sig edges at that threshold
pos_edges <- edge_ses_pvals_mat;pos_edges[edge_ses_betas_mat<0] <- NA
neg_edges <- edge_ses_pvals_mat;neg_edges[edge_ses_betas_mat>0] <- NA
for (pvalue in pvalues){
indices <- which(neg_edges<pvalue, arr.ind = T) #indices of edges that have age effects  below a pval
l <- data.frame(table(indices)) #for each parcel, how many age-significant edges does it have at a given pval thresh
values <- vector(mode = "double", 400)
for (i in 1:400){
values[as.numeric(as.character(l$indices[i]))] <- l$Freq[i]#replace the indices in values with the num of sig edges from that parcel in the table
}
print(max(values))
values <- values/2 #because we indexed the full matrix, there are duplicates for each edge
#values <- ifelse(values>num_edges,1,0)
#which(values>num_edges)
num_of_sig_age_edges_lh=as.list(setNames(c(0, values[1:200]), schaefer_atlas_region_names_lh))
num_of_sig_age_edges_rh=as.list(setNames(c(0, values[201:400]), schaefer_atlas_region_names_rh))
#colormap
colFn_diverging = colorRampPalette(c("white","#3602D9"));makecmap_options=list('colFn'=colFn_diverging) 
rglactions=list("snapshot_png"=paste0(output_image_directory,"ses_neg_pvals_", pvalue,"regions.png"),'shift_hemis_apart'=T) #purple="#7502E3", red=#E0011C, blue=#3602D9
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  num_of_sig_age_edges_lh, 
                             num_of_sig_age_edges_rh, makecmap_options = makecmap_options, "inflated", views="t9", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)
}

```

## Run edgwise linear models for CFG: U_united
Run linear models on edges, controlling for age, sex and average motion.
Look at two measures on the CFG - unique.shapes and U_united?
```{r edgewise linear models CFG}
#multi-core apply the linear model across the matrix of edges, get age pvals 
edgewise_cfg_uunited_pvals<- mclapply(1:79800, function(x) { summary(lm(n92_all_edges[,x]~main_unique$U_united+main_unique$age_scan+main_unique$male+main_unique$fd_mean_avg+main_unique$avgweight+main_unique$totalSizet))$coef[2,4]}, mc.cores = 4)
edgewise_cfg_uunited_pvals <- unlist(edgewise_cfg_uunited_pvals)
edgewise_cfg_uunited_pvals_fdr <- cbind(edgewise_cfg_uunited_pvals,p.adjust(edgewise_cfg_uunited_pvals,method = "fdr"))
#get age betas
edgewise_cfg_uunited_betas<- mclapply(1:79800, function(x) { lm.beta(lm(n92_all_edges[,x]~main_unique$U_united+main_unique$age_scan+main_unique$male+main_unique$fd_mean_avg+main_unique$avgweight+main_unique$totalSizet))$standardized.coefficients[[2]]}, mc.cores = 4)
edgewise_cfg_uunited_betas <- unlist(edgewise_cfg_uunited_betas)
#save for reloading in future
save(edgewise_cfg_uunited_pvals_fdr, edgewise_cfg_uunited_betas,file= "~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/edgewise_cfg_uunited_effects_all_cov_n92.Rdata")

#load back in edge cfg effects
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/edgewise_cfg_uunited_effects_all_cov_n92.Rdata")

#code to read back into a 400 x 400 matrix! This works correctly.
# vec<- mat[lower.tri(mat)]
edge_cfg_uunited_pvals_mat <- matrix(nrow = 400, ncol=400)
edge_cfg_uunited_pvals_mat[lower.tri(edge_cfg_uunited_pvals_mat, diag=FALSE)] <- edgewise_cfg_uunited_pvals_fdr[,1] #take uncorrected p-values for now
#copy lower triangle to upper triangle
edge_cfg_uunited_pvals_mat[upper.tri(edge_cfg_uunited_pvals_mat)] <- t(edge_cfg_uunited_pvals_mat)[upper.tri(edge_cfg_uunited_pvals_mat)]
edge_cfg_uunited_betas_mat <- matrix(nrow = 400, ncol=400)
edge_cfg_uunited_betas_mat[lower.tri(edge_cfg_uunited_betas_mat, diag=FALSE)] <- edgewise_cfg_uunited_betas
edge_cfg_uunited_betas_mat[upper.tri( edge_cfg_uunited_betas_mat)] <- t(edge_cfg_uunited_betas_mat)[upper.tri( edge_cfg_uunited_betas_mat)]
```

## Plot pvals on brain.

```{r brain plotting initial, include=FALSE, echo=FALSE}
#Use different pval thresholds and plot parcels that have age-sig edges at that threshold
pvalues=c(0.01,0.001,0.0001)
pvalue=0.001
#Use different pval thresholds and plot parcels that have age-nonlin-sig edges at that threshold
pos_edges <- edge_cfg_uunited_pvals_mat;pos_edges[edge_cfg_uunited_betas_mat<0] <- NA
neg_edges <- edge_cfg_uunited_pvals_mat;neg_edges[edge_cfg_uunited_betas_mat>0] <- NA
for (pvalue in pvalues){
indices <- which(pos_edges<pvalue, arr.ind = T) #indices of edges that have age effects  below a pval
l <- data.frame(table(indices)) #for each parcel, how many age-significant edges does it have at a given pval thresh
values <- vector(mode = "double", 400)
for (i in 1:400){
values[as.numeric(as.character(l$indices[i]))] <- l$Freq[i]#replace the indices in values with the num of sig edges from that parcel in the table
}
print(max(values))
values <- values/2 #because we indexed the full matrix, there are duplicates for each edge
#values <- ifelse(values>num_edges,1,0)
#which(values>num_edges)
num_of_sig_age_edges_lh=as.list(setNames(c(0, values[1:200]), schaefer_atlas_region_names_lh))
num_of_sig_age_edges_rh=as.list(setNames(c(0, values[201:400]), schaefer_atlas_region_names_rh))
#colormap
colFn_diverging = colorRampPalette(c("white","#E0011C"));makecmap_options=list('colFn'=colFn_diverging) 
rglactions=list("snapshot_png"=paste0(output_image_directory,"cfg_uunited_pos_pvals_", pvalue,"regions.png"),'shift_hemis_apart'=T) #purple="#7502E3", red=#E0011C, blue=#3602D9
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  num_of_sig_age_edges_lh, 
                             num_of_sig_age_edges_rh, makecmap_options = makecmap_options, "inflated", views="t9", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)
}
```

## Run edgwise linear models for CFG: unique.shapes
Run linear models on edges, controlling for age, sex and average motion.
```{r edgewise linear models CFG}
#multi-core apply the linear model across the matrix of edges, get age pvals 
edgewise_cfg_uniqshps_pvals<- mclapply(1:79800, function(x) { summary(lm(n92_all_edges[,x]~main_unique$unique.shapes+main_unique$age_scan+main_unique$male+main_unique$fd_mean_avg+main_unique$avgweight+main_unique$totalSizet))$coef[2,4]}, mc.cores = 4)
edgewise_cfg_uniqshps_pvals <- unlist(edgewise_cfg_uniqshps_pvals)
edgewise_cfg_uniqshps_pvals_fdr <- cbind(edgewise_cfg_uniqshps_pvals,p.adjust(edgewise_cfg_uniqshps_pvals,method = "fdr"))
#get age betas
edgewise_cfg_uniqshps_betas<- mclapply(1:79800, function(x) { lm.beta(lm(n92_all_edges[,x]~main_unique$unique.shapes+main_unique$age_scan+main_unique$male+main_unique$fd_mean_avg+main_unique$avgweight+main_unique$totalSizet))$standardized.coefficients[[2]]}, mc.cores = 4)
edgewise_cfg_uniqshps_betas <- unlist(edgewise_cfg_uniqshps_betas)
#save for reloading in future
save(edgewise_cfg_uniqshps_pvals_fdr, edgewise_cfg_uniqshps_betas,file= "~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/edgewise_cfg_uniqshps_effects_all_cov_n92.Rdata")

#load back in edge cfg effects
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/edgewise_cfg_uniqshps_effects_all_cov_n92.Rdata")

#code to read back into a 400 x 400 matrix! This works correctly.
# vec<- mat[lower.tri(mat)]
edge_cfg_uniqshps_pvals_mat <- matrix(nrow = 400, ncol=400)
edge_cfg_uniqshps_pvals_mat[lower.tri(edge_cfg_uniqshps_pvals_mat, diag=FALSE)] <- edgewise_cfg_uniqshps_pvals_fdr[,1] #take uncorrected p-values for now
#copy lower triangle to upper triangle
edge_cfg_uniqshps_pvals_mat[upper.tri(edge_cfg_uniqshps_pvals_mat)] <- t(edge_cfg_uniqshps_pvals_mat)[upper.tri(edge_cfg_uniqshps_pvals_mat)]
edge_cfg_uniqshps_betas_mat <- matrix(nrow = 400, ncol=400)
edge_cfg_uniqshps_betas_mat[lower.tri(edge_cfg_uniqshps_betas_mat, diag=FALSE)] <- edgewise_cfg_uniqshps_betas
edge_cfg_uniqshps_betas_mat[upper.tri( edge_cfg_uniqshps_betas_mat)] <- t(edge_cfg_uniqshps_betas_mat)[upper.tri( edge_cfg_uniqshps_betas_mat)]
```

## Plot pvals on brain.

```{r brain plotting initial, include=FALSE, echo=FALSE}
#Use different pval thresholds and plot parcels that have age-sig edges at that threshold
pvalues=c(0.01,0.001,0.0001)
pvalue=0.001
#Use different pval thresholds and plot parcels that have age-nonlin-sig edges at that threshold
pos_edges <- edge_cfg_uniqshps_pvals_mat;pos_edges[edge_cfg_uniqshps_betas_mat<0] <- NA
neg_edges <- edge_cfg_uniqshps_pvals_mat;neg_edges[edge_cfg_uniqshps_betas_mat>0] <- NA
for (pvalue in pvalues){
indices <- which(neg_edges<pvalue, arr.ind = T) #indices of edges that have age effects  below a pval
l <- data.frame(table(indices)) #for each parcel, how many age-significant edges does it have at a given pval thresh
values <- vector(mode = "double", 400)
for (i in 1:400){
values[as.numeric(as.character(l$indices[i]))] <- l$Freq[i]#replace the indices in values with the num of sig edges from that parcel in the table
}
print(max(values))
values <- values/2 #because we indexed the full matrix, there are duplicates for each edge
#values <- ifelse(values>num_edges,1,0)
#which(values>num_edges)
num_of_sig_age_edges_lh=as.list(setNames(c(0, values[1:200]), schaefer_atlas_region_names_lh))
num_of_sig_age_edges_rh=as.list(setNames(c(0, values[201:400]), schaefer_atlas_region_names_rh))
#colormap
colFn_diverging = colorRampPalette(c("white","#3602D9"));makecmap_options=list('colFn'=colFn_diverging) 
rglactions=list("snapshot_png"=paste0(output_image_directory,"cfg_uniqshps_neg_pvals_", pvalue,"regions.png"),'shift_hemis_apart'=T) #purple="#7502E3", red=#E0011C, blue=#3602D9
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  num_of_sig_age_edges_lh, 
                             num_of_sig_age_edges_rh, makecmap_options = makecmap_options, "inflated", views="t9", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)
}
```

#What do these edges CFG unique.shapes look like pattern-wise?
```{r CFG unique.shapes plots}
library(ggplot2)
library(gridExtra)
sum(edgewise_cfg_uniqshps_pvals_fdr[,1]<0.0001)/length(edgewise_cfg_uniqshps_pvals_fdr[,1]) #percentage
#make a big plot of them
par(mfrow=c(4,4))
myplots <- lapply(which(edgewise_cfg_uniqshps_pvals_fdr[,1]<0.0001), function(x) {ggplot(data=cbind(n92_all_edges[,x],main_unique), aes(x = unique.shapes,y = ...1)) +theme_bw() +labs(x = "CFG Unique.shapes", y = "Edge connectivity")+ geom_point(size = .9) +geom_smooth(method = "lm")+ theme(legend.position = "none")})
#arrange in a grid because par doesn't work with ggplot2
gridExtra::grid.arrange( grobs = myplots, nrow = 4)

#make sure these are sig edges
lapply(which(edgewise_cfg_uniqshps_pvals_fdr[,1]<0.0001), function(x) {summary(lm(n92_all_edges[,x]~main_unique$age_scan+main_unique$male+main_unique$fd_mean_avg+main_unique$avgweight+main_unique$totalSizet+main_unique$unique.shapes))})

#which systems are these?
#read in node identity and order
community_assign <- read.delim("~/Documents/tools/parcellations/schaefer400x7CommunityAffiliation.1D", header = F)
#communities <- paste0("comm",community_assign$V1) %>% car::recode(.,"'comm1'='Visual'; 'comm2'='Somatomotor' ; 'comm3'='Dorsal Attention';'comm4'='Ventral Attention';'comm5'='Limbic';'comm6'='Frontoparietal';'comm7'='Default'")
communities <- paste0("comm",community_assign$V1) %>% car::recode(.,"'comm1'='VIS'; 'comm2'='SM' ; 'comm3'='DA';'comm4'='VA';'comm5'='LIM';'comm6'='FP';'comm7'='DM'")
community_colors <- communities %>% car::recode(.,"'Visual'='#7B287E'; 'Somatomotor'='#5CA1C8' ; 'Dorsal Attention'='#0A9045';'Ventral Attention'='#C33AF8';'Limbic'='#dcf8a4';'Frontoparietal'='#EF9C23';'Default'='#E34A53'")

# put pvalues back in matrix, but don't copy lower triangle to upper triangle
edge_cfg_uniqshps_pvals_mat  <- matrix(nrow = 400, ncol=400)
edge_cfg_uniqshps_pvals_mat [lower.tri(edge_cfg_uniqshps_pvals_mat , diag=FALSE)] <- edgewise_cfg_uniqshps_pvals_fdr[,1] #take uncorrected p-values for now
length(which(edgewise_cfg_uniqshps_pvals_fdr[,1]<0.0001))
#rows and cols
rownames(edge_cfg_uniqshps_pvals_mat ) <- communities;colnames(edge_cfg_uniqshps_pvals_mat ) <- communities
edges <- which(edge_cfg_uniqshps_pvals_mat < 0.0001, arr.ind = T)
rownames(edge_cfg_uniqshps_pvals_mat [edges[,1],])
colnames(edge_cfg_uniqshps_pvals_mat [, edges[,2]])
paste0(rownames(edge_cfg_uniqshps_pvals_mat [edges[,1],]),"-",colnames(edge_cfg_uniqshps_pvals_mat [, edges[,2]]))
```

## Run edgwise linear models for age x SES
Run linear models on edges, controlling for age, sex and average motion.
```{r edgewise linear models age x SES}
#multi-core apply the linear model across the matrix of edges, take the last p-value and coefficient (bc interaction)
edgewise_agexses_pvals<- mclapply(1:79800, function(x) { summary(lm(n92_all_edges[,x]~main_unique$age_scan*main_unique$ses_composite+main_unique$age_scan+main_unique$male+main_unique$fd_mean_avg+main_unique$avgweight+main_unique$totalSizet))$coef[8,4]}, mc.cores = 4)
edgewise_agexses_pvals <- unlist(edgewise_agexses_pvals)
edgewise_agexses_pvals_fdr <- cbind(edgewise_agexses_pvals,p.adjust(edgewise_agexses_pvals,method = "fdr"))
#get age betas
edgewise_agexses_betas<- mclapply(1:79800, function(x) { lm.beta(lm(n92_all_edges[,x]~main_unique$age_scan*main_unique$ses_composite+main_unique$age_scan+main_unique$male+main_unique$fd_mean_avg+main_unique$avgweight+main_unique$totalSizet))$standardized.coefficients[[8]]}, mc.cores = 4)
edgewise_agexses_betas <- unlist(edgewise_agexses_betas)
#save for reloading in future
save(edgewise_agexses_pvals_fdr,edgewise_agexses_pvals, edgewise_agexses_betas,file= "~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/edgewise_agexses_effects_all_cov_n92_2.Rdata")

#load back in edge effects
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/edgewise_agexses_effects_all_cov_n92.Rdata")

#code to read back into a 400 x 400 matrix! This works correctly.
# vec<- mat[lower.tri(mat)]
edge_agexses_pvals_mat <- matrix(nrow = 400, ncol=400)
edge_agexses_pvals_mat[lower.tri(edge_agexses_pvals_mat, diag=FALSE)] <- edgewise_agexses_pvals_fdr[,1] #take uncorrected p-values for now
#copy lower triangle to upper triangle
edge_agexses_pvals_mat[upper.tri(edge_agexses_pvals_mat)] <- t(edge_agexses_pvals_mat)[upper.tri(edge_agexses_pvals_mat)]
edge_agexses_betas_mat <- matrix(nrow = 400, ncol=400)
edge_agexses_betas_mat[lower.tri(edge_agexses_betas_mat, diag=FALSE)] <- edgewise_agexses_betas
edge_agexses_betas_mat[upper.tri( edge_agexses_betas_mat)] <- t(edge_agexses_betas_mat)[upper.tri( edge_agexses_betas_mat)]
```

## Plot pvals on brain.

```{r brain plotting initial, include=FALSE, echo=FALSE}
#Use different pval thresholds and plot parcels that have age-sig edges at that threshold
pvalues=c(0.01,0.001,0.0001)
pvalue=0.001
#Use different pval thresholds and plot parcels that have age-nonlin-sig edges at that threshold
pos_edges <- edge_agexses_pvals_mat;pos_edges[edge_agexses_betas_mat<0] <- NA
neg_edges <- edge_agexses_pvals_mat;neg_edges[edge_agexses_betas_mat>0] <- NA
for (pvalue in pvalues){
indices <- which(edge_agexses_pvals_mat<pvalue, arr.ind = T) #indices of edges that have age effects  below a pval
l <- data.frame(table(indices)) #for each parcel, how many age-significant edges does it have at a given pval thresh
values <- vector(mode = "double", 400)
for (i in 1:400){
values[as.numeric(as.character(l$indices[i]))] <- l$Freq[i]#replace the indices in values with the num of sig edges from that parcel in the table
}
print(max(values))
values <- values/2 #because we indexed the full matrix, there are duplicates for each edge
#values <- ifelse(values>num_edges,1,0)
#which(values>num_edges)
num_of_sig_age_edges_lh=as.list(setNames(c(0, values[1:200]), schaefer_atlas_region_names_lh))
num_of_sig_age_edges_rh=as.list(setNames(c(0, values[201:400]), schaefer_atlas_region_names_rh))
#colormap
colFn_diverging = colorRampPalette(c("white","#7502E3"));makecmap_options=list('colFn'=colFn_diverging) 
rglactions=list("snapshot_png"=paste0(output_image_directory,"agexses_pvals_", pvalue,"regions.png"),'shift_hemis_apart'=T) #purple="#7502E3", red=#E0011C, blue=#3602D9
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  num_of_sig_age_edges_lh, 
                             num_of_sig_age_edges_rh, makecmap_options = makecmap_options, "inflated", views="t9", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)
}

```


#What do these edges age x SES look like pattern-wise?
```{r age x SES plots}
library(ggplot2)
library(gridExtra)
sum(edgewise_agexses_pvals_fdr[,1]<0.001)/length(edgewise_agexses_pvals_fdr[,1]) #percentage
#make a big plot of them
par(mfrow=c(4,3))
myplots <- lapply(which(edgewise_agexses_pvals_fdr[,1]<0.0001), function(x) {ggplot(data=cbind(n92_all_edges[,x],main_unique), aes(x = age_scan,y = ...1,color = factor(ses_composite>-0.3507257))) +theme_bw() +labs(x = "Age", y = "Edge connectivity", color = "SES > median SES")+ geom_point(size = .9) +geom_smooth(method = "lm",)+ theme(legend.position = "none")})
#arrange in a grid because par doesn't work with ggplot2
gridExtra::grid.arrange( grobs = myplots, nrow = 3)

#make sure these are sig edges
lapply(which(edgewise_agexses_pvals_fdr[,1]<0.0001), function(x) {summary(lm(n92_all_edges[,x]~main_unique$age_scan*main_unique$ses_composite+main_unique$age_scan+main_unique$male+main_unique$fd_mean_avg+main_unique$avgweight+main_unique$totalSizet))})

#which systems are these?
#read in node identity and order
community_assign <- read.delim("~/Documents/tools/parcellations/schaefer400x7CommunityAffiliation.1D", header = F)
#communities <- paste0("comm",community_assign$V1) %>% car::recode(.,"'comm1'='Visual'; 'comm2'='Somatomotor' ; 'comm3'='Dorsal Attention';'comm4'='Ventral Attention';'comm5'='Limbic';'comm6'='Frontoparietal';'comm7'='Default'")
communities <- paste0("comm",community_assign$V1) %>% car::recode(.,"'comm1'='VIS'; 'comm2'='SM' ; 'comm3'='DA';'comm4'='VA';'comm5'='LIM';'comm6'='FP';'comm7'='DM'")
community_colors <- communities %>% car::recode(.,"'Visual'='#7B287E'; 'Somatomotor'='#5CA1C8' ; 'Dorsal Attention'='#0A9045';'Ventral Attention'='#C33AF8';'Limbic'='#dcf8a4';'Frontoparietal'='#EF9C23';'Default'='#E34A53'")
# don't copy lower triangle to upper triangle
edge_agexses_pvals_mat <- matrix(nrow = 400, ncol=400)
edge_agexses_pvals_mat[lower.tri(edge_agexses_pvals_mat, diag=FALSE)] <- edgewise_agexses_pvals_fdr[,1] #take uncorrected p-values for now
which(edgewise_agexses_pvals_fdr[,1]<0.0001)
#rows and cols
rownames(edge_agexses_pvals_mat) <- communities;colnames(edge_agexses_pvals_mat) <- communities
edges <- which(edge_agexses_pvals_mat< 0.0001, arr.ind = T)
rownames(edge_agexses_pvals_mat[edges[,1],])
colnames(edge_agexses_pvals_mat[, edges[,2]])
paste0(rownames(edge_agexses_pvals_mat[edges[,1],]),"-",colnames(edge_agexses_pvals_mat[, edges[,2]]))
```
