---
title: "CBPD Parcel-Level Restuls"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(stats)
library(parallel)
library(lm.beta)
library(packrat)
library(summarytools)
library(visreg)
library(mgcv)
library(RLRsim)
library(GGally)
library(stringr)
library(tidyverse)
library(data.table)
library(bigmemory)
library(biglm)
#load the .RDS file
pipeline='nogsr_spkreg_fd0.5dvars1.75_drpvls'
pipeline="nogsr_spkreg_fd1.25dvars2_drpvls"
pipeline='gsr_spkreg_fd0.5dvars1.75_drpvls'
network_dir=paste0("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/",pipeline)

load(paste0(network_dir,"/CBPD_n92_schaefer400_allruns.Rdata"))
```

```{r brain plotting setup, include=FALSE, echo=FALSE}
library(fsbrain) #this may not work if you're editing the script directly on the cluster...
library(freesurferformats)
#rearrange the order of the brains in the T9 view of fsbrain
source("~/Documents/tools/fsbrain_fix_t9.R")
environment(brainview.t9) <- asNamespace('fsbrain')
assignInNamespace("brainview.t9", brainview.t9, ns = "fsbrain")
subjects_dir = "/Users/utooley/Documents/tools/CBIG/stable_projects/brain_parcellation/Schaefer2018_LocalGlobal/Parcellations/FreeSurfer5.3/";
subject_id = 'fsaverage';       # for functions which use one subject only
atlas='Schaefer2018_400Parcels_7Networks_order'

#Get the Schaefer atlas region names
schaefer_atlas_region_names_lh = get.atlas.region.names(atlas, template_subjects_dir = subjects_dir,template_subject=subject_id, hemi="lh");
schaefer_atlas_region_names_rh = get.atlas.region.names(atlas, template_subjects_dir = subjects_dir,template_subject=subject_id, hemi="rh");
# right <- subject.annot(subjects_dir = subjects_dir,subject_id =subject_id, hemi="rh", atlas = atlas);
# left <- subject.annot(subjects_dir = subjects_dir,subject_id =subject_id, hemi="lh", atlas = atlas);
# lh_inf <- subject.surface(subjects_dir = subjects_dir, "fsaverage", "inflated", "lh")
# rh_inf <- subject.surface(subjects_dir = subjects_dir, "fsaverage", "inflated", "rh")
# rglactions=list("snapshot_png"=paste0(output_image_directory,"yeo_schaefer400_7nets.png"))
# aparc_outline <- list(
#   lh = fsbrain::annot.outline(annotdata = left,
#                               surface_mesh = lh_inf,
#                               outline_color = NULL),
#   rh = fsbrain::annot.outline(annotdata = right,
#                               surface_mesh = lh_inf,
#                               outline_color = NULL))
# vis.symmetric.data.on.subject(subjects_dir = subjects_dir, "fsaverage",
#                               communities_lh,
#                               communities_rh,
#                               surface = "inflated",
#                               views = "t4",
#                               bg=aparc_outline,
#                               rglactions = list(no_vis = TRUE))
# 
# vis.subject.annot(subjects_dir = subjects_dir,subject_id =subject_id, hemi="both", atlas = atlas,surface = "inflated",outline = list('outline_color'='#000000'))
#set output dir for saving images
output_image_directory="~/Documents/projects/in_progress/within_between_network_conn_CBPD/output/figures/brains/"
  
#Set RGL defaults, larger window and how to make snapshots!
rgloptions=list("windowRect"=c(50,50,1000,1000));

## Make subjlist for qdec analyses
# tab <- read.table("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/qdec.agesext1rating.n89.table.dat",header = T)
# subid <- main_unique$ID
# age_scan <- scale(main_unique$age_scan, center=T, scale = T)
# sex <- ifelse(main_unique$male=="Male", 1, 0)
# t1_rating <- scale(main_unique$t1_rating_avg, center=T, scale = T)
# n92_agesex_ursula_data <- cbind(subid,age_scan,sex,t1_rating)
# colnames(n92_agesex_ursula_data) <- c("fsid","age_scan","sex","t1_rating")
# #Make the sex column 0-1 to not lose df
# write.table(n92_agesex_ursula_data, file = paste("~/Desktop/qdec.agesext1rating.n92.table.dat", sep=""), row.names = F, quote=F)
```

## Load data
```{r load parcel data, include=FALSE, echo=FALSE}
pipeline='gsr_spkreg_fd0.5dvars1.75_drpvls'
edges_dir=paste0("/cbica/home/tooleyu/projects/in_progress/within_between_network_conn_CBPD/data/imageData/",pipeline,"/schaefer400zNetworks_avg/")
#make a huge dataframe of subjects x edges

# files <- data.frame(list.files(edges_dir)) %>% filter( list.files.edges_dir. %in% paste0(main_unique$ID, "_schaefer400MNI_zavgnetwork.txt")); files$list.files.edges_dir. <- paste0(edges_dir,files$list.files.edges_dir.)
# vect <- matrix(nrow = dim(main_unique)[1], ncol = 79801)
# for (i in 1:dim(main_unique)[1]){
# mat <- data.frame(read_csv(file =paste0(edges_dir,main_unique$ID[i], "_schaefer400MNI_zavgnetwork.txt"), col_names = F))
# vect[i,2:79801]<-mat[lower.tri(mat)] #read out the lower triangle from matrix by row
# }
# 
# #code to read back into a 400 x 400 matrix! This works correctly.
# vec<- mat[lower.tri(mat)]
# goback <- matrix(nrow = 400, ncol=400)
# goback[lower.tri(goback, diag=FALSE)] <- vec
# goback <- t(goback)
# goback
# 
# saveRDS(vect,"~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/n92_all_edges.Rdata")

#Read back in the matrix of edges, so you don't create every time.
#n90_all_edges<- readRDS("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/n90_all_edges.Rds");n90_all_edges <- n90_all_edges[,-1]
n92_all_edges<- readRDS("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/n92_all_edges.RData");n92_all_edges <- n92_all_edges[,-1]
```

## Run edgwise linear models
Run linear models on edges, controlling for age, sex and average motion.
```{r edgewise linear models}
# edgewise_age_pvals<- apply(n90_all_edges,2, function(x) { summary(lm(x~main_unique$age_scan+main_unique$male+main_unique$fd_mean_avg+main_unique$avgweight+main_unique$pctVolsCensored+main_unique$totalSizet))$coef[2,4]}) #without multicore

#multi-core apply the linear model across the matrix of edges, get age pvals 
edgewise_age_pvals<- mclapply(1:79800, function(x) { summary(lm(n92_all_edges[,x]~main_unique$age_scan+main_unique$male+main_unique$fd_mean_avg+main_unique$avgweight+main_unique$totalSizet))$coef[2,4]}, mc.cores = 4)
edgewise_age_pvals <- unlist(edgewise_age_pvals)
edgewise_age_pvals_fdr <- cbind(edgewise_age_pvals,p.adjust(edgewise_age_pvals,method = "fdr"))
#get age betas
edgewise_age_betas<- mclapply(1:79800, function(x) { lm.beta(lm(n92_all_edges[,x]~main_unique$age_scan+main_unique$male+main_unique$fd_mean_avg+main_unique$avgweight+main_unique$totalSizet))$standardized.coefficients[[2]]}, mc.cores = 4)
edgewise_age_betas <- unlist(edgewise_age_betas)
#save for reloading in future
save(edgewise_age_pvals_fdr, edgewise_age_betas,file= "~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/edgewise_age_effects_all_cov_n92.Rdata")

#load back in edge age effects
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/edgewise_motion_effects_all_cov_n92.Rdata")

#code to read back into a 400 x 400 matrix! This works correctly.
# vec<- mat[lower.tri(mat)]
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400)
edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1] #take uncorrected p-values for now
#copy lower triangle to upper triangle
edge_age_pvals_mat[upper.tri(edge_age_pvals_mat)] <- t(edge_age_pvals_mat)[upper.tri(edge_age_pvals_mat)]
edge_age_betas_mat <- matrix(nrow = 400, ncol=400)
edge_age_betas_mat[lower.tri(edge_age_betas_mat, diag=FALSE)] <- edgewise_age_betas
edge_age_betas_mat[upper.tri( edge_age_betas_mat)] <- t(edge_age_betas_mat)[upper.tri( edge_age_betas_mat)]
```

## Make a chord diagram of pvals and betas

```{r chord diagram of edges, include=FALSE, echo=FALSE}
library(circlize)
library(car)
library(dplyr)
#read in node identity and order
community_assign <- read.delim("~/Documents/tools/parcellations/schaefer400x7CommunityAffiliation.1D", header = F)
communities <- paste0("comm",community_assign$V1) %>% car::recode(.,"'comm1'='Visual'; 'comm2'='Somatomotor' ; 'comm3'='Dorsal Attention';'comm4'='Ventral Attention';'comm5'='Limbic';'comm6'='Frontoparietal';'comm7'='Default'")
community_colors <- communities %>% car::recode(.,"'Visual'='#7B287E'; 'Somatomotor'='#5CA1C8' ; 'Dorsal Attention'='#0A9045';'Ventral Attention'='#C33AF8';'Limbic'='#dcf8a4';'Frontoparietal'='#EF9C23';'Default'='#E34A53'")

#just threshold the betas
links_to_show=edge_age_pvals_mat<= 0.001;edge_age_betas_mat[links_to_show==FALSE] <- 0
#how stringently you threshold determines when you hit the memory limit, 400x400 won't show at 0.005.
col_fun = colorRamp2(breaks = c(-0.43,0,0.49),
                  colors = c("royalblue1","white","red"),
                  transparency = .5)
#Original chord diagram
rownames(edge_age_betas_mat) <- communities;colnames(edge_age_betas_mat) <- communities
par(cex = 1)
chordDiagramFromMatrix(edge_age_betas_mat, annotationTrack = c("name","grid"),
             symmetric = TRUE, grid.col = c("#7B287E", "#5CA1C8", "#0A9045","#C33AF8","#dcf8a4", "#EF9C23", "#E34A53"), col=col_fun, reduce = -1) #reduce keeps even the tiny grids, keeps from eliminating some sectors, annotationTrack turns off the tick marks

#Diagrams trying to keep sectors (regions in this case) in order of region
#make the sector names vertical
rownames(edge_age_betas_mat) <- paste0("region", rep(1:400));colnames(edge_age_betas_mat) <- paste0("region", rep(1:400))
chordDiagramFromMatrix(edge_age_betas_mat[1:200,1:200], annotationTrack = c("grid"), preAllocateTracks = list(track.height = max(strwidth(unlist(dimnames(edge_age_betas_mat[1:200,1:200]))))), 
             symmetric = TRUE, grid.col = community_colors[1:200], col=col_fun, reduce = -1)

#try ordering the sectors--this works!
chordDiagramFromMatrix(edge_age_betas_mat[1:200,1:200], annotationTrack = c("grid"), preAllocateTracks = list(track.height = max(strwidth(unlist(dimnames(edge_age_betas_mat[1:200,1:200]))))), order=rownames(edge_age_betas_mat[1:200,1:200]),
             symmetric = TRUE, col=col_fun, reduce = -1)

#using grouped chord diagram--this is it!
rownames(edge_age_betas_mat) <- paste0("region", rep(1:400));colnames(edge_age_betas_mat) <- paste0("region", rep(1:400))
group = structure(communities[1:400], names = rownames(edge_age_betas_mat[1:400,1:400]))
group = factor(group, levels = c("Visual","Somatomotor","Dorsal Attention","Ventral Attention", "Limbic","Frontoparietal","Default"))#make it a factor with levels in the order I want to see them
group.col=structure(community_colors[1:400],
                names = rownames(edge_age_betas_mat[1:400,1:400]))
chordDiagramFromMatrix(edge_age_betas_mat[1:400,1:400], annotationTrack = c("grid"), preAllocateTracks = list(track.height = max(strwidth(unlist(dimnames(edge_age_betas_mat[1:400,1:400]))))), order=rownames(edge_age_betas_mat[1:400,1:400]),
             symmetric = TRUE, col=col_fun, reduce = -1, group=group, grid.col = group.col, small.gap = 0, big.gap = 5)

#this adds vertical labels to check region order
# we go back to the first track and customize sector labels
circos.track(track.index = 1, panel.fun = function(x, y) {
    circos.text(CELL_META$xcenter, CELL_META$ylim[1], CELL_META$sector.index, 
        facing = "clockwise", niceFacing = TRUE, adj = c(0, 0.5))
}, bg.border = NA) # here set bg.border to NA is important

#take out the vertical labels
chordDiagramFromMatrix(edge_age_betas_mat[1:400,1:400], annotationTrack = c("grid"),  order=rownames(edge_age_betas_mat[1:400,1:400]),
             symmetric = TRUE, col=col_fun, reduce = -1, group=group, grid.col = group.col, small.gap = 0, big.gap = 5)
```

## Plot parcelwise on brain at different sig thresholds

```{r get nodes to plot, include=FALSE, echo=FALSE}
#code to read back into a 400 x 400 matrix! This works correctly.
# vec<- mat[lower.tri(mat)]
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400)
edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1] #take uncorrected p-values for now
#copy lower triangle to upper triangle
#edge_age_pvals_mat <- t(edge_age_pvals_mat)
edge_age_pvals_mat[upper.tri(edge_age_pvals_mat)] <- t(edge_age_pvals_mat)[upper.tri(edge_age_pvals_mat)]# for a symmetric matrix
```

## Plot pvals on brain.

```{r brain plotting initial, include=FALSE, echo=FALSE}
#Use different pval thresholds and plot parcels that have age-sig edges at that threshold
pvalues=c(0.01,0.001,0.0001,0.00001)
pvalue=0.001
#Use different pval thresholds and plot parcels that have age-nonlin-sig edges at that threshold
pos_edges <- edge_age_pvals_mat;pos_edges[edge_age_betas_mat<0] <- NA
neg_edges <- edge_age_pvals_mat;neg_edges[edge_age_betas_mat>0] <- NA
for (pvalue in pvalues){
indices <- which(edge_age_pvals_mat<pvalue, arr.ind = T) #indices of edges that have age effects  below a pval
l <- data.frame(table(indices)) #for each parcel, how many age-significant edges does it have at a given pval thresh
values <- vector(mode = "double", 400)
for (i in 1:400){
values[as.numeric(as.character(l$indices[i]))] <- l$Freq[i]#replace the indices in values with the num of sig edges from that parcel in the table
}
print(max(values))
values <- values/2 #because we indexed the full matrix, there are duplicates for each edge
#values <- ifelse(values>num_edges,1,0)
#which(values>num_edges)
num_of_sig_age_edges_lh=as.list(setNames(c(0, values[1:200]), schaefer_atlas_region_names_lh))
num_of_sig_age_edges_rh=as.list(setNames(c(0, values[201:400]), schaefer_atlas_region_names_rh))
#colormap
colFn_diverging = colorRampPalette(c("white","#7502E3"));makecmap_options=list('colFn'=colFn_diverging) 
rglactions=list("snapshot_png"=paste0(output_image_directory,"motion_pvals_", pvalue,"regions.png")) #purple="#7502E3", red=#E0011C, blue=#3602D9
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  num_of_sig_age_edges_lh, 
                             num_of_sig_age_edges_rh, makecmap_options = makecmap_options, "inflated", views="t4", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)
}

#Show with the community colors
#Create a list from the vector of Schaefer structure names and the labels from WSBM consensus partition
comms_and_edges=ifelse(values==0,community_assign$V1,-values) #where there are sig age effects, overwrite community color assignment
num_of_sig_age_edges_lh=as.list(setNames(c(0, comms_and_edges[1:200]), schaefer_atlas_region_names_lh))
num_of_sig_age_edges_rh=as.list(setNames(c(0, comms_and_edges[201:400]), schaefer_atlas_region_names_rh))

#plot with colors of communities
yeo_colors=colorRampPalette(c("#000000","#A9A9A9", "#7B287E", "#5CA1C8", "#0A9045","#C33AF8", "#dcf8a4", "#EF9C23", "#E34A53"))
makecmap_options=list('colFn'=yeo_colors)

rgloptions=list("windowRect"=c(50,50,1000,1000));
rglactions=list("snapshot_png"=paste0(output_image_directory,"age_pvals_", pvalue,"community_colors.png"))
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  num_of_sig_age_edges_lh, 
                             num_of_sig_age_edges_rh, makecmap_options = makecmap_options, "inflated", views="t4", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)
#just plot schaefer communities
rglactions=list("snapshot_png"=paste0(output_image_directory,"community_colors.png"))
vis.subject.annot(subjects_dir, 'fsaverage6','Schaefer2018_400Parcels_7Networks_order','both', "inflated", views="t4",
                  rgloptions = rgloptions,rglactions = rglactions)
```

## Plot raincloud number of significant edges in parcels by community

```{raincloud plot}
source("~/Documents/tools/raincloud.R")
community_assign <- read.delim("~/Documents/tools/parcellations/schaefer400x7CommunityAffiliation.1D", header = F)
communities <- paste0("comm",community_assign$V1) %>% car::recode(.,"'comm1'='Visual'; 'comm2'='Somatomotor' ; 'comm3'='Dorsal Attention';'comm4'='Ventral Attention';'comm5'='Limbic';'comm6'='Frontoparietal';'comm7'='Default'") %>% factor(levels=c("Visual","Somatomotor","Dorsal Attention", "Ventral Attention", "Limbic", "Frontoparietal", "Default"))
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400);edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1];edge_age_pvals_mat[upper.tri(edge_age_pvals_mat)] <- t(edge_age_pvals_mat)[upper.tri(edge_age_pvals_mat)]

edge_age_betas_mat <- matrix(nrow = 400, ncol=400);edge_age_betas_mat[lower.tri(edge_age_betas_mat, diag=FALSE)] <- edgewise_age_betas; edge_age_betas_mat[upper.tri( edge_age_betas_mat)] <- t(edge_age_betas_mat)[upper.tri( edge_age_betas_mat)]
#Use different pval thresholds and plot parcels that have age-nonlin-sig edges at that threshold
pos_edges <- edge_age_pvals_mat;pos_edges[edge_age_betas_mat<0] <- NA
neg_edges <- edge_age_pvals_mat;neg_edges[edge_age_betas_mat>0] <- NA
pvalue=0.001
indices <- which(pos_edges<pvalue, arr.ind = T) #indices of edges that have age effects  below a pval
l <- data.frame(table(indices)) #for each parcel, how many age-significant edges does it have at a given pval thresh
values <- vector(mode = "double", 400)
for (i in 1:400){
values[as.numeric(as.character(l$indices[i]))] <- l$Freq[i]#replace the indices in values with the num of sig edges from that parcel in the table
}
values <- values/2 #because we indexed twice
num_edges <- data.frame(factor(communities, ),values);colnames(num_edges) <- c("community","data"); 
longdata = num_edges %>% dplyr::group_by(community) %>% mutate(med = median(data))

g <- ggplot(data = longdata, aes(y = data, x = community, fill=community)) +
  #geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .5) +
  geom_point(aes(y = data, color = community), position = position_jitter(width = .15), size = .3, alpha = 0.5) +geom_boxplot(width = .3, guides = FALSE, outlier.shape = NA, alpha = 0.5) +
  ylim(c(0,13)) +
  guides(fill = FALSE) +
  guides(color = FALSE) +
  # scale_color_manual(values=c("#4669dc","pink","purple")) +
  #scale_color_distiller(palette="Blues", direction = 1) +
  #scale_fill_distiller(palette="Blues", direction = 1) +
  scale_color_manual(values=c("#7B287E", "#5CA1C8", "#0A9045","#C33AF8", "#B6C988", "#EF9C23", "#E34A53")) +
  scale_fill_manual(values= c("#7B287E", "#5CA1C8", "#0A9045","#C33AF8", "#B6C988", "#EF9C23", "#E34A53")) +
  #scale_color_gradient2(low="#FFFFFF",mid= "#FB6A4A", high="#67000D", midpoint= 0.475, aesthetics = c("color", "fill")) +
  theme_bw() +
  raincloud_theme
print(g)

kruskal.test(data~community, data = num_edges)
pairwise.wilcox.test(num_edges$data, num_edges$community,
                     p.adjust.method = "fdr")
num_edges$community <- relevel(num_edges$community, "Default")
anova(lm(data~community,data=num_edges))
TukeyHSD(aov(lm(data~community,data=num_edges)))

```

## Statistical tests on communities by age-significant number of edges
```{stat tests on edges by community}
#statistical tests for pos-neg-all
indices <- which(neg_edges<pvalue, arr.ind = T) #indices of edges that have age effects  below a pval
l <- data.frame(table(indices)) #for each parcel, how many age-significant edges does it have at a given pval thresh
values <- vector(mode = "double", 400)
for (i in 1:400){
values[as.numeric(as.character(l$indices[i]))] <- l$Freq[i]#replace the indices in values with the num of sig edges from that parcel in the table
}
num_edges <- data.frame(factor(communities, ),values);colnames(num_edges) <- c("community","data"); 

kruskal.test(data~community, data = num_edges)
pairwise.wilcox.test(num_edges$data, num_edges$community,
                     p.adjust.method = "bonferroni")
summary(lm(data~community,data=num_edges)) #adjust reference level for this?

#What I'm trying to test is whether the age effect on edge-level connectivity is different by community. Age x community interaction? Think about this. Or just take the average age beta on edges only within a community?
#reload edges pvals mat
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400);edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1];edge_age_pvals_mat[upper.tri(edge_age_pvals_mat)] <- t(edge_age_pvals_mat)[upper.tri(edge_age_pvals_mat)]

edge_age_betas_mat <- matrix(nrow = 400, ncol=400);edge_age_betas_mat[lower.tri(edge_age_betas_mat, diag=FALSE)] <- edgewise_age_betas; edge_age_betas_mat[upper.tri( edge_age_betas_mat)] <- t(edge_age_betas_mat)[upper.tri( edge_age_betas_mat)]
#threshold at p< 0.001
betas <- list()
edge_age_betas_mat_thresh <- edge_age_betas_mat
links_to_show=edge_age_pvals_mat<0.001;edge_age_betas_mat_thresh[links_to_show==FALSE] <- NA
rownames(edge_age_betas_mat_thresh) <- communities;colnames(edge_age_betas_mat_thresh) <- communities
for (j in 1:7){
  set=unique(communities)[j]
  #take the rows from vis and the columns from SM (and vice-versa?)
  betas[[set]] <- na.omit(c(edge_age_betas_mat_thresh[rownames(edge_age_betas_mat_thresh)==set,]))
}
betas<- lapply(betas, function (x) {length (x) <- 18953;x}) #make the all the same length and pad with NAS
betas <- do.call("cbind", betas) #can also rbind if want rows
colnames(betas) <- unique(communities);longdata <- melt(betas);colnames(longdata) <- c("x","community","value")
kruskal.test(value~community, data = longdata)
pairwise.wilcox.test(longdata$value, longdata$community,
                     p.adjust.method = "fdr")
summary(lm(value~community,data=longdata))
TukeyHSD(aov(lm(value~community,data=longdata))

#Plot it
means <- apply(betas,MARGIN = 2,mean, na.rm=T)
barplot(means,col = c("#7B287E", "#5CA1C8", "#0A9045","#C33AF8", "#B6C988", "#EF9C23", "#E34A53"))
g <- ggplot(data = longdata, aes(y = value, x = community, fill=community)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .5) +
  geom_point(aes(y = value, color = community), position = position_jitter(width = .15), size = .3, alpha = 0.8) +
  #geom_boxplot(width = .2, guides = FALSE, outlier.shape = NA, alpha = 0.3) +
  #ylim(c(0,15)) +
  guides(fill = FALSE) +
  guides(color = FALSE) +
  # scale_color_manual(values=c("#4669dc","pink","purple")) +
  #scale_color_distiller(palette="Blues", direction = 1) +
  #scale_fill_distiller(palette="Blues", direction = 1) +
  scale_color_manual(values=c("#7B287E", "#5CA1C8", "#0A9045","#C33AF8", "#B6C988", "#EF9C23", "#E34A53")) +
  scale_fill_manual(values= c("#7B287E", "#5CA1C8", "#0A9045","#C33AF8", "#B6C988", "#EF9C23", "#E34A53")) +
  #scale_color_gradient2(low="#FFFFFF",mid= "#FB6A4A", high="#67000D", midpoint= 0.475, aesthetics = c("color", "fill")) +
  theme_bw() +
  #geom_hline(yintercept=0)+
  raincloud_theme
print(g)
```

## Where is connectivity from parcel(s) showing age-associated remodeling associated with age?

```{r select parcel connectivity associated with age or reasoning, include=FALSE, echo=FALSE}
#reload edges pvals mat
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/edgewise_age_effects_all_cov_n92.Rdata")
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400);edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1];edge_age_pvals_mat <- t(edge_age_pvals_mat)
# pos_edges <- edge_age_pvals_mat;pos_edges[edge_age_betas_mat<0] <- NA
# neg_edges <- edge_age_pvals_mat;neg_edges[edge_age_betas_mat>0] <- NA
pvalue=0.001
indices <- which(edge_age_pvals_mat<pvalue, arr.ind = T) #indices of edges that have age effects  below a pval
l <- data.frame(table(indices)) #for each parcel, how many age-significant edges does it have at a given pval thresh
values <- vector(mode = "double", 400)
for (i in 1:400){
values[as.numeric(as.character(l$indices[i]))] <- l$Freq[i]
}
#Number of edges > 10
print(max(values))
#pull out only the parcel(s) that have over 10 edges
which(values>15)
num_edges=10
#start with one parcel
#for each subject, pull out that parcel column
# n92_parcel_conn<- apply(n92_all_edges,1, function (x){
#   goback <- matrix(nrow = 400, ncol=400)
# goback[lower.tri(goback, diag=FALSE)] <-x
# goback[upper.tri(goback)] <- t(goback)[upper.tri(goback)]
# return(goback[,which(values>num_edges)])
# })
#to use multiple parcels
n92_parcel_conn<- apply(n92_all_edges,1, function (x){
  goback <- matrix(nrow = 400, ncol=400)
goback[lower.tri(goback, diag=FALSE)] <-x
goback[upper.tri(goback)] <- t(goback)[upper.tri(goback)]
return(rowMeans(goback[,which(values>num_edges)], na.rm = T))
})
#92 x 400 subject by parcel connectivity matrix for one parcel
n92_parcel_conn <- t(n92_parcel_conn)
#lapply across across the matrix of edges to that parcel to look at where connectivity is associated with age, get age pvals 
edgewise_age_pvals<- apply(n92_parcel_conn,2, function(x) { tryCatch(summary(lm(x~main_unique$age_scan+ main_unique$age_scan+main_unique$male+main_unique$fd_mean_avg+main_unique$avgweight+main_unique$pctVolsCensored+main_unique$totalSizet))$coef[2,4], error=function(e) NA)}) #without multicore
edgewise_age_pvals <- unlist(edgewise_age_pvals)
edgewise_age_pvals_fdr <- cbind(edgewise_age_pvals,p.adjust(edgewise_age_pvals,method = "fdr"))
#get age betas
edgewise_age_betas<- apply(n92_parcel_conn,2, function(x) { tryCatch(lm.beta(lm(x~main_unique$age_scan+main_unique$male+main_unique$fd_mean_avg+main_unique$avgweight+main_unique$pctVolsCensored+main_unique$totalSizet))$standardized.coefficients[[2]], error=function(e) NA)})
edgewise_age_betas <- unlist(edgewise_age_betas)

#plot on brain
#toplot <- ifelse(values>num_edges,1,0)
toplot <- ifelse(edgewise_age_pvals_fdr[,2]<0.05,edgewise_age_betas, NA)
num_of_sig_age_edges_lh=as.list(setNames(c(0, toplot[1:200]), schaefer_atlas_region_names_lh))
num_of_sig_age_edges_rh=as.list(setNames(c(0, toplot[201:400]), schaefer_atlas_region_names_rh))
#colormap
#colFn_diverging = colorRampPalette(RColorBrewer::brewer.pal(3, name="Purples"));makecmap_options=list('colFn'=colFn_diverging) 
colFn_diverging = colorRampPalette(rev(RColorBrewer::brewer.pal(9, name="RdBu")));makecmap_options=list('colFn'=colFn_diverging) 
rglactions=list("snapshot_png"=paste0(output_image_directory,"reasoning_associated_connectivity_from_5_region.png"))
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  num_of_sig_age_edges_lh, 
                             num_of_sig_age_edges_rh, makecmap_options = makecmap_options, "inflated", views="t4", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)
```

## Where is connectivity from parcel(s) showing age-associated remodeling associated with reasoning?
```{r age-associated connectivity with reasoning}
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/edgewise_age_effects_all_cov_n92.Rdata")
#reload edges pvals mat
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400);edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1];edge_age_pvals_mat <- t(edge_age_pvals_mat)
# pos_edges <- edge_age_pvals_mat;pos_edges[edge_age_betas_mat<0] <- NA
# neg_edges <- edge_age_pvals_mat;neg_edges[edge_age_betas_mat>0] <- NA
pvalue=0.001
indices <- which(edge_age_pvals_mat<pvalue, arr.ind = T) #indices of edges that have age effects  below a pval
l <- data.frame(table(indices)) #for each parcel, how many age-significant edges does it have at a given pval thresh
values <- vector(mode = "double", 400)
for (i in 1:400){
values[as.numeric(as.character(l$indices[i]))] <- l$Freq[i]
}
#Number of edges > 10
print(max(values))
#pull out only the parcel(s) that have over 10 edges
which(values>15)
num_edges=10
#start with one parcel
#for each subject, pull out that parcel column
# n92_parcel_conn<- apply(n92_all_edges,1, function (x){
#   goback <- matrix(nrow = 400, ncol=400)
# goback[lower.tri(goback, diag=FALSE)] <-x
# goback[upper.tri(goback)] <- t(goback)[upper.tri(goback)]
# return(goback[,which(values>num_edges)])
# })
#to use multiple parcels
n92_parcel_conn<- apply(n92_all_edges,1, function (x){
  goback <- matrix(nrow = 400, ncol=400)
goback[lower.tri(goback, diag=FALSE)] <-x
goback[upper.tri(goback)] <- t(goback)[upper.tri(goback)]
return(rowMeans(goback[,which(values>num_edges)], na.rm = T))
})
# #Matrix Reasoning
n92_parcel_conn <- t(n92_parcel_conn)
main_unique$matrix_reasoning_both <- ifelse(is.na(main_unique$wppsi_matrix_valid),main_unique$wisc_matrix_scaled,ifelse(main_unique$wppsi_matrix_valid==0,NA,main_unique$wppsi_matrix_scaled))
main_unique$matrix_reasoning_both_raw <- ifelse(is.na(main_unique$wppsi_matrix_valid),main_unique$wisc_matrix_raw,ifelse(main_unique$wppsi_matrix_valid==0,NA,main_unique$wppsi_matrix_raw))
main_unique$matrix_reasoning_both;main_unique$matrix_reasoning_both_raw

#lapply across across the matrix of edges to that parcel to look at where connectivity is associated with age, get age pvals 
edgewise_age_pvals<- apply(n92_parcel_conn,2, function(x) { tryCatch(summary(lm(x~main_unique$matrix_reasoning_both+ main_unique$age_scan+main_unique$male+main_unique$fd_mean_avg+main_unique$avgweight+main_unique$pctVolsCensored+main_unique$totalSizet))$coef[2,4], error=function(e) NA)}) #without multicore
edgewise_age_pvals <- unlist(edgewise_age_pvals)
edgewise_age_pvals_fdr <- cbind(edgewise_age_pvals,p.adjust(edgewise_age_pvals,method = "fdr"))
#get age betas
edgewise_age_betas<- apply(n92_parcel_conn,2, function(x) { tryCatch(lm.beta(lm(x~main_unique$matrix_reasoning_both+main_unique$age_scan+main_unique$male+main_unique$fd_mean_avg+main_unique$avgweight+main_unique$pctVolsCensored+main_unique$totalSizet))$standardized.coefficients[[2]], error=function(e) NA)})
edgewise_age_betas <- unlist(edgewise_age_betas)

#plot on brain
#toplot <- ifelse(values>num_edges,1,0)
toplot <- ifelse(edgewise_age_pvals_fdr[,2]<0.05,edgewise_age_betas, NA)
num_of_sig_age_edges_lh=as.list(setNames(c(0, toplot[1:200]), schaefer_atlas_region_names_lh))
num_of_sig_age_edges_rh=as.list(setNames(c(0, toplot[201:400]), schaefer_atlas_region_names_rh))
#colormap
#colFn_diverging = colorRampPalette(RColorBrewer::brewer.pal(3, name="Purples"));makecmap_options=list('colFn'=colFn_diverging) 
colFn_diverging = colorRampPalette(rev(RColorBrewer::brewer.pal(9, name="RdBu")));makecmap_options=list('colFn'=colFn_diverging, 'symm'=T) 
rglactions=list("snapshot_png"=paste0(output_image_directory,"reasoning_associated_connectivity_from_5_region.png"), 'shift_hemis_apart'=T)
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  num_of_sig_age_edges_lh, 
                             num_of_sig_age_edges_rh, makecmap_options = makecmap_options, "inflated", views="t9", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)
```

## How many are within and how many are between edges that show age effects?
```{r proportion of pos and negative edges within and between}
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/edgewise_age_effects_all_cov_n92.Rdata")
#reload edges pvals mat--only upper triangle
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400)
edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1] #take uncorrected p-values for now
edge_age_pvals_mat <- t(edge_age_pvals_mat)
edge_age_betas_mat <- matrix(nrow = 400, ncol=400);edge_age_betas_mat[lower.tri(edge_age_betas_mat, diag=FALSE)] <- edgewise_age_betas; edge_age_betas_mat<- t(edge_age_betas_mat)

#threshold at p< 0.001
#for the proportion within community
betas <- list()
edge_age_betas_mat_thresh <- edge_age_betas_mat
links_to_show=edge_age_pvals_mat<0.001;edge_age_betas_mat_thresh[links_to_show==FALSE] <- 0
rownames(edge_age_betas_mat_thresh) <- communities;colnames(edge_age_betas_mat_thresh) <- communities
for (j in 1:7){
  set=unique(communities)[j]
  #take the rows from vis and the columns from SM (and vice-versa?)
  betas[[set]] <- na.omit(c(edge_age_betas_mat_thresh[rownames(edge_age_betas_mat_thresh)==set,colnames(edge_age_betas_mat_thresh)==set]))
}
betas <- unlist(betas)
sum(betas<0)/sum(betas!=0);sum(betas>0)/sum(betas!=0);

#for the proportion between communities
betas <- list()
edge_age_betas_mat_thresh <- edge_age_betas_mat
links_to_show=edge_age_pvals_mat<0.001;edge_age_betas_mat_thresh[links_to_show==FALSE] <- 0
rownames(edge_age_betas_mat_thresh) <- communities;colnames(edge_age_betas_mat_thresh) <- communities
for (j in 1:7){
  set=unique(communities)[j]
  #take the rows from vis and the columns from SM (and vice-versa?)
  betas[[set]] <- na.omit(c(edge_age_betas_mat_thresh[rownames(edge_age_betas_mat_thresh)==set,colnames(edge_age_betas_mat_thresh)!=set]))
}
betas <- unlist(betas)
sum(betas<0)/sum(betas!=0);sum(betas>0)/sum(betas!=0);

rownames(edge_age_betas_mat) <- communities;colnames(edge_age_betas_mat) <- communities
#for all possible combinations of communities
combinations=combn(unique(communities),2)
set=combinations[,1]#take vis and sm community
#reload edges pvals mat
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400);edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1] #take uncorrected p-values for now
edge_age_pvals_mat <- t(edge_age_pvals_mat)
#for positive, take only the edge pvals that have positive betas associated with them 
links_to_show=edge_age_betas_mat>= 0;edge_age_pvals_mat[links_to_show==FALSE] <- NA

for (j in 1:dim(combinations)[2]){
  set=combinations[,j]
  #take the rows from vis and the columns from SM (and vice-versa?)
  #View(edge_age_betas_mat[rownames(edge_age_betas_mat)==set[1],colnames(edge_age_betas_mat)==set[2]])
  #rows <- which(rownames(edge_age_betas_mat)==set[1], arr.ind = T);cols <- which(colnames(edge_age_betas_mat)==set[2], arr.ind = T)
  colmax=rep(0,400)
  rowmax=rep(0,400)
  indices=which(rownames(edge_age_betas_mat)==set[1])
  for (x in indices){
      rowmax[x] <- sum(edge_age_pvals_mat[x,which(colnames(edge_age_betas_mat)==set[2])]<=pvalue, na.rm = T)
  }
  indices=which(colnames(edge_age_betas_mat)==set[2])
  for (x in indices){
      colmax[x] <- sum(edge_age_pvals_mat[rownames(edge_age_betas_mat)==set[1],x]<=pvalue, na.rm = T)
  }
  #Plot only in one community at a time
  for (community in set){
    values=rowSums(cbind(colmax,rowmax), na.rm = T)  #these two vectors should be non-overlapping, for the combinations of communities, so can add them together
    print(community)
  values=ifelse(communities==community,values,0)
  pos_sig_age_betas_lh=as.list(setNames(c(0, values[1:200]), schaefer_atlas_region_names_lh))
  pos_sig_age_betas_rh=as.list(setNames(c(0, values[201:400]), schaefer_atlas_region_names_rh))
  #colormap
  colFn_diverging = colorRampPalette(c("white","orange","red"));makecmap_options=list('colFn'=colFn_diverging,'range'=c(0,10))
  rglactions=list("snapshot_png"=paste0(output_image_directory,"/pairwise_comm_age_connectivity/num_sig_edges_pos_age_for_parcel_",set[1],set[2],"_regions_in_",community,"_",pvalue,".png"), 'shift_hemis_apart'=TRUE)
  vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  pos_sig_age_betas_lh, 
                               pos_sig_age_betas_rh, makecmap_options = makecmap_options, "inflated", views="t9", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)
  }
}
#do the negative edges
#reload pvals mat
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400);edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1] #take uncorrected p-values for now
edge_age_pvals_mat <- t(edge_age_pvals_mat)
links_to_show=edge_age_betas_mat<= 0;edge_age_pvals_mat[links_to_show==FALSE] <- NA
for (j in 1:dim(combinations)[2]){
  set=combinations[,j]
  #take the rows from vis and the columns from SM (and vice-versa?)
  #View(edge_age_betas_mat[rownames(edge_age_betas_mat)==set[1],colnames(edge_age_betas_mat)==set[2]])
  #rows <- which(rownames(edge_age_betas_mat)==set[1], arr.ind = T);cols <- which(colnames(edge_age_betas_mat)==set[2], arr.ind = T)
  colmax=rep(0,400)
  rowmax=rep(0,400)
  indices=which(rownames(edge_age_betas_mat)==set[1])
  for (x in indices){
      rowmax[x] <- sum(edge_age_pvals_mat[x,which(colnames(edge_age_betas_mat)==set[2])]<=pvalue, na.rm = T)
  }
  indices=which(colnames(edge_age_betas_mat)==set[2])
  for (x in indices){
      colmax[x] <- sum(edge_age_pvals_mat[rownames(edge_age_betas_mat)==set[1],x]<=pvalue, na.rm = T)
  }
  #Plot only in one community at a time
  for (community in set){
    values=rowSums(cbind(colmax,rowmax), na.rm = T)   #these two vectors should be non-overlapping, for the combinations of communities, so can add them together
    print(community)
  values=ifelse(communities==community,values,0)
  pos_sig_age_betas_lh=as.list(setNames(c(0, values[1:200]), schaefer_atlas_region_names_lh))
  pos_sig_age_betas_rh=as.list(setNames(c(0, values[201:400]), schaefer_atlas_region_names_rh))
  #colormap
  colFn_diverging = colorRampPalette(c("white","lightblue","blue"));makecmap_options=list('colFn'=colFn_diverging,'range'=c(0,10))
  rglactions=list("snapshot_png"=paste0(output_image_directory,"/pairwise_comm_age_connectivity/num_sig_edges_neg_age_for_parcel_",set[1],set[2],"_regions_in",community,"_",pvalue,".png"),'shift_hemis_apart'=TRUE)
  vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  pos_sig_age_betas_lh, 
                               pos_sig_age_betas_rh, makecmap_options = makecmap_options, "inflated", views="t9", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)
  }
}
```

## Plot specific communities age-significant edges number of edges

```{r brain plotting pvals threshold, include=FALSE, echo=FALSE}
#take each set of communities 
community_assign <- read.delim("~/Documents/tools/parcellations/schaefer400x7CommunityAffiliation.1D", header = F)
communities <- paste0("comm",community_assign$V1) %>% car::recode(.,"'comm1'='Visual'; 'comm2'='Somatomotor' ; 'comm3'='Dorsal Attention';'comm4'='Ventral Attention';'comm5'='Limbic';'comm6'='Frontoparietal';'comm7'='Default'")
edge_age_pvals_mat;edge_age_betas_mat
#threshold the betas to only keep those at p < 0.01
pvalue=0.01
rownames(edge_age_betas_mat) <- communities;colnames(edge_age_betas_mat) <- communities
#for all possible combinations of communities
combinations=combn(unique(communities),2)
set=combinations[,1]#take vis and sm community
#reload edges pvals mat
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400);edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1] #take uncorrected p-values for now
edge_age_pvals_mat <- t(edge_age_pvals_mat)
#for positive, take only the edge pvals that have positive betas associated with them 
links_to_show=edge_age_betas_mat>= 0;edge_age_pvals_mat[links_to_show==FALSE] <- NA

for (j in 1:dim(combinations)[2]){
  set=combinations[,j]
  #take the rows from vis and the columns from SM (and vice-versa?)
  #View(edge_age_betas_mat[rownames(edge_age_betas_mat)==set[1],colnames(edge_age_betas_mat)==set[2]])
  #rows <- which(rownames(edge_age_betas_mat)==set[1], arr.ind = T);cols <- which(colnames(edge_age_betas_mat)==set[2], arr.ind = T)
  colmax=rep(0,400)
  rowmax=rep(0,400)
  indices=which(rownames(edge_age_betas_mat)==set[1])
  for (x in indices){
      rowmax[x] <- sum(edge_age_pvals_mat[x,which(colnames(edge_age_betas_mat)==set[2])]<=pvalue, na.rm = T)
  }
  indices=which(colnames(edge_age_betas_mat)==set[2])
  for (x in indices){
      colmax[x] <- sum(edge_age_pvals_mat[rownames(edge_age_betas_mat)==set[1],x]<=pvalue, na.rm = T)
  }
  #Plot only in one community at a time
  for (community in set){
    values=rowSums(cbind(colmax,rowmax), na.rm = T)  #these two vectors should be non-overlapping, for the combinations of communities, so can add them together
    print(community)
  values=ifelse(communities==community,values,0)
  pos_sig_age_betas_lh=as.list(setNames(c(0, values[1:200]), schaefer_atlas_region_names_lh))
  pos_sig_age_betas_rh=as.list(setNames(c(0, values[201:400]), schaefer_atlas_region_names_rh))
  #colormap
  colFn_diverging = colorRampPalette(c("white","orange","red"));makecmap_options=list('colFn'=colFn_diverging,'range'=c(0,10))
  rglactions=list("snapshot_png"=paste0(output_image_directory,"/pairwise_comm_age_connectivity/num_sig_edges_pos_age_for_parcel_",set[1],set[2],"_regions_in_",community,"_",pvalue,".png"), 'shift_hemis_apart'=TRUE)
  vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  pos_sig_age_betas_lh, 
                               pos_sig_age_betas_rh, makecmap_options = makecmap_options, "inflated", views="t9", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)
  }
}
#do the negative edges
#reload pvals mat
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400);edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1] #take uncorrected p-values for now
edge_age_pvals_mat <- t(edge_age_pvals_mat)
links_to_show=edge_age_betas_mat<= 0;edge_age_pvals_mat[links_to_show==FALSE] <- NA
for (j in 1:dim(combinations)[2]){
  set=combinations[,j]
  #take the rows from vis and the columns from SM (and vice-versa?)
  #View(edge_age_betas_mat[rownames(edge_age_betas_mat)==set[1],colnames(edge_age_betas_mat)==set[2]])
  #rows <- which(rownames(edge_age_betas_mat)==set[1], arr.ind = T);cols <- which(colnames(edge_age_betas_mat)==set[2], arr.ind = T)
  colmax=rep(0,400)
  rowmax=rep(0,400)
  indices=which(rownames(edge_age_betas_mat)==set[1])
  for (x in indices){
      rowmax[x] <- sum(edge_age_pvals_mat[x,which(colnames(edge_age_betas_mat)==set[2])]<=pvalue, na.rm = T)
  }
  indices=which(colnames(edge_age_betas_mat)==set[2])
  for (x in indices){
      colmax[x] <- sum(edge_age_pvals_mat[rownames(edge_age_betas_mat)==set[1],x]<=pvalue, na.rm = T)
  }
  #Plot only in one community at a time
  for (community in set){
    values=rowSums(cbind(colmax,rowmax), na.rm = T)   #these two vectors should be non-overlapping, for the combinations of communities, so can add them together
    print(community)
  values=ifelse(communities==community,values,0)
  pos_sig_age_betas_lh=as.list(setNames(c(0, values[1:200]), schaefer_atlas_region_names_lh))
  pos_sig_age_betas_rh=as.list(setNames(c(0, values[201:400]), schaefer_atlas_region_names_rh))
  #colormap
  colFn_diverging = colorRampPalette(c("white","lightblue","blue"));makecmap_options=list('colFn'=colFn_diverging,'range'=c(0,10))
  rglactions=list("snapshot_png"=paste0(output_image_directory,"/pairwise_comm_age_connectivity/num_sig_edges_neg_age_for_parcel_",set[1],set[2],"_regions_in",community,"_",pvalue,".png"),'shift_hemis_apart'=TRUE)
  vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  pos_sig_age_betas_lh, 
                               pos_sig_age_betas_rh, makecmap_options = makecmap_options, "inflated", views="t9", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)
  }
}

#Do with the within-community edges
combinations=rbind(unique(communities),unique(communities))
#do the max
#reload pvals mat
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400);edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1] #take uncorrected p-values for now
edge_age_pvals_mat <- t(edge_age_pvals_mat)
links_to_show=edge_age_betas_mat>= 0;edge_age_pvals_mat[links_to_show==FALSE] <- NA
for (j in 1:dim(combinations)[2]){
  set=combinations[,j]
  rowmax=rep(0,400)
  indices=which(rownames(edge_age_betas_mat)==set[1])
  for (x in indices){
      rowmax[x] <- sum(edge_age_pvals_mat[x,which(colnames(edge_age_betas_mat)==set[2])]<=pvalue, na.rm = T)
  }
  pos_sig_age_betas_lh=as.list(setNames(c(0, rowmax[1:200]), schaefer_atlas_region_names_lh))
  pos_sig_age_betas_rh=as.list(setNames(c(0, rowmax[201:400]), schaefer_atlas_region_names_rh))
  #colormap
  colFn_diverging = colorRampPalette(c("white","orange","red"));makecmap_options=list('colFn'=colFn_diverging,'range'=c(0,10))
  rglactions=list("snapshot_png"=paste0(output_image_directory,"/pairwise_comm_age_connectivity/num_sig_edges_pos_age_for_parcel_",set[1],set[2],"_regions_",pvalue,".png"))
  vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  pos_sig_age_betas_lh, 
                               pos_sig_age_betas_rh, makecmap_options = makecmap_options, "inflated", views="t4", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)
}
#do the min
#reload pvals mat
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400);edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1] #take uncorrected p-values for now
edge_age_pvals_mat <- t(edge_age_pvals_mat)
links_to_show=edge_age_betas_mat<= 0;edge_age_pvals_mat[links_to_show==FALSE] <- NA
for (j in 1:dim(combinations)[2]){
  set=combinations[,j]
  rowmax=rep(0,400)
  indices=which(rownames(edge_age_betas_mat)==set[1])
  for (x in indices){
      rowmax[x] <- sum(edge_age_pvals_mat[x,which(colnames(edge_age_betas_mat)==set[2])]<=pvalue, na.rm = T)
  }
  pos_sig_age_betas_lh=as.list(setNames(c(0, rowmax[1:200]), schaefer_atlas_region_names_lh))
  pos_sig_age_betas_rh=as.list(setNames(c(0, rowmax[201:400]), schaefer_atlas_region_names_rh))
  #colormap
  colFn_diverging = colorRampPalette(c("white","lightblue","blue"));makecmap_options=list('colFn'=colFn_diverging,'range'=c(0,10))
  rglactions=list("snapshot_png"=paste0(output_image_directory,"num_sig_edges_neg_age_for_parcel_",set[1],set[2],"_regions_",pvalue,".png"))
  vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  pos_sig_age_betas_lh, 
                               pos_sig_age_betas_rh, makecmap_options = makecmap_options, "inflated", views="t4", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)
}
```

## Plot specific communities age-significant edges max betas

```{r specific communities age-significant edges, include=FALSE, echo=FALSE}
#take each set of communities 
community_assign <- read.delim("~/Documents/tools/parcellations/schaefer400x7CommunityAffiliation.1D", header = F)
communities <- paste0("comm",community_assign$V1) %>% car::recode(.,"'comm1'='Visual'; 'comm2'='Somatomotor' ; 'comm3'='Dorsal Attention';'comm4'='Ventral Attention';'comm5'='Limbic';'comm6'='Frontoparietal';'comm7'='Default'")
edge_age_pvals_mat;edge_age_betas_mat
#threshold the betas to only keep those at p < 0.01
pvalue=0.001
links_to_show=edge_age_pvals_mat<= pvalue;edge_age_betas_mat[links_to_show==FALSE] <- 0

rownames(edge_age_betas_mat) <- communities;colnames(edge_age_betas_mat) <- communities
#for all possible combinations of communities
combinations=combn(unique(communities),2)
set=combinations[,1]#take vis and sm community
#do the max
for (j in 1:dim(combinations)[2]){
  set=combinations[,j]
  #take the rows from vis and the columns from SM (and vice-versa?)
  #View(edge_age_betas_mat[rownames(edge_age_betas_mat)==set[1],colnames(edge_age_betas_mat)==set[2]])
  #rows <- which(rownames(edge_age_betas_mat)==set[1], arr.ind = T);cols <- which(colnames(edge_age_betas_mat)==set[2], arr.ind = T)
  colmax=rep(0,400)
  rowmax=rep(0,400)
  indices=which(rownames(edge_age_betas_mat)==set[1])
  for (x in indices){
      rowmax[x] <- max(edge_age_betas_mat[x,which(colnames(edge_age_betas_mat)==set[2])], na.rm = T)
  }
  indices=which(colnames(edge_age_betas_mat)==set[2])
  for (x in indices){
      colmax[x] <- max(edge_age_betas_mat[rownames(edge_age_betas_mat)==set[1],x], na.rm = T)
  }
  #Plot only in one community at a time
  for (community in set){
    values=colmax+rowmax  #these two vectors should be non-overlapping, for the combinations of communities, so can add them together
    print(community)
  values=ifelse(communities==community,values,0)
  pos_sig_age_betas_lh=as.list(setNames(c(0, values[1:200]), schaefer_atlas_region_names_lh))
  pos_sig_age_betas_rh=as.list(setNames(c(0, values[201:400]), schaefer_atlas_region_names_rh))
  #colormap
  colFn_diverging = colorRampPalette(c("white","white","orange","red"));makecmap_options=list('colFn'=colFn_diverging)
  rglactions=list("snapshot_png"=paste0(output_image_directory,"/pairwise_comm_age_connectivity/max_sig_pos_age_betas_for_parcel_",set[1],set[2],"_regions_in_",community,"_",pvalue,".png"))
  vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  pos_sig_age_betas_lh, 
                               pos_sig_age_betas_rh, makecmap_options = makecmap_options, "inflated", views="t4", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)
  }
}
#do the min
for (j in 1:dim(combinations)[2]){
  set=combinations[,j]
  #take the rows from vis and the columns from SM (and vice-versa?)
  #View(edge_age_betas_mat[rownames(edge_age_betas_mat)==set[1],colnames(edge_age_betas_mat)==set[2]])
  #rows <- which(rownames(edge_age_betas_mat)==set[1], arr.ind = T);cols <- which(colnames(edge_age_betas_mat)==set[2], arr.ind = T)
  colmax=rep(0,400)
  rowmax=rep(0,400)
  indices=which(rownames(edge_age_betas_mat)==set[1])
  for (x in indices){
      rowmax[x] <- min(edge_age_betas_mat[x,which(colnames(edge_age_betas_mat)==set[2])], na.rm = T)
  }
  indices=which(colnames(edge_age_betas_mat)==set[2])
  for (x in indices){
      colmax[x] <- min(edge_age_betas_mat[rownames(edge_age_betas_mat)==set[1],x], na.rm = T)
  }
  #Plot only in one community at a time
  for (community in set){
    values=colmax+rowmax  #these two vectors should be non-overlapping, for the combinations of communities, so can add them together
    print(community)
  values=ifelse(communities==community,values,0)
  pos_sig_age_betas_lh=as.list(setNames(c(0, values[1:200]), schaefer_atlas_region_names_lh))
  pos_sig_age_betas_rh=as.list(setNames(c(0, values[201:400]), schaefer_atlas_region_names_rh))
  #colormap
  colFn_diverging = colorRampPalette(c("blue","lightblue","white","white"));makecmap_options=list('colFn'=colFn_diverging)
  rglactions=list("snapshot_png"=paste0(output_image_directory,"/pairwise_comm_age_connectivity/min_sig_neg_age_betas_for_parcel_",set[1],set[2],"_regions_in",community,"_",pvalue,".png"))
  vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  pos_sig_age_betas_lh, 
                               pos_sig_age_betas_rh, makecmap_options = makecmap_options, "inflated", views="t4", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)
  }
}

#Do with the within-community edges
combinations=rbind(unique(communities),unique(communities))
#do the max
for (j in 1:dim(combinations)[2]){
  set=combinations[,j]
  rowmax=rep(0,400)
  indices=which(rownames(edge_age_betas_mat)==set[1])
  for (x in indices){
      rowmax[x] <- max(edge_age_betas_mat[x,which(colnames(edge_age_betas_mat)==set[2])], na.rm = T)
  }
  pos_sig_age_betas_lh=as.list(setNames(c(0, rowmax[1:200]), schaefer_atlas_region_names_lh))
  pos_sig_age_betas_rh=as.list(setNames(c(0, rowmax[201:400]), schaefer_atlas_region_names_rh))
  #colormap
  colFn_diverging = colorRampPalette(c("white","white","orange","red"));makecmap_options=list('colFn'=colFn_diverging)
  rglactions=list("snapshot_png"=paste0(output_image_directory,"max_sig_pos_age_betas_for_parcel_",set[1],set[2],"_regions_",pvalue,".png"))
  vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  pos_sig_age_betas_lh, 
                               pos_sig_age_betas_rh, makecmap_options = makecmap_options, "inflated", views="t4", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)
}
#do the min
for (j in 1:dim(combinations)[2]){
  set=combinations[,j]
  rowmax=rep(0,400)
  indices=which(rownames(edge_age_betas_mat)==set[1])
  for (x in indices){
      rowmax[x] <- min(edge_age_betas_mat[x,which(colnames(edge_age_betas_mat)==set[2])], na.rm = T)
  }
  pos_sig_age_betas_lh=as.list(setNames(c(0, rowmax[1:200]), schaefer_atlas_region_names_lh))
  pos_sig_age_betas_rh=as.list(setNames(c(0, rowmax[201:400]), schaefer_atlas_region_names_rh))
  #colormap
  colFn_diverging = colorRampPalette(c("blue","lightblue","white","white"));makecmap_options=list('colFn'=colFn_diverging)
  rglactions=list("snapshot_png"=paste0(output_image_directory,"min_sig_neg_age_betas_for_parcel_",set[1],set[2],"_regions_",pvalue,".png"))
  vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  pos_sig_age_betas_lh, 
                               pos_sig_age_betas_rh, makecmap_options = makecmap_options, "inflated", views="t4", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)
}
```

## Non-linear effects across edges

Where are there non-linear effects of age, if anywhere.
```{r edgewise gam models}
library(mgcv)
library(RLRsim)
library(parallel)
#Read back in the matrix of edges, so you don't create every time.
n92_all_edges<- readRDS("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/n92_all_edges.Rdata");n92_all_edges <- n92_all_edges[,-1]
#read back in subject data
pipeline='gsr_spkreg_fd0.5dvars1.75_drpvls'
network_dir=paste0("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/",pipeline)
load(paste0(network_dir,"/CBPD_n92_schaefer400_allruns.Rdata"))

#multi-core apply the exactRLRT test for non-linear model across the matrix of edges, get age non-lin pvals 
edgewise_age_nonlin_pvals<- mclapply(1:79800, function(x) {exactRLRT(gamm(n92_all_edges[,x]~s(main_unique$age_scan)+main_unique$male+main_unique$fd_mean_avg+main_unique$avgweight+main_unique$totalSizet, method = "REML")$lme)$p.value}, mc.cores = 4)
edgewise_age_nonlin_pvals <- unlist(edgewise_age_nonlin_pvals)
#save for reloading in future
save(edgewise_age_nonlin_pvals,file= "~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/edgewise_age_nonlin_pvals_n92.Rdata")

#load back in edge age effects
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/edgewise_age_nonlin_pvals_n92.Rdata")

#code to read back into a 400 x 400 matrix! This works correctly.
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400)
edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_nonlin_pvals #take uncorrected p-values for now
#copy lower triangle to upper triangle
#edge_age_pvals_mat[upper.tri(edge_age_pvals_mat)] <- t(edge_age_pvals_mat)[upper.tri(edge_age_pvals_mat)]

#Use different pval thresholds and plot parcels that have age-nonlin-sig edges at that threshold
pvalues=c(0.01,0.001,0.0001,0.00001)
for (pvalue in pvalues){
indices <- which(edge_age_pvals_mat<pvalue, arr.ind = T) #indices of edges that have age effects  below a pval
l <- data.frame(table(indices)) #for each parcel, how many age-significant edges does it have at a given pval thresh--indices gives duplicates!
values <- vector(mode = "double", 400)
for (i in 1:400){
values[as.numeric(as.character(l$indices[i]))] <- l$Freq[i]#replace the indices in values with the num of sig edges from that parcel in the table
}
num_of_sig_age_edges_lh=as.list(setNames(c(0, values[1:200]), schaefer_atlas_region_names_lh))
num_of_sig_age_edges_rh=as.list(setNames(c(0, values[201:400]), schaefer_atlas_region_names_rh))
#colormap
colFn_diverging = colorRampPalette(c("white","#7502E3"));makecmap_options=list('colFn'=colFn_diverging, 'range'=c(0,10)) #purple="#7502E3"
rglactions=list("snapshot_png"=paste0(output_image_directory,"age_nonlin_pvals_", pvalue,"regions.png"))
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  num_of_sig_age_edges_lh, 
                             num_of_sig_age_edges_rh, makecmap_options = makecmap_options, "inflated", views="t4", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)
}

#What do these edges look like pattern-wise?
sum(edgewise_age_nonlin_pvals<0.001)/length(edgewise_age_nonlin_pvals) #percentage
which(edgewise_age_nonlin_pvals<0.0001)
#make a big plot of them
par(mfrow=c(4,3))
lapply(which(edgewise_age_nonlin_pvals<0.0001), function(x) {plot(gam(n92_all_edges[,x]~s(main_unique$age_scan, k=4)+main_unique$male+main_unique$fd_mean_avg+main_unique$avgweight+main_unique$totalSizet, method = "REML"), ylab="edge", xlab="age", residuals=T);summary(gam(n92_all_edges[,x]~s(main_unique$age_scan, k=4)+main_unique$male+main_unique$fd_mean_avg+main_unique$avgweight+main_unique$totalSizet, method = "REML"))})
```

## Are these long or short-distance edges?

First, need to compute the distance matrix for Schaefer400 (distances between centroids), then could sort out significant edges based on distance.

## Compare cosine similarity across significance levels for nodes

Need to use Rick's Matlab code to make null models. Or use some kind of null model--maybe first just use different random pairs of parcels.

Also--would do this on the average matrix (Do I already have this on the cluster? If not, make it), and not the subject matrices? Seems like so.
For a given significance level, take the sig parcels and compute cosine similarity between pairs of connectivity profiles->mean or distribution
Then, compare that to consine similarity between those same pairs of parcels but on randomized null networks generated using Rick's code, or to random pairs of parcels as a less stringent test.
```{r make average FC matrix}
edges_dir=paste0("/cbica/home/tooleyu/projects/in_progress/within_between_network_conn_CBPD/data/imageData/",pipeline,"/schaefer400zNetworks_avg/")
#get adj matrix files
files <- data.frame(list.files(edges_dir)) %>% filter( list.files.edges_dir. %in% paste0(main_unique$ID, "_schaefer400MNI_zavgnetwork.txt")); files$list.files.edges_dir. <- paste0(edges_dir,files$list.files.edges_dir.)
#make an average matrix
summed=matrix(0,400,400)
for (i in 1:dim(main_unique)[1]){
mat <- as.matrix(read_csv(file =paste0(edges_dir,main_unique$ID[i], "_schaefer400MNI_zavgnetwork.txt"), col_names = F))
summed<- summed+mat
}
average <- summed/dim(main_unique)[1]
#save for reloading in future
write.csv(average,file= "~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/n92_average_zscored_FC_matrix.csv", row.names = F)
```

Note: rewrote this code in mid-May to do the analysis separating out the edges with positive age effects from the edges with negative age effects and computing their similarity separately.

```{r cosine similarity between significant age nodes, first with all edges, then only significant edges}
library(lsa) #for cosine similarity
#read in average matrix
average_FC_mat <- as.matrix(read.csv("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/n90_average_zscored_FC_matrix.csv"))
#load back in edge age effects
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/edgewise_age_effects_all_cov.Rdata")
#make a matrix
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400);edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1] #take uncorrected p-values for now
edge_age_pvals_mat[upper.tri(edge_age_pvals_mat)] <- t(edge_age_pvals_mat)[upper.tri(edge_age_pvals_mat)]
#put betas in matrix
edge_age_betas_mat <- matrix(nrow = 400, ncol=400);edge_age_betas_mat[lower.tri(edge_age_betas_mat, diag=FALSE)] <- edgewise_age_betas #take uncorrected p-values for now
edge_age_betas_mat[upper.tri(edge_age_betas_mat)] <- t(edge_age_betas_mat)[upper.tri(edge_age_betas_mat)]

#Use different pval thresholds and plot parcels that have age-nonlin-sig edges at that threshold
pos_edges <- edge_age_pvals_mat;pos_edges[edge_age_betas_mat<0] <- NA
neg_edges <- edge_age_pvals_mat;neg_edges[edge_age_betas_mat>0] <- NA
#separate into edges that have positive sig age effects and edges that have negative
sig_parcel_cosine=vector()
#skip 0.01 for now, because it's really big
pvalues=c(0.01, 0.001,0.0001,0.00001)
for (pvalue in pvalues){
  #i=1
  sig_parcel_cosine=vector()
indices <- which(neg_edges<pvalue, arr.ind = T) #indices of edges that have age effects below a pval
#plot them on a brain
  l <- data.frame(table(indices)) #for each parcel, how many age-significant edges does it have at a given pval thresh--indices gives duplicates!
  values <- vector(mode = "double", 400)
  for (i in 1:400){
  values[as.numeric(as.character(l$indices[i]))] <- l$Freq[i]#replace the indices in values with the num of sig edges from that parcel in the table
  }
  num_of_sig_age_edges_lh=as.list(setNames(c(0, values[1:200]), schaefer_atlas_region_names_lh));num_of_sig_age_edges_rh=as.list(setNames(c(0, values[201:400]), schaefer_atlas_region_names_rh))
  colFn_diverging = colorRampPalette(c("white","blue"));makecmap_options=list('colFn'=colFn_diverging) #, 'range'=c(0,80)) #change range here to display!
  rglactions=list("snapshot_png"=paste0(output_image_directory,"age_pvals_neg_only_", pvalue,"regions.png"))
  vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  num_of_sig_age_edges_lh, 
                               num_of_sig_age_edges_rh, makecmap_options = makecmap_options, "inflated", views="t4", draw_colorbar = T, rgloptions = rgloptions, rglactions = NULL)
for (x in 1:dim(indices)[1]){
  #for (y in indices[,2]){ #for looking at all edges that are connected to a parcel
    sig_parcel_cosine[x] <- cosine(average_FC_mat[,indices[x,1]], average_FC_mat[,indices[x,2]])#take both columns
    #i <- i+1
  #}
}
assign(paste0("sig_parcel_",pvalue,"cosine"), sig_parcel_cosine[sig_parcel_cosine!=1]) #each cosine value has a duplicate?
}
sig_parcel_edges_only_0.01cosine <- sig_parcel_0.01cosine
sig_parcel_edges_only_0.001cosine <- sig_parcel_0.001cosine
sig_parcel_edges_only_0.0001cosine <- `sig_parcel_1e-04cosine`
sig_parcel_edges_only_0.00001cosine <- `sig_parcel_1e-05cosine`
save(sig_parcel_edges_only_0.001cosine, sig_parcel_edges_only_0.0001cosine, sig_parcel_edges_only_0.00001cosine, file="~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/cosine_similarity_edges_only_data.Rdata")
load(file="~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/cosine_similarity_data.Rdata")

null_parcel_cosine=vector()
pvalues=c(0.01,0.001,0.0001,0.00001)
for (pvalue in pvalues){
  i=1
  null_parcel_cosine=vector()
indices <- which(neg_edges<pvalue, arr.ind = T) #indices of edges that have age effects  below a pval
indices[,1] <- sample(1:400,dim(indices)[1], replace = T)#replace with random integers 1-400
indices[,2] <- sample(1:400,dim(indices)[1], replace = T)#replace with random integers 1-400
for (x in 1:dim(indices)[1]){
  #for (y in indices[,2]){
    #null_parcel_cosine[i] <- print(cosine(average_FC_mat[,x], average_FC_mat[,y]))#take both columns
    null_parcel_cosine[x] <- cosine(average_FC_mat[,indices[x,1]], average_FC_mat[,indices[x,2]])
    #i <- i+1
  #}
}
assign(paste0("null_parcel_",pvalue,"cosine"), null_parcel_cosine[null_parcel_cosine!=1]) #each cosine value has a duplicate?
}
null_parcel_edges_only_0.01cosine <- null_parcel_0.01cosine
null_parcel_edges_only_0.001cosine <- null_parcel_0.001cosine
null_parcel_edges_only_0.0001cosine <- `null_parcel_1e-04cosine`
null_parcel_edges_only_0.00001cosine <- `null_parcel_1e-05cosine`
save(null_parcel_edges_only_0.001cosine, null_parcel_edges_only_0.0001cosine, null_parcel_edges_only_0.00001cosine, file="~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/cosine_similarity_null_edges_only_data.Rdata")

load(file="~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/cosine_similarity_null_edges_only_data.Rdata")
#plot the difference
pvalues=c("0.001","0.0001","0.00001")
for (pvalue in pvalues){
plt <- ggplot() + theme_classic()+
  geom_density(aes(x=get(paste0("null_parcel_edges_only_",pvalue,"cosine")), ..count..),fill="purple", alpha=0.2) + 
  geom_density(aes(x=get(paste0("sig_parcel_edges_only_",pvalue,"cosine")),..count..),fill="red", alpha=0.2)+ ggtitle(paste0("Connectivity similarity of parcels w/ pos age FC effects at p <",pvalue)) +
  labs(y= "Number of pairs of parcels", x = "Cosine similarity between parcel connectivity")
print(plt)
print(t.test(get(paste0("sig_parcel_edges_only_",pvalue,"cosine")), get(paste0("null_parcel_edges_only_",pvalue,"cosine"))))
}
```

# Surface Area Models

```{r get average SA for each subject}
library(fsbrain)
library(freesurferformats)
subjects_list <- main_unique$ID
subjects_dir = "/cbica/projects/cbpd_main_data/CBPD_bids_crosssectional/derivatives/freesurfer/"

#get mean thickness and area for these subjects
n90_average_wholebrain_data = group.multimorph.agg.native(subjects_dir, subjects_list, c("thickness", "area"),
     c("lh", "rh"), cast=FALSE, cortex_only=TRUE, agg_fun=mean,
     agg_fun_extra_params=list("na.rm"=TRUE));
#save it
save(n90_average_wholebrain_data, file="~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/mean_thickness_SA_n90.Rdata")
#load it
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/mean_thickness_SA_n90.Rdata")
#plot mean whole-brain with age
brain_data <- left_join(rename(n90_average_wholebrain_data, ID=subject_id), main_unique, by="ID") %>% mutate(mean_SA=(rh.area+lh.area)/2, mean_CT=(rh.thickness+lh.thickness)/2)
summary(lm(mean_SA~age_scan+male+t1_rating_avg, data=brain_data))
summary(lm(mean_CT~age_scan+male+t1_rating_avg, data=brain_data))
visreg(lm(mean_SA~age_scan+male+t1_rating_avg, data=brain_data), main= "Surface Area")

#get raw SA
n90_total_SA_wholebrain_data = group.multimorph.agg.native(subjects_dir, subjects_list, "area",
     c("lh", "rh"), cast=FALSE, cortex_only=TRUE, agg_fun=sum,
     agg_fun_extra_params=list("na.rm"=TRUE));
#save it
save(n90_total_SA_wholebrain_data, file="~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/total_SA_n90.Rdata")
#save it
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/total_SA_n90.Rdata") 
n90_total_SA_wholebrain_data <- left_join(main_unique, mutate(n90_total_SA_wholebrain_data, total_SA=rh.area+lh.area), by="ID")
summary(lm(total_SA~age_scan+male+t1_rating_avg, data=n90_total_SA_wholebrain_data))
visreg(lm(total_SA~age_scan+male+t1_rating_avg, data=n90_total_SA_wholebrain_data), main= "Total Surface Area")
```

## Run age models with edited SA

The R function in fsbrain called `group.agg.atlas.native` will get SA within each parcel with an annot file.
However, this function looks like it computes surface area within each parcel itself, based on the annotation file I wrote with mri_surf2surf, meaning that the mri_segstats I ran was not needed. 
These values don't match those generated by mri_segstats, though.

```{r get raw SA age effect within Schaefer400 parcels for edited subjects}
library(stringi)
#EXCLUDE SOME SUBJECTS?! CBPD0113, CBPD0169, CBPD0054?
#t1 data
lh <- read.delim("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/schaefer400_lh_surfarea_stats.txt") %>% rename(.,ID=lh.schaefer400_7nets.surfarea.area);rh <- read.delim("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/schaefer400_rh_surfarea_stats.txt")%>% rename(.,ID=rh.schaefer400_7nets.surfarea.area)
#t2
lh2 <- read.delim("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t2/schaefer400_lh_surfarea_stats.txt") %>% rename(.,ID=lh.schaefer400_7nets.surfarea.area) %>% mutate(ID=paste0(ID,"2"));rh2 <- read.delim("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t2/schaefer400_rh_surfarea_stats.txt")%>% rename(.,ID=rh.schaefer400_7nets.surfarea.area)%>% mutate(ID=paste0(ID,"2"))
#t3
lh3 <- read.delim("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t3/schaefer400_lh_surfarea_stats.txt") %>% rename(.,ID=lh.schaefer400_7nets.surfarea.area)%>% mutate(ID=paste0(ID,"3"));rh3 <- read.delim("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t3/schaefer400_rh_surfarea_stats.txt")%>% rename(.,ID=rh.schaefer400_7nets.surfarea.area)%>% mutate(ID=paste0(ID,"3"))
lh <- rbind(lh,lh2,lh3)
rh <- rbind(rh,rh2,rh3)
main <- read.csv("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/subjectData/CBPD_data_DMD_2020.05.22_UNOFFICIAL_mergedPITMRIdropout.csv") %>% mutate(ID=paste0("sub-",sub("_","",record_id))) %>% mutate(base_ID= stri_split(record_id,fixed="_", simplify=T)[,1])
#full subject list, not just t1
n126_parcel_SA_data <- left_join(lh,main,by="ID")
n126_parcel_SA_data <- left_join(rh,n126_parcel_SA_data,by="ID")
#raw surface area in mm2
n92_parcel_SA_data <- left_join(main_unique,lh, by= "ID")
n92_parcel_SA_data <- left_join(n92_parcel_SA_data,rh, by= "ID")
#n92_parcel_SA_data <- n92_parcel_SA_data %>% select(-lh_1_area, rh_1_area)

#get total SA using this approach
n92_parcel_SA_data$sum_parcel_area <- rowSums(n92_parcel_SA_data[,1646:2047]) 
#need to exclude medial wall from this calculation
summary(lm(sum_parcel_area~age_scan+male+t1_rating_avg, data=n92_parcel_SA_data))

visreg(lm(sum_parcel_area~age_scan+male+t1_rating_avg, data=n92_parcel_SA_data), main= "Total Surface Area")
exactRLRT(gamm(sum_parcel_area~s(age_scan)+male+t1_rating_avg, data = n92_parcel_SA_data, method = "REML")$lme)
visreg(gam(sum_parcel_area~s(age_scan)+male+t1_rating_avg, data = n92_parcel_SA_data, method = "REML"), main="Summed total SA")

summary(gam(sum_parcel_area~s(age_scan, k=4, fx=T)+male+t1_rating_avg, data = n92_parcel_SA_data, method = "REML"), main="Summed total SA")
visreg(gam(sum_parcel_area~s(age_scan, k=4, fx=F)+male+t1_rating_avg, data = n92_parcel_SA_data, method = "REML"), main="Summed total SA")

#plot mean whole-brain with age
main_unique$age_scan_sq <- (n92_parcel_SA_data$age_scan)^2
parcel_SA_pvals<- lapply(names(n92_parcel_SA_data[,1646:2047]), function(x) { summary(lm(as.formula(paste0(x,"~age_scan+male+t1_rating_avg")), data=n92_parcel_SA_data))$coef[2,4]})
parcel_SA_pvals <- unlist(parcel_SA_pvals)
parcel_SA_pvals_fdr <- cbind(parcel_SA_pvals,p.adjust(parcel_SA_pvals,method = "fdr"))
#get age betas
parcel_SA_betas<- lapply(names(n92_parcel_SA_data[,1646:2047]), function(x) { lm.beta(lm(as.formula(paste0(x,"~age_scan+male+t1_rating_avg")), data=n92_parcel_SA_data))$standardized.coefficients[[2]]})
parcel_SA_betas <- unlist(parcel_SA_betas)

#save for reloading in future
save(n92_parcel_SA_data,parcel_SA_pvals_fdr, parcel_SA_betas, file="~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/parcel_SA_motion_n92.Rdata")
```

# Use full SA sample
```{full edited sample}
n126_parcel_SA_data$male <- as.factor(n126_parcel_SA_data$male)
#get total SA using this approach
n126_parcel_SA_data$sum_parcel_area <- rowSums(n126_parcel_SA_data[,2:403]) 
#need to exclude medial wall from this calculation
summary(lm(sum_parcel_area~age_scan+male+t1_rating_avg, data=n126_parcel_SA_data))

visreg(lm(sum_parcel_area~age_scan+male+t1_rating_avg, data=n126_parcel_SA_data), main= "Total Surface Area")
exactRLRT(gamm(sum_parcel_area~s(age_scan)+male+t1_rating_avg, data = n126_parcel_SA_data, method = "REML")$lme)
visreg(gam(sum_parcel_area~s(age_scan)+male+t1_rating_avg, data = n126_parcel_SA_data, method = "REML"), main="Summed total SA")

summary(gam(sum_parcel_area~s(age_scan, k=4, fx=T)+male+t1_rating_avg, data = n126_parcel_SA_data, method = "REML"), main="Summed total SA")
visreg(gam(sum_parcel_area~s(age_scan, k=4, fx=F)+male+t1_rating_avg, data = n126_parcel_SA_data, method = "REML"), main="Summed total SA")

#plot mean whole-brain with age
parcel_SA_pvals<- lapply(names(n126_parcel_SA_data[,2:403]), function(x) { summary(lm(as.formula(paste0(x,"~age_scan+male+t1_rating_avg")), data=n126_parcel_SA_data))$coef[2,4]})
parcel_SA_pvals <- unlist(parcel_SA_pvals)
parcel_SA_pvals_fdr <- cbind(parcel_SA_pvals,p.adjust(parcel_SA_pvals,method = "fdr"))
#get age betas
parcel_SA_betas<- lapply(names(n126_parcel_SA_data[,2:403]), function(x) { lm.beta(lm(as.formula(paste0(x,"~age_scan+male+t1_rating_avg")), data=n126_parcel_SA_data))$standardized.coefficients[[2]]})
parcel_SA_betas <- unlist(parcel_SA_betas)

#save for reloading in future
save(parcel_SA_pvals_fdr, parcel_SA_betas, file="~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/parcel_SA_age_n126.Rdata")
```

## Run SA without the --accumulate flag

```{r get raw SA age effect within Schaefer400 parcels for edited subjects}
#EXCLUDE SOME SUBJECTS?! CBPD0113, CBPD0169, CBPD0054?
#t1 data
lh <- read.delim("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/schaefer400_lh_surfarea_noaccumulate_stats.txt") %>% rename(.,ID=Measure.mean);rh <- read.delim("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/schaefer400_rh_surfarea_noaccumulate_stats.txt")%>% rename(.,ID= Measure.mean)
#t2
lh2 <- read.delim("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t2/schaefer400_lh_surfarea_noaccumulate_stats.txt") %>% rename(.,ID=  Measure.mean) %>% mutate(ID=paste0(ID,"2"));rh2 <- read.delim("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t2/schaefer400_rh_surfarea_noaccumulate_stats.txt")%>% rename(.,ID=  Measure.mean)%>% mutate(ID=paste0(ID,"2"))
#t3
lh3 <- read.delim("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t3/schaefer400_lh_surfarea_noaccumulate_stats.txt") %>% rename(.,ID=  Measure.mean)%>% mutate(ID=paste0(ID,"3"));rh3 <- read.delim("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t3/schaefer400_rh_surfarea_noaccumulate_stats.txt")%>% rename(.,ID=  Measure.mean)%>% mutate(ID=paste0(ID,"3"))
lh <- rbind(lh,lh2,lh3)
rh <- rbind(rh,rh2,rh3)
#raw surface area in mm2
n92_parcel_SA_data <- left_join(main_unique,lh, by= "ID")
n92_parcel_SA_data <- left_join(n92_parcel_SA_data,rh, by= "ID")
n92_parcel_SA_data <- n92_parcel_SA_data %>% select(-Background.FreeSurfer_Defined_Medial_Wall.x, Background.FreeSurfer_Defined_Medial_Wall.y)

#get total SA using this approach
n92_parcel_SA_data$sum_parcel_area <- rowSums(n92_parcel_SA_data[,1648:2049]) 
#need to exclude medial wall from this calculation?
summary(lm(sum_parcel_area~age_scan+male+t1_rating_avg, data=n92_parcel_SA_data))

visreg(lm(sum_parcel_area~age_scan+male+t1_rating_avg, data=n92_parcel_SA_data), main= "Total Surface Area")
exactRLRT(gamm(sum_parcel_area~s(age_scan)+male+t1_rating_avg, data = n92_parcel_SA_data, method = "REML")$lme)
visreg(gam(sum_parcel_area~s(age_scan)+male+t1_rating_avg, data = n92_parcel_SA_data, method = "REML"), main="Summed total SA")

summary(gam(sum_parcel_area~s(age_scan, k=4, fx=T)+male+t1_rating_avg, data = n92_parcel_SA_data, method = "REML"), main="Summed total SA")
visreg(gam(sum_parcel_area~s(age_scan, k=4, fx=T)+male+t1_rating_avg, data = n92_parcel_SA_data, method = "REML"), main="Summed total SA")

#plot mean whole-brain with age
parcel_SA_pvals<- lapply(names(n92_parcel_SA_data[,1646:2047]), function(x) { summary(lm(as.formula(paste0(x,"~age_scan+male+t1_rating_avg")), data=n92_parcel_SA_data))$coef[2,4]})
parcel_SA_pvals <- unlist(parcel_SA_pvals)
parcel_SA_pvals_fdr <- cbind(parcel_SA_pvals,p.adjust(parcel_SA_pvals,method = "fdr"))
#get age betas
parcel_SA_betas<- lapply(names(n92_parcel_SA_data[,1646:2047]), function(x) { lm.beta(lm(as.formula(paste0(x,"~age_scan+male+t1_rating_avg")), data=n92_parcel_SA_data))$standardized.coefficients[[2]]})
parcel_SA_betas <- unlist(parcel_SA_betas)

#save for reloading in future
save(parcel_SA_pvals_fdr, parcel_SA_betas, file="~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/parcel_SA_age_n92.Rdata")
```

```{r plot parcel-wise age SA effect}
library(viridis)
num_of_sig_age_edges_lh=as.list(setNames(parcel_SA_pvals[1:201], schaefer_atlas_region_names_lh)) #this has the medial wall in it.
num_of_sig_age_edges_rh=as.list(setNames(parcel_SA_pvals[202:402], schaefer_atlas_region_names_rh))
#colormap
colFn_diverging = colorRampPalette(magma(20,direction=-1));makecmap_options=list('colFn'=colFn_diverging)
rglactions=list("snapshot_png"=paste0(output_image_directory,"SA_age_pvals_edited_brains.png"))
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  num_of_sig_age_edges_lh, 
                             num_of_sig_age_edges_rh, makecmap_options = makecmap_options, "inflated", views="t4", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)

#plot only significant regions
parcel_SA_pvals_thresh <- ifelse(parcel_SA_pvals<0.01,parcel_SA_betas,NA)
num_of_sig_age_edges_lh=as.list(setNames(c(NA,parcel_SA_pvals_thresh[2:201]), schaefer_atlas_region_names_lh)) #this has the medial wall in it.
num_of_sig_age_edges_rh=as.list(setNames(c(NA,parcel_SA_pvals_thresh[203:402]), schaefer_atlas_region_names_rh))
#colormap
colormap= colorRampPalette(rev(RColorBrewer::brewer.pal(9, name="RdBu")));makecmap_options=list('colFn'=colormap)
rglactions=list("snapshot_png"=paste0(output_image_directory,"n92_SA_motion_thresh_betas.png"))
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  num_of_sig_age_edges_lh, 
                             num_of_sig_age_edges_rh, makecmap_options = makecmap_options, "inflated", views="t4", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)

#plot betas for significant regions
parcel_SA_betas_thresh <- ifelse(parcel_SA_pvals_fdr[,2]<0.05,parcel_SA_betas,NA)
num_of_sig_age_edges_lh=as.list(setNames(c(NA,parcel_SA_betas_thresh[2:201]), schaefer_atlas_region_names_lh)) #this has the medial wall in it.
num_of_sig_age_edges_rh=as.list(setNames(c(NA,parcel_SA_betas_thresh[203:402]), schaefer_atlas_region_names_rh))
colormap= colorRampPalette(rev(RColorBrewer::brewer.pal(9, name="RdBu")));makecmap_options=list('colFn'=colormap)
rglactions=list("snapshot_png"=paste0(output_image_directory,"n126_SA_age_betas_p0.05_fdr_thresh.png"))
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  num_of_sig_age_edges_lh, 
                             num_of_sig_age_edges_rh, makecmap_options = makecmap_options, "inflated", views="t4", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)

#plot just average SA across parcels
n92_parcel_SA_only <- n92_parcel_SA_data %>%ungroup %>%  select(lh_2_area:rh_201_area) %>% select(-rh_1_area)%>% as.matrix(.)
SA_vect <- colMeans(n92_parcel_SA_only, na.rm = T)
num_of_sig_age_edges_lh=as.list(setNames(c(NA,SA_vect[1:200]), schaefer_atlas_region_names_lh)) #this has the medial wall in it.
num_of_sig_age_edges_rh=as.list(setNames(c(NA,SA_vect[201:400]), schaefer_atlas_region_names_rh))
colormap= colorRampPalette(inferno(10, direction = -1));makecmap_options=list('colFn'=colormap)
rglactions=list("snapshot_png"=paste0(output_image_directory,"mean_SA_map.png"),'shift_hemis_apart'=TRUE)
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  num_of_sig_age_edges_lh, 
                             num_of_sig_age_edges_rh, makecmap_options = makecmap_options, "inflated", views="t9", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)
```

## Non-linear parcel SA effects too.

```{r parcel-wise gam models for SA}
library(mgcv)
library(RLRsim)

#apply the exactRLRT test for non-linear model across the parcels, get age non-lin pvals 
parcelwise_age_sa_nonlin_pvals<- lapply(names(n92_parcel_SA_data[,1666:2047]), function(x) {exactRLRT(gamm(as.formula(paste0(x,"~s(age_scan)+male+t1_rating_avg")), data = n92_parcel_SA_data, method = "REML")$lme)$p.value})
#parcelwise_age_sa_nonlin_pvals<- lapply(names(n92_parcel_SA_data[,1646:2047]), function(x) {summary(gam(as.formula(paste0(x,"~s(age_scan, k=4,fx=T)+male+t1_rating_avg")), data = n92_parcel_SA_data, method = "REML"))$s.table[1,4]}) Using p-values from the gam
parcelwise_age_sa_nonlin_pvals <- unlist(parcelwise_age_sa_nonlin_pvals)
parcelwise_age_sa_nonlin_pvals <- cbind(parcelwise_age_sa_nonlin_pvals,p.adjust(parcelwise_age_sa_nonlin_pvals,method = "fdr"))
parcelwise_age_sa_nonlin_pvals <- data.frame(parcelwise_age_sa_nonlin_pvals,names(n92_parcel_SA_data[,1666:2047]));colnames(parcelwise_age_sa_nonlin_pvals) <- c("pvalue","pvalue_fdr", "area")
#save for reloading in future
save(parcelwise_age_sa_nonlin_pvals,file= "~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/parcelwise_age_sa_n92_edited_nonlin_pvals.Rdata")

#load back in parcel SA age effects
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/parcelwise_age_sa_n92_edited_nonlin_pvals.Rdata")

#plot parcels that have age-nonlin-sig SA
parcelwise_age_sa_nonlin <- ifelse(parcelwise_age_sa_nonlin_pvals$pvalue <0.05,parcelwise_age_sa_nonlin_pvals$pvalue,NA)
num_of_sig_age_edges_lh=as.list(setNames(c(NA,parcels_SA_FS_effect[1:200]), schaefer_atlas_region_names_lh))
num_of_sig_age_edges_rh=as.list(setNames(c(NA, ,parcels_SA_FS_effect[201:400]), schaefer_atlas_region_names_rh))
#colormap
colFn_diverging = colorRampPalette(rev(c("white","orange", "red")));makecmap_options=list('colFn'=colFn_diverging)
rglactions=list("snapshot_png"=paste0(output_image_directory,"parcel_age_nonlin_sa_pvals.png"))
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  num_of_sig_age_edges_lh, 
                             num_of_sig_age_edges_rh, makecmap_options = makecmap_options, "inflated", views="t4", draw_colorbar = T, rgloptions = rgloptions, rglactions = NULL)

#What do these edges look like pattern-wise? UNUSED
which(parcelwise_age_sa_nonlin_pvals<0.05)
#make a big plot of them
par(mfrow=c(4,5))
lapply(which(parcelwise_age_sa_nonlin_pvals<0.05), function(x) {visreg(gam(as.formula(paste0(names(n92_parcel_SA_data[,1645+x]),"~s(age_scan, k=4, fx=T)+male+t1_rating_avg")), method = "REML", data=n92_parcel_SA_data), "age_scan", partial=T)})

```

## Are the edge and SA maps more similar than is expected by chance?
```{r similarity of edge and SA age effects}
library(lsa)
#load back in edge age effects
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/edgewise_age_effects_all_cov_n92.Rdata")
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400)
edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1] #take uncorrected p-values for now
edge_age_pvals_mat <- t(edge_age_pvals_mat)#copy lower triangle to upper triangle
#load in parcel SA age effects
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/parcel_SA_age_n92.Rdata")

#reload edges pvals mat
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400);edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1] #take uncorrected p-values for now
edge_age_pvals_mat <- t(edge_age_pvals_mat)
#for positive, take only the edge pvals that have positive betas associated with them 
links_to_show=edge_age_betas_mat>= 0;edge_age_pvals_mat[links_to_show==FALSE] <- NA


#for SA age effect pvalues
pvalues=c(0.01,0.001,0.0001)
for (pvalue in pvalues){
indices <- which(edge_age_pvals_mat<pvalue, arr.ind = T) #indices of edges that have age effects  below a pval
l <- data.frame(table(indices)) #for each parcel, how many age-significant edges does it have at a given pval thresh
values <- vector(mode = "double", 400)
for (i in 1:400){
values[as.numeric(as.character(l$indices[i]))] <- l$Freq[i]#replace the indices in values with the num of sig edges from that parcel in the table
}
#compare
edge_vector=values
SA_vector=parcel_SA_pvals_fdr[-c(1,202),1] #take out the medial wall #parcel_SA_pvals, or thresh of either of these
SA_vector=round(SA_vector,digits = 2)#need to round the pvalues or betas so they are not "singleton", e.g. all different
#SA_vector[is.na(SA_vector)] <- 0
similarity_metric<- cor(edge_vector, SA_vector) #or correlation, cosine similarity, or mahalabonois distance? Other distance metrics?
similarity_metric_perm <- numeric()
#create a null distribution
for (x in 1:10000){
  edge_vector_perm=sample(edge_vector, replace = F)
  SA_vector_perm=sample(SA_vector, replace = F)
  similarity_metric_perm[x] <- cor(edge_vector_perm, SA_vector_perm)
}
p<- ecdf(unlist(similarity_metric_perm))(similarity_metric)
hist(unlist(similarity_metric_perm), main = paste0("Correlation between FC edge age effects and SA pvalues, edge p < ",pvalue), 
     xlab = paste0("p=",p))
abline(v = similarity_metric, col="blue", lwd=3)
}

#for SA age effect betas
pvalues=c(0.01,0.001,0.0001,0.00001)
for (pvalue in pvalues){
indices <- which(edge_age_pvals_mat<pvalue, arr.ind = T) #indices of edges that have age effects  below a pval
l <- data.frame(table(indices)) #for each parcel, how many age-significant edges does it have at a given pval thresh
values <- vector(mode = "double", 400)
for (i in 1:400){
values[as.numeric(as.character(l$indices[i]))] <- l$Freq[i]#replace the indices in values with the num of sig edges from that parcel in the table
}
#compare
edge_vector=values
SA_vector=parcel_SA_betas[-c(1,202)] #take out the medial wall #parcel_SA_pvals, or thresh of either of these
SA_vector=round(SA_vector,digits = 2)#need to round the pvalues or betas so they are not "singleton", e.g. all different
#SA_vector[is.na(SA_vector)] <- 0
similarity_metric<- cor(edge_vector, SA_vector) #or correlation, cosine similarity, or mahalabonois distance? Other distance metrics?
similarity_metric_perm <- numeric()
#create a null distribution
for (x in 1:10000){
  edge_vector_perm=sample(edge_vector, replace = F)
  SA_vector_perm=sample(SA_vector, replace = F)
  similarity_metric_perm[x] <- cosine(edge_vector_perm, SA_vector_perm)
}
p<- ecdf(unlist(similarity_metric_perm))(similarity_metric)
hist(unlist(similarity_metric_perm), main = paste0("Cosine sim between FC edge age effects and SA betas, edge p < ",pvalue), 
     xlab = paste0("p=",p))
abline(v = similarity_metric, col="blue", lwd=3)
}
```

## Spin test of the edge and SA maps

Before running this code block, use the MATLAB function `centroid_extraction_sphere.m` to get the centroid coordinates on the Freesurfer sphere of each of the parcels in the Schaefer400 parcellation. That is needed as input to these functions.

```{r spin test edge and SA age effects}
source("~/Documents/tools/rotate_parcellation/R/rotate.parcellation.R")
source("~/Documents/tools/rotate_parcellation/R/perm.sphere.p.R")
library(matrixStats) #otherwise get rowMins error
#read in centroids of the Schaefer400 parcels
lh_centroids <- as.matrix(read.csv("~/Documents/tools/parcellations/lh.Schaefer400_7Nets_fsaverage6.centroids.csv", header = F));rh_centroids <- as.matrix(read.csv("~/Documents/tools/parcellations/rh.Schaefer400_7Nets_fsaverage6.centroids.csv", header = F))
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/rotations_schaefer400_fsaverage6_10000x.Rdata")
#SHOULD BE MASKING OUT MEDIAL WALL? Assuming that is first centroid for each
lh_centroids <- lh_centroids[-1,];rh_centroids <- rh_centroids[-1,];

#load back in edge age effects
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/edgewise_age_effects_all_cov_n92.Rdata")
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400)
edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1] #take uncorrected p-values for now
edge_age_pvals_mat <- t(edge_age_pvals_mat)#copy lower triangle to upper triangle
edge_age_betas_mat <- matrix(nrow = 400, ncol=400)
edge_age_betas_mat[lower.tri(edge_age_betas_mat, diag=FALSE)] <- edgewise_age_betas
edge_age_betas_mat[upper.tri( edge_age_betas_mat)] <- t(edge_age_betas_mat)[upper.tri( edge_age_betas_mat)]
pos_edges <- edge_age_pvals_mat;pos_edges[edge_age_betas_mat<0] <- NA
neg_edges <- edge_age_pvals_mat;neg_edges[edge_age_betas_mat>0] <- NA

pvalues=c(0.05,0.01,0.001,0.0001)
for (pvalue in pvalues){
  print(pvalue)
indices <- which(neg_edges<pvalue, arr.ind = T) #indices of edges that have age effects  below a pval
l <- data.frame(table(indices)) #for each parcel, how many age-significant edges does it have at a given pval thresh
values <- vector(mode = "double", 400)
for (i in 1:400){
values[as.numeric(as.character(l$indices[i]))] <- l$Freq[i]#replace the indices in values with the num of sig edges from that parcel in the table
}
#maps to compare
edge_vector=values

#other map of SA or CT
parcel_SA_pvals_thresh <- ifelse(parcel_SA_pvals_fdr[,1]<0.05,parcel_SA_pvals_fdr[,1],0)
#parcel_SA_betas_pos <- ifelse(parcel_SA_betas>0,parcel_SA_betas,0);parcel_SA_betas_pos <- parcel_SA_betas_pos[-c(1,202)]
#SA_vector=parcel_SA_pvals_thresh[-c(1,202)]
SA_vector=1-parcel_SA_pvals_fdr[-c(1,202),1] #parcel_SA_pvals uncorrected, or thresholded p-values
#SA_vector=round(SA_vector,2) #need to round?


#rotations<- rotate.parcellation(lh_centroids,rh_centroids,1000)
print(perm.sphere.p(edge_vector,SA_vector, rotations, "pearson"))
print(perm.sphere.p(edge_vector,parcel_SA_betas[-c(1,202)], rotations, "pearson"))

}
#save rotations so don't have to do
save(rotations,file= "~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/rotations_schaefer400_fsaverage6_1000x.Rdata")
```

## Average SA age effect within areas that show age-significant FC edge effects

Plot the average beta for SA within the areas that show age-significant FC effects

```{r average beta for SA age effects within age-sig regions}
#load back in edge age effects + SA betas
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/edgewise_age_effects_all_cov_n92.Rdata")
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400)
edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1] #take uncorrected p-values for now
edge_age_pvals_mat <- t(edge_age_pvals_mat)#copy lower triangle to upper triangle
edge_age_betas_mat <- matrix(nrow = 400, ncol=400)
edge_age_betas_mat[lower.tri(edge_age_betas_mat, diag=FALSE)] <- edgewise_age_betas
edge_age_betas_mat[upper.tri( edge_age_betas_mat)] <- t(edge_age_betas_mat)[upper.tri( edge_age_betas_mat)]
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/parcel_SA_age_n92.Rdata")

pvalues=c(0.01,0.001,0.0001,0.00001)
for (pvalue in pvalues){
  print(pvalue)
  remove(dat);dat <- data.frame()
  edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1]; edge_age_pvals_mat <- t(edge_age_pvals_mat)#copy lower triangle to upper triangle
  #to do for only positive or only negative edges
  #links_to_show=edge_age_betas_mat>= 0;edge_age_pvals_mat[links_to_show==FALSE] <- NA
  indices <- which(edge_age_pvals_mat<pvalue, arr.ind = T) #indices of edges that have age effects  below a pval
  l <- data.frame(table(indices)) #for each parcel, how many age-significant edges does it have at a given pval thresh
  # values <- vector(mode = "double", 400)
  # for (i in 1:400){
  # values[as.numeric(as.character(l$indices[i]))] <- l$Freq[i]#replace the indices in values with the num of sig edges from that parcel in the table
  # }
  betas_within <- parcel_SA_betas[as.numeric(as.character(l$indices))] #get SA betas at each age-sig parcel
  #betas_without <- parcel_SA_betas[-as.numeric(as.character(l$indices))] #get SA betas at each age-sig parcel
  dat<- data.frame(c(betas_within, parcel_SA_betas));colnames(dat) <- "data"; 
  dat$variable <- c(rep("Betas in age-sig", length(betas_within)), rep("All betas", length(parcel_SA_betas)))
  longdata = dat %>% dplyr::group_by(variable) %>% mutate(med = median(data))
  g <- ggplot(data = longdata, aes(y = data, x = variable, fill=med)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
  geom_point(aes(y = data, color = data), position = position_jitter(width = .15), size = .3, alpha = 0.5) +
  geom_boxplot(width = .1, guides = FALSE, outlier.shape = NA, alpha = 0.5) +
  #expand_limits(x = 5.25) +
  guides(fill = FALSE) +
  guides(color = FALSE) +
  # scale_color_manual(values=c("#4669dc","pink","purple")) +
  scale_color_distiller(palette="Blues", direction = 1) +
  scale_fill_distiller(palette="Blues", direction = 1) +
  #scale_color_gradient2(low="#FFFFFF",mid= "#FB6A4A", high="#67000D", midpoint= 0.475, aesthetics = c("color", "fill")) +
  coord_flip() + ggtitle(paste0("SA betas in areas showing \n age-associated FC remodeling at p <",pvalue))+
  theme_bw() +
  raincloud_theme
print(g)
  
print(t.test(betas_within, parcel_SA_betas))
print(wilcox.test(betas_within, parcel_SA_betas))
print(kruskal.test(data~variable, data = longdata))

plt <- ggplot() + theme_classic()+
  geom_density(aes(x=betas_within, ..count..),fill="purple", alpha=0.2) + 
  geom_density(aes(x=parcel_SA_betas,..count..),fill="red", alpha=0.2)+ ggtitle(paste0("SA betas within areas showing \n age-associated FC remodeling at p <",pvalue)) +
  labs(y= "Values", x = "Beta")
print(plt)
}

```

## Average edge FC age effect within areas that show uncorrected significant SA effects--parcel-wise
```{r average beta for FC age effects within age-sig SA regions}
#load data above
pvalue=0.001
links_to_show=edge_age_betas_mat<= 0;edge_age_pvals_mat[links_to_show==FALSE] <- NA
colmax=vector();rowmax=vector()
#indices <- which(ifelse(parcel_SA_pvals[,1]<0.01 & parcel_SA_betas > 0, 1, NA)==1)
indices <- which(parcel_CT_pvals_fdr[,2]<0.05, arr.ind = T) 
for (x in indices){
  b <- edge_age_betas_mat[x,][edge_age_pvals_mat[x,]<=0.001] 
  rowmax<-c(rowmax,b[!is.na(b)])
} 
#indices=which(colnames(edge_age_betas_mat)==set[2])
for (x in indices){
  b <- edge_age_betas_mat[,x][edge_age_pvals_mat[,x]<=0.001] 
  colmax<-c(colmax,b[!is.na(b)])
}
edge_effects_in_CT_areas <- c(colmax,rowmax)
distribution=list()
for (i in 1){
colmax=vector();rowmax=vector()
notindices <- sample(which(!parcel_CT_pvals_fdr[,2]<0.05, arr.ind = T), size=length(indices))
#notindices <- sample(which(is.na(ifelse(!parcel_SA_pvals[,1]<0.01 & parcel_SA_betas > 0, 1, NA))), size=length(indices))
for (x in notindices){
  b <- edge_age_betas_mat[x,][edge_age_pvals_mat[x,]<=0.001] 
  rowmax<-c(rowmax,b[!is.na(b)])
}
#indices=which(colnames(edge_age_betas_mat)==set[2])
for (x in notindices){
  b <- edge_age_betas_mat[,x][edge_age_pvals_mat[,x]<=0.001] 
  colmax<-c(colmax,b[!is.na(b)])
}
edge_effects_in_nonCT_areas <- c(colmax,rowmax)
distribution[[i]] <- edge_effects_in_nonCT_areas
}
hist(unlist(distribution)); hist(edge_effects_in_CT_areas)
print(t.test(edge_effects_in_CT_areas, edge_effects_in_nonCT_areas))
print(wilcox.test(edge_effects_in_CT_areas, edge_effects_in_nonCT_areas))
ks.test(edge_effects_in_CT_areas, ecdf(unlist(distribution)))
ecdf(unlist(distribution))

plt <- ggplot() + theme_classic()+
  geom_density(aes(x=edge_effects_in_CT_areas, ..scaled.. ),fill="purple", alpha=0.2) + 
  geom_density(aes(x=unlist(distribution),  ..scaled.. ),fill="red", alpha=0.2)+ ggtitle(paste0("Betas of age edge effects within areas showing sig \n age effects on CT at corrected p < 0.05")) +
  labs(y= "Values", x = "# of age-sig edges per parcel") 
print(plt)

pvalue=0.001
remove(dat);dat <- data.frame()
edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1]; edge_age_pvals_mat <- t(edge_age_pvals_mat)#copy lower triangle to upper triangle
edge_age_betas_mat[lower.tri(edge_age_betas_mat, diag=FALSE)] <- edgewise_age_betas; edge_age_betas_mat <- t(edge_age_betas_mat)#copy lower triangle to upper triangle
#to do for only positive or only negative edges
links_to_show=edge_age_pvals_mat< 0.05 & edge_age_betas_mat > 0;edge_age_betas_mat[links_to_show==FALSE] <- NA
#threshold for a given pval?
indices <- which(parcel_CT_pvals_fdr[,2]<0.05 & parcel_CT_betas < 0, arr.ind = T) #indices of edges that have age effects  below a pval
l <- data.frame(table(indices)) #for each parcel, how many age-significant edges does it have at a given pval thresh
edges_within <- c(edge_age_betas_mat[as.numeric(as.character(l$indices)),]) #get CT betas at each age-sig parcel
edges_without<- c(edge_age_betas_mat[-as.numeric(as.character(l$indices)),]) 
dat<- data.frame(c(edges_within, edges_without));colnames(dat) <- "data"; 
dat$variable <- c(rep("Edges in age-sig", length(edges_within)), rep("Other edges", length((edges_without))))
longdata = dat %>% dplyr::group_by(variable) %>% mutate(med = median(data, na.rm = T))
g <- ggplot(data = longdata, aes(y = data, x = variable, fill=med)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
  geom_point(aes(y = data, color = data), position = position_jitter(width = .15), size = .3, alpha = 0.5) +
  geom_boxplot(width = .1, guides = FALSE, outlier.shape = NA, alpha = 0.5) +
  #expand_limits(x = 5.25) +
  guides(fill = FALSE) +
  guides(color = FALSE) +
  # scale_color_manual(values=c("#4669dc","pink","purple")) +
  scale_color_distiller(palette="Blues", direction = 1) +
  scale_fill_distiller(palette="Blues", direction = 1) +
  #scale_color_gradient2(low="#FFFFFF",mid= "#FB6A4A", high="#67000D", midpoint= 0.475, aesthetics = c("color", "fill")) +
  coord_flip() + ggtitle(paste0("Edge FC betas in areas showing sig CT thinning \n thresh at p < 0.05"))+
  theme_bw() +
  raincloud_theme
print(g)
  
print(t.test(edges_within, edges_without))
print(wilcox.test(edges_within, edges_without))
kruskal.test(data~variable, data = longdata)
summary(lm(data~variable, data = longdata))

plt <- ggplot() + theme_classic()+
  geom_density(aes(x=edges_within, ..scaled..),fill="purple", alpha=0.2) + 
  geom_density(aes(x=edges_without,..scaled..),fill="red", alpha=0.2)+ ggtitle(paste0("Edge FC betas in areas showing sig CT thinning \n thresh at p < 0.05")) +
  labs(y= "Values", x = "Beta")
print(plt)
```

## Average edge FC age effect within areas that show significant age-sq SA effects in FS
```{r average beta for FC age effects within age-sq FS sig SA regions}
detach("package:plyr", unload=TRUE)
#load age on CT from FS
lh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/lh_area_agesq_age_sex_t1rating_fwhm10_n89/lh-Avg-area-age_sq-Cor/cache.th23.abs.sig.masked.mgh") #voxel-wise corrected?
#load schaefer parcellation at fsaverage res and average by parcel
schaefer_lh <-subject.annot(subjects_dir = subjects_dir,subject_id =subject_id, hemi="lh", atlas = atlas)
d <- data.frame(lh, schaefer_lh$label_names) %>% dplyr::rename(schaefer_atlas_region_names_lh=schaefer_lh.label_names) %>% group_by(schaefer_atlas_region_names_lh) %>% summarise(mean=mean(lh));
lh_parcels_SA <- left_join(data.frame(schaefer_atlas_region_names_lh),d, by= "schaefer_atlas_region_names_lh")
schaefer_rh <-subject.annot(subjects_dir = subjects_dir,subject_id =subject_id, hemi="rh", atlas = atlas)
rh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/rh_area_ageagesqsext1rating_fwhm10_n89/rh-Avg-area-age_sq-Cor/cache.th23.abs.sig.masked.mgh")
d <- data.frame(rh, schaefer_rh$label_names) %>% rename(schaefer_atlas_region_names_rh=schaefer_rh.label_names) %>% group_by(schaefer_atlas_region_names_rh) %>% summarise(mean=mean(rh));
rh_parcels_SA <- left_join(data.frame(schaefer_atlas_region_names_rh),d, by= "schaefer_atlas_region_names_rh")

parcels_SA_FS_effect <- c(lh_parcels_SA$mean,rh_parcels_SA$mean)[-c(1,202)]

#Different approach
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400)
edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1];edge_age_pvals_mat[upper.tri(edge_age_pvals_mat)] <- t(edge_age_pvals_mat)[upper.tri(edge_age_pvals_mat)]
edge_age_betas_mat <- matrix(nrow = 400, ncol=400)
edge_age_betas_mat[lower.tri(edge_age_betas_mat, diag=FALSE)] <- edgewise_age_betas;edge_age_betas_mat[upper.tri( edge_age_betas_mat)] <- t(edge_age_betas_mat)[upper.tri( edge_age_betas_mat)]
#to do for only positive or only negative edges
#links_to_show=edge_age_pvals_mat< 0.05 & edge_age_betas_mat > 0;edge_age_betas_mat[links_to_show==FALSE] <- NA
#threshold for a given pval?
indices <- which(parcels_SA_FS_effect!=0, arr.ind = T) #indices of edges that have age effects  below a pval
l <- data.frame(table(indices)) #for each parcel, how many age-significant edges does it have at a given pval thresh
edges_within <- c(edge_age_betas_mat[as.numeric(as.character(l$indices)),]) #get CT betas at each age-sig parcel
edges_without<- c(edge_age_betas_mat[-as.numeric(as.character(l$indices)),]) 
dat<- data.frame(c(edges_within, edges_without));colnames(dat) <- "data"; 
dat$variable <- c(rep("Edges in age-sig", length(edges_within)), rep("Other edges", length((edges_without))))
longdata = dat %>% dplyr::group_by(variable) %>% mutate(med = median(data, na.rm = T))
g <- ggplot(data = longdata, aes(y = data, x = variable, fill=med)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
  geom_point(aes(y = data, color = data), position = position_jitter(width = .15), size = .3, alpha = 0.5) +
  geom_boxplot(width = .1, guides = FALSE, outlier.shape = NA, alpha = 0.5) +
  #expand_limits(x = 5.25) +
  guides(fill = FALSE) +
  guides(color = FALSE) +
  # scale_color_manual(values=c("#4669dc","pink","purple")) +
  scale_color_distiller(palette="Blues", direction = 1) +
  scale_fill_distiller(palette="Blues", direction = 1) +
  #scale_color_gradient2(low="#FFFFFF",mid= "#FB6A4A", high="#67000D", midpoint= 0.475, aesthetics = c("color", "fill")) +
  coord_flip() + ggtitle(paste0("Edge FC betas in areas showing sig age-sq SA \n thresh at p < 0.05"))+
  theme_bw() +
  raincloud_theme
print(g)
  
print(t.test(edges_within, edges_without))
print(wilcox.test(edges_within, edges_without))
kruskal.test(data~variable, data = longdata)
summary(lm(data~variable, data = longdata))

plt <- ggplot() + theme_classic()+
  geom_density(aes(x=edges_within, ..scaled..),fill="blue", alpha=0.2) + 
  geom_density(aes(x=edges_without,..scaled..),fill="purple", alpha=0.2)+ ggtitle(paste0("Edge FC betas in areas showing sig CT thinning \n thresh at p < 0.05")) +
  labs(y= "Values", x = "Beta")
print(plt)
```

## CT models with edited brains
```{r get CT data}
library(fsbrain)
library(freesurferformats)
not_edited=c("sub-CBPD0054", "sub-CBPD0038","sub-CBPD0068","sub-CBPD0089","sub-CBPD0090","sub-CBPD0097","sub-CBPD0113","sub-CBPD0121")
subjects_list <- main_unique$ID[! main_unique$ID %in% not_edited]
subjects_dir = "/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/"

#get mean thickness for these subjects using fsbrain
n90_averageCT_edited_data = group.multimorph.agg.native(subjects_dir, subjects_list, "thickness",
     c("lh", "rh"), cast=FALSE, cortex_only=TRUE, agg_fun=mean,
     agg_fun_extra_params=list("na.rm"=TRUE));
#save it
save(n90_averageCT_edited_data, file="~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/mean_edited_CT_n90.Rdata")
#load it
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/mean_edited_CT_n90.Rdata")
#plot mean whole-brain with age
brain_data <- left_join(rename(n90, ID=subject_id), main_unique, by="ID") %>% mutate(mean_CT=(rh.thickness+lh.thickness)/2)
summary(lm(mean_CT~age_scan+male+t1_rating_avg, data=brain_data))
visreg(lm(mean_CT~age_scan+male+t1_rating_avg, data=brain_data), main= "Surface Area")

#get total SA using fsbrain
n90_edited_sum_SA_wholebrain_data = group.multimorph.agg.native(subjects_dir, subjects_list, "area",
     c("lh", "rh"), cast=FALSE, cortex_only=TRUE, agg_fun=sum,
     agg_fun_extra_params=list("na.rm"=TRUE));
#save it
save(n90_edited_sum_SA_wholebrain_data, file="~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/total_edited_SA_n90.Rdata")
#save it
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/total_edited_SA_n90.Rdata") 
n90_total_SA_wholebrain_data <- left_join(main_unique, mutate(n9, total_SA=rh.area+lh.area), by="ID")
summary(lm(total_SA~age_scan+male+t1_rating_avg, data=n90_total_SA_wholebrain_data))
visreg(lm(total_SA~age_scan+male+t1_rating_avg, data=n90_total_SA_wholebrain_data), main= "Total Surface Area")
```

## Run parcel-wise age models with CT

The R function in fsbrain called `group.agg.atlas.native` will get SA within each parcel with an annot file.
However, that function looks gets different values than those generated by mri_segstats, sometimes.

```{r get mean CT age effect within Schaefer400 parcels for each subject}
#t1 data
lh <- read.delim("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/schaefer400_lh_thickness_stats.txt") %>% rename(.,ID=Measure.mean) %>% select(-Background.FreeSurfer_Defined_Medial_Wall);rh <- read.delim("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/schaefer400_rh_thickness_stats.txt") %>% rename(.,ID=Measure.mean) %>% select(-Background.FreeSurfer_Defined_Medial_Wall);
#t2
lh2 <- read.delim("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t2/schaefer400_lh_thickness_stats.txt") %>% rename(.,ID=Measure.mean) %>% select(-Background.FreeSurfer_Defined_Medial_Wall)%>% mutate(ID=paste0(ID,"2"));rh2 <- read.delim("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t2/schaefer400_rh_thickness_stats.txt") %>% rename(.,ID=Measure.mean) %>% select(-Background.FreeSurfer_Defined_Medial_Wall)%>% mutate(ID=paste0(ID,"2"));
#t2
lh3 <- read.delim("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t3/schaefer400_lh_thickness_stats.txt") %>% rename(.,ID=Measure.mean) %>% select(-Background.FreeSurfer_Defined_Medial_Wall)%>% mutate(ID=paste0(ID,"3"));rh3 <- read.delim("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t3/schaefer400_rh_thickness_stats.txt") %>% rename(.,ID=Measure.mean) %>% select(-Background.FreeSurfer_Defined_Medial_Wall)%>% mutate(ID=paste0(ID,"3"));
lh <- rbind(lh,lh2,lh3)
rh <- rbind(rh,rh2,rh3)
#meanCT
n92_parcel_CT_data <- left_join(main_unique,lh, by= "ID")
n92_parcel_CT_data <- left_join(n92_parcel_CT_data,rh, by= "ID")

#get total SA using this approach
n92_parcel_CT_data$mean_parcel_CT <- rowMeans(n92_parcel_CT_data[,1646:2045])
summary(lm(mean_parcel_CT~age_scan*male+t1_rating_avg, data=n92_parcel_CT_data))
visreg(lm(mean_parcel_CT~age_scan*male+t1_rating_avg, data=n92_parcel_CT_data), main= "Total CT")
exactRLRT(gamm(mean_parcel_CT~s(age_scan)+male+t1_rating_avg, data = n92_parcel_CT_data, method = "REML")$lme)
visreg(gam(mean_parcel_CT~s(age_scan, k=4, fx=T)+male+t1_rating_avg, data = n92_parcel_CT_data, method = "REML"), main="Average whole-brain CT")

#plot mean whole-brain with age
parcel_CT_pvals<- lapply(names(n92_parcel_CT_data[,1646:2045]), function(x) { summary(lm(as.formula(paste0(x,"~age_scan+male+t1_rating_avg")), data=n92_parcel_CT_data))$coef[2,4]})
parcel_CT_pvals <- unlist(parcel_CT_pvals)
parcel_CT_pvals_fdr <- cbind(parcel_CT_pvals,p.adjust(parcel_CT_pvals,method = "fdr"))
#get age betas
parcel_CT_betas<- lapply(names(n92_parcel_CT_data[,1646:2045]), function(x) { lm.beta(lm(as.formula(paste0(x,"~age_scan+male+t1_rating_avg")), data=n92_parcel_CT_data))$standardized.coefficients[[2]]})
parcel_CT_betas <- unlist(parcel_CT_betas)

#save for reloading in future
save(n92_parcel_CT_data, parcel_CT_pvals_fdr, parcel_CT_betas, file="~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/parcel_CT_age_n92.Rdata")

#plot pvalues or betas for significant quality-affected regions
parcel_CT_betas_thresh <- ifelse(parcel_CT_pvals_fdr[,1]<0.05,parcel_CT_betas,NA)
num_of_sig_age_edges_lh=as.list(setNames(c(NA,parcel_CT_betas_thresh[1:200]), schaefer_atlas_region_names_lh)) #this has the medial wall in it.
num_of_sig_age_edges_rh=as.list(setNames(c(NA,parcel_CT_betas_thresh[201:400]), schaefer_atlas_region_names_rh))
colormap= colorRampPalette(rev(RColorBrewer::brewer.pal(9, name="RdBu")));makecmap_options=list('colFn'=colormap, 'symm'=T)
rglactions=list("snapshot_png"=paste0(output_image_directory,"CT_motion_thresh_FDR_betas.png"),'shift_hemis_apart'=TRUE)
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  num_of_sig_age_edges_lh, 
                             num_of_sig_age_edges_rh, makecmap_options = makecmap_options, "inflated", views="t9", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)

```

```{r plot parcel-wise age CT effect}
library(viridis)
num_of_sig_age_edges_lh=as.list(setNames(c(NA,parcel_CT_pvals[1:200]), schaefer_atlas_region_names_lh)) #this has the medial wall in it.
num_of_sig_age_edges_rh=as.list(setNames(c(NA,parcel_CT_pvals[201:400]), schaefer_atlas_region_names_rh))
#colormap
colFn_diverging = colorRampPalette(magma(20,direction=-1));makecmap_options=list('colFn'=colFn_diverging)
rglactions=list("snapshot_png"=paste0(output_image_directory,"CT_age_pvals.png"),'shift_hemis_apart'=TRUE)
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  num_of_sig_age_edges_lh, 
                             num_of_sig_age_edges_rh, makecmap_options = makecmap_options, "inflated", views="t9", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)

#plot only significant regions
parcel_CT_pvals_thresh <- ifelse(parcel_CT_pvals<0.05,parcel_CT_pvals,NA)
num_of_sig_age_edges_lh=as.list(setNames(c(NA,parcel_CT_pvals_thresh[1:200]), schaefer_atlas_region_names_lh)) #this has the medial wall in it.
num_of_sig_age_edges_rh=as.list(setNames(c(NA,parcel_CT_pvals_thresh[201:400]), schaefer_atlas_region_names_rh))
#colormap
colormap= colorRampPalette(rev(RColorBrewer::brewer.pal(9, name="OrRd")));makecmap_options=list('colFn'=colormap)
rglactions=list("snapshot_png"=paste0(output_image_directory,"CT_age_thresh_pvals.png"),'shift_hemis_apart'=TRUE)
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  num_of_sig_age_edges_lh, 
                             num_of_sig_age_edges_rh, makecmap_options = makecmap_options, "inflated", views="t9", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)

#plot betas for significant regions
parcel_CT_betas_thresh <- ifelse(parcel_CT_pvals_fdr[,2]<0.05,parcel_CT_betas,NA)
num_of_sig_age_edges_lh=as.list(setNames(c(NA,parcel_CT_betas_thresh[1:200]), schaefer_atlas_region_names_lh)) #this has the medial wall in it.
num_of_sig_age_edges_rh=as.list(setNames(c(NA,parcel_CT_betas_thresh[201:400]), schaefer_atlas_region_names_rh))
colormap= colorRampPalette(rev(RColorBrewer::brewer.pal(9, name="RdBu")));makecmap_options=list('colFn'=colormap)
rglactions=list("snapshot_png"=paste0(output_image_directory,"CT_age_thresh_FDR_betas.png"),'shift_hemis_apart'=TRUE)
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  num_of_sig_age_edges_lh, 
                             num_of_sig_age_edges_rh, makecmap_options = makecmap_options, "inflated", views="t9", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)

#plot just average CT across parcels
n92_parcel_CT_only <- n92_parcel_CT_data %>%ungroup %>%  select(X7Networks_LH_Vis_1:X7Networks_RH_Default_pCunPCC_9) %>% as.matrix(.)
CT_vect <- colMeans(n92_parcel_CT_only, na.rm = T)
num_of_sig_age_edges_lh=as.list(setNames(c(NA,CT_vect[1:200]), schaefer_atlas_region_names_lh)) #this has the medial wall in it.
num_of_sig_age_edges_rh=as.list(setNames(c(NA,CT_vect[201:400]), schaefer_atlas_region_names_rh))
colormap= colorRampPalette(inferno(10, direction = -1));makecmap_options=list('colFn'=colormap)
rglactions=list("snapshot_png"=paste0(output_image_directory,"mean_CT_map.png"),'shift_hemis_apart'=TRUE)
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  num_of_sig_age_edges_lh, 
                             num_of_sig_age_edges_rh, makecmap_options = makecmap_options, "inflated", views="t9", draw_colorbar = T, rgloptions = rgloptions, rglactions = NULL)
```

## Plot parcel-wise CT effects by network

```{CT parcel-wise effects by system}
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/parcel_CT_age_n92.Rdata")
community_assign <- read.delim("~/Documents/tools/parcellations/schaefer400x7CommunityAffiliation.1D", header = F)
communities <- paste0("comm",community_assign$V1) %>% car::recode(.,"'comm1'='Visual'; 'comm2'='Somatomotor' ; 'comm3'='Dorsal Attention';'comm4'='Ventral Attention';'comm5'='Limbic';'comm6'='Frontoparietal';'comm7'='Default'") %>% factor(levels=c("Visual","Somatomotor","Dorsal Attention", "Ventral Attention", "Limbic", "Frontoparietal", "Default")) 
toplot <- ifelse(parcel_CT_pvals_fdr[,2]<0.05,parcel_CT_betas,NA)
num_edges <- data.frame(factor(communities),toplot);colnames(num_edges) <- c("community","data"); 
longdata = num_edges %>% dplyr::group_by(community) %>% mutate(med = median(data))

g <- ggplot(data = longdata, aes(y = data, x = community, fill=community)) +
  geom_flat_violin(aes(y=data, color=community), position = position_nudge(x = .2, y = 0), alpha = .5) +
  geom_point(aes(y = data, color = community), position = position_jitter(width = .15), size = .3, alpha = 0.5) +
  #geom_boxplot(width = .3, guides = FALSE, outlier.shape = NA, alpha = 0.5) +
  guides(fill = FALSE) +
  guides(color = FALSE) +
  # scale_color_manual(values=c("#4669dc","pink","purple")) +
  #scale_color_distiller(palette="Blues", direction = 1) +
  #scale_fill_distiller(palette="Blues", direction = 1) +
  scale_color_manual(values=c("#7B287E", "#5CA1C8", "#0A9045","#C33AF8", "#B6C988", "#EF9C23", "#E34A53")) +
  scale_fill_manual(values= c("#7B287E", "#5CA1C8", "#0A9045","#C33AF8", "#B6C988", "#EF9C23", "#E34A53")) +
  #scale_color_gradient2(low="#FFFFFF",mid= "#FB6A4A", high="#67000D", midpoint= 0.475, aesthetics = c("color", "fill")) +
  theme_bw() +
  raincloud_theme
print(g)

#stats
kruskal.test(data~community, data = longdata)
pairwise.wilcox.test(longdata$data, longdata$community,
                     p.adjust.method = "bonferroni")
summary(lm(data~community,data=longdata))

```

## Spin test of the edge and CT maps

Before running this code block, use the MATLAB function `centroid_extraction_sphere.m` to get the centroid coordinates on the Freesurfer sphere of each of the parcels in the Schaefer400 parcellation. That is needed as input to these functions.

```{r spin test edge and CT age effects}
source("~/Documents/tools/rotate_parcellation/R/rotate.parcellation.R")
source("~/Documents/tools/rotate_parcellation/R/perm.sphere.p.R")
library(matrixStats) #otherwise get rowMins error
#read in centroids of the Schaefer400 parcels
lh_centroids <- as.matrix(read.csv("~/Documents/tools/parcellations/lh.Schaefer400_7Nets_fsaverage6.centroids.csv", header = F));rh_centroids <- as.matrix(read.csv("~/Documents/tools/parcellations/rh.Schaefer400_7Nets_fsaverage6.centroids.csv", header = F))
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/rotations_schaefer400_fsaverage6_10000x.Rdata")
#SHOULD BE MASKING OUT MEDIAL WALL? Assuming that is first centroid for each
lh_centroids <- lh_centroids[-1,];rh_centroids <- rh_centroids[-1,];
#load CT
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/parcel_CT_age_n92.Rdata")

#load back in edge age effects
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/edgewise_age_effects_all_cov_n92.Rdata")
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400)
edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1] #take uncorrected p-values for now
edge_age_pvals_mat <- t(edge_age_pvals_mat)#copy lower triangle to upper triangle
pos_edges <- edge_age_pvals_mat;pos_edges[edge_age_betas_mat<0] <- NA
neg_edges <- edge_age_pvals_mat;neg_edges[edge_age_betas_mat>0] <- NA

pvalues=c(0.05,0.01,0.001,0.0001)
for (pvalue in pvalues){
  print(pvalue)
indices <- which(pos_edges<pvalue, arr.ind = T) #indices of edges that have age effects  below a pval
l <- data.frame(table(indices)) #for each parcel, how many age-significant edges does it have at a given pval thresh
values <- vector(mode = "double", 400)
for (i in 1:400){
values[as.numeric(as.character(l$indices[i]))] <- l$Freq[i]#replace the indices in values with the num of sig edges from that parcel in the table
}
#maps to compare
edge_vector=values

#other map of CT
parcel_CT_pvals_thresh <- ifelse(parcel_CT_pvals_fdr[,2]<0.05,parcel_CT_pvals_fdr[,1],0)
CT_betas_vector=ifelse(parcel_CT_pvals_fdr[,2]<0.05, parcel_CT_betas,0)
CT_vector=1-parcel_CT_pvals_fdr[,1] #parcel_SA_pvals uncorrected, or thresholded p-values

#rotations<- rotate.parcellation(lh_centroids,rh_centroids,1000)
print(perm.sphere.p(edge_vector,CT_vector, rotations, "spearman"))
print(perm.sphere.p(edge_vector,parcel_CT_pvals_thresh, rotations, "spearman"))
print(perm.sphere.p(edge_vector,parcel_CT_betas, rotations, "spearman"))
print(perm.sphere.p(edge_vector,CT_betas_vector, rotations, "spearman"))
#print(perm.sphere.p(edge_vector,CT_betas_vector, rotations, "pearson"))
}
```

## Average CT age effect within areas that show age-significant FC edge effects

Plot the average beta for CT within the areas that show age-significant FC effects

```{r average beta for CT age effects within age-sig regions}
#load back in edge age effects + SA betas
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/edgewise_age_effects_all_cov_n92.Rdata")
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400)
edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1] #take uncorrected p-values for now
edge_age_pvals_mat <- t(edge_age_pvals_mat)#copy lower triangle to upper triangle
edge_age_betas_mat <- matrix(nrow = 400, ncol=400)
edge_age_betas_mat[lower.tri(edge_age_betas_mat, diag=FALSE)] <- edgewise_age_betas
edge_age_betas_mat[upper.tri( edge_age_betas_mat)] <- t(edge_age_betas_mat)[upper.tri( edge_age_betas_mat)]
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/parcel_CT_age_n92.Rdata")

pvalues=c(0.01,0.001,0.0001,0.00001)
for (pvalue in pvalues){
  print(pvalue)
  remove(dat);dat <- data.frame()
  edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1]; edge_age_pvals_mat <- t(edge_age_pvals_mat)#copy lower triangle to upper triangle
  #to do for only positive or only negative edges
  #links_to_show=edge_age_betas_mat<= 0;edge_age_pvals_mat[links_to_show==FALSE] <- NA
  indices <- which(edge_age_pvals_mat<pvalue, arr.ind = T) #indices of edges that have age effects  below a pval
  l <- data.frame(table(indices)) #for each parcel, how many age-significant edges does it have at a given pval thresh
  # values <- vector(mode = "double", 400)
  # for (i in 1:400){
  # values[as.numeric(as.character(l$indices[i]))] <- l$Freq[i]#replace the indices in values with the num of sig edges from that parcel in the table
  # }
  betas_within <- parcel_CT_betas[as.numeric(as.character(l$indices))] #get CT betas at each age-sig parcel
  betas_without<- parcel_CT_betas[-as.numeric(as.character(l$indices))] 
  dat<- data.frame(c(betas_within, betas_without));colnames(dat) <- "data"; 
  dat$variable <- c(rep("Betas in age-sig", length(betas_within)), rep("Other betas", length(betas_without)))
  longdata = dat %>% dplyr::group_by(variable) %>% mutate(med = median(data))
  g <- ggplot(data = longdata, aes(y = data, x = variable, fill=med)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
  geom_point(aes(y = data, color = data), position = position_jitter(width = .15), size = .3, alpha = 0.5) +
  geom_boxplot(width = .1, guides = FALSE, outlier.shape = NA, alpha = 0.5) +
  #expand_limits(x = 5.25) +
  guides(fill = FALSE) +
  guides(color = FALSE) +
  # scale_color_manual(values=c("#4669dc","pink","purple")) +
  scale_color_distiller(palette="Blues", direction = 1) +
  scale_fill_distiller(palette="Blues", direction = 1) +
  #scale_color_gradient2(low="#FFFFFF",mid= "#FB6A4A", high="#67000D", midpoint= 0.475, aesthetics = c("color", "fill")) +
  coord_flip() + ggtitle(paste0("CT betas in areas showing \n pos age-associated FC remodeling at p <",pvalue))+
  theme_bw() +
  raincloud_theme
print(g)
  
print(t.test(betas_within, betas_without))
print(wilcox.test(betas_within, betas_without))
print(kruskal.test(data~variable, data = longdata))

plt <- ggplot() + theme_classic()+
  geom_density(aes(x=betas_within, ..count..),fill="purple", alpha=0.2) + 
  geom_density(aes(x=betas_without,..count..),fill="red", alpha=0.2)+ ggtitle(paste0("CT betas within areas showing \n pos age-associated FC remodeling at p <",pvalue)) +
  labs(y= "Values", x = "Beta")
print(plt)
}

```

## Average edge FC age effect within areas that show significant CT effects
```{r average beta for FC age effects within age-sig CT regions}
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/parcel_CT_age_n92.Rdata")
parcel_CT_pvals <- parcel_CT_pvals_fdr[,2] 
parcel_CT_betas<- parcel_CT_betas

#load back in edge age effects + SA betas
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/edgewise_age_effects_all_cov_n92.Rdata")
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400)
edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1] #take uncorrected p-values for now
#copy lower triangle to upper triangle
edge_age_pvals_mat[upper.tri(edge_age_pvals_mat)] <- t(edge_age_pvals_mat)[upper.tri(edge_age_pvals_mat)]
edge_age_betas_mat <- matrix(nrow = 400, ncol=400)
edge_age_betas_mat[lower.tri(edge_age_betas_mat, diag=FALSE)] <- edgewise_age_betas
edge_age_betas_mat[upper.tri( edge_age_betas_mat)] <- t(edge_age_betas_mat)[upper.tri( edge_age_betas_mat)]

pvalue=0.001
#links_to_show=edge_age_betas_mat<= 0;edge_age_pvals_mat[links_to_show==FALSE] <- NA
colmax=vector();rowmax=vector()
#indices <- which(ifelse(parcel_SA_pvals[,1]<0.01 & parcel_SA_betas > 0, 1, NA)==1)
indices <- which(parcel_CT_pvals_fdr[,2]<0.05, arr.ind = T) 
for (x in indices){
  b <- edge_age_betas_mat[x,][edge_age_pvals_mat[x,]<=0.001] 
  rowmax<-c(rowmax,b[!is.na(b)])
} 
#indices=which(colnames(edge_age_betas_mat)==set[2])
for (x in indices){
  b <- edge_age_betas_mat[,x][edge_age_pvals_mat[,x]<=0.001] 
  colmax<-c(colmax,b[!is.na(b)])
}
edge_effects_in_CT_areas <- c(colmax,rowmax)
distribution=list()
for (i in 1:1000){
colmax=vector();rowmax=vector()
notindices <- sample(which(!parcel_CT_pvals_fdr[,2]<0.05, arr.ind = T), size=length(indices))
#notindices <- sample(which(is.na(ifelse(!parcel_SA_pvals[,1]<0.01 & parcel_SA_betas > 0, 1, NA))), size=length(indices))
for (x in notindices){
  b <- edge_age_betas_mat[x,][edge_age_pvals_mat[x,]<=0.001] 
  rowmax<-c(rowmax,b[!is.na(b)])
}
#indices=which(colnames(edge_age_betas_mat)==set[2])
for (x in notindices){
  b <- edge_age_betas_mat[,x][edge_age_pvals_mat[,x]<=0.001] 
  colmax<-c(colmax,b[!is.na(b)])
}
edge_effects_in_nonCT_areas <- c(colmax,rowmax)
distribution[[i]] <- edge_effects_in_nonCT_areas
}
hist(unlist(distribution))
print(t.test(edge_effects_in_CT_areas, unlist(distribution)))
print(wilcox.test(edge_effects_in_CT_areas,unlist(distribution)))
ks.test(edge_effects_in_CT_areas, unlist(distribution))

plt <- ggplot() + theme_classic()+
  geom_density(aes(x=edge_effects_in_CT_areas, ..scaled.. ),fill="purple", alpha=0.2) + 
  geom_density(aes(x=unlist(distribution),  ..scaled.. ),fill="red", alpha=0.2)+ ggtitle(paste0("Betas of age edge effects within areas showing sig \n age effects on CT at corrected p < 0.05")) +
  labs(y= "Values", x = "# of age-sig edges per parcel") 
print(plt)

#Different approach
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400)
edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1];edge_age_pvals_mat[upper.tri(edge_age_pvals_mat)] <- t(edge_age_pvals_mat)[upper.tri(edge_age_pvals_mat)]
edge_age_betas_mat <- matrix(nrow = 400, ncol=400)
edge_age_betas_mat[lower.tri(edge_age_betas_mat, diag=FALSE)] <- edgewise_age_betas;edge_age_betas_mat[upper.tri( edge_age_betas_mat)] <- t(edge_age_betas_mat)[upper.tri( edge_age_betas_mat)]
#to do for only positive or only negative edges
links_to_show=edge_age_pvals_mat< 0.001 ;edge_age_betas_mat[links_to_show==FALSE] <- NA
#threshold for a given pval?
indices <- which(parcel_CT_pvals_fdr[,2]<0.05, arr.ind = T) #indices of edges that have age effects  below a pval
l <- data.frame(table(indices)) #for each parcel, how many age-significant edges does it have at a given pval thresh
edges_within <- c(edge_age_betas_mat[as.numeric(as.character(l$indices)),]) #get CT betas at each age-sig parcel
edges_without<- c(edge_age_betas_mat[-as.numeric(as.character(l$indices)),]) 
dat<- data.frame(c(edges_within, edges_without));colnames(dat) <- "data"; 
dat$variable <- c(rep("Edges in age-sig", length(edges_within)), rep("Other edges", length((edges_without))))
longdata = dat %>% dplyr::group_by(variable) %>% mutate(med = median(data, na.rm = T))
g <- ggplot(data = longdata, aes(y = data, x = variable, fill=med)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
  geom_point(aes(y = data, color = data), position = position_jitter(width = .15), size = .3, alpha = 0.5) +
  geom_boxplot(width = .1, guides = FALSE, outlier.shape = NA, alpha = 0.5) +
  #expand_limits(x = 5.25) +
  guides(fill = FALSE) +
  guides(color = FALSE) +
  # scale_color_manual(values=c("#4669dc","pink","purple")) +
  scale_color_distiller(palette="Blues", direction = 1) +
  scale_fill_distiller(palette="Blues", direction = 1) +
  #scale_color_gradient2(low="#FFFFFF",mid= "#FB6A4A", high="#67000D", midpoint= 0.475, aesthetics = c("color", "fill")) +
  coord_flip() + ggtitle(paste0("Edge FC betas in areas showing sig CT thinning \n thresh at p < 0.05"))+
  theme_bw() +
  raincloud_theme
print(g)
  
print(t.test(edges_within, edges_without))
print(wilcox.test(edges_within, edges_without))
kruskal.test(data~variable, data = longdata)
summary(lm(data~variable, data = longdata))
ks.test(edges_within, edges_without)

plt <- ggplot() + theme_classic()+
  geom_density(aes(x=edges_within, ..scaled..),fill="purple", alpha=0.2) + 
  geom_density(aes(x=edges_without,..scaled..),fill="red", alpha=0.2)+ ggtitle(paste0("Edge FC betas in areas showing sig CT thinning \n thresh at p < 0.05")) +
  labs(y= "Values", x = "Beta")
print(plt)
```

### Positive only
```{r average beta for pos FC age effects within age-sig CT regions}
#load data above
pvalue=0.001
links_to_show=edge_age_betas_mat>= 0;edge_age_pvals_mat[links_to_show==FALSE] <- NA
colmax=vector();rowmax=vector()
#indices <- which(ifelse(parcel_SA_pvals[,1]<0.01 & parcel_SA_betas > 0, 1, NA)==1)
indices <- which(parcel_CT_pvals_fdr[,2]<0.05, arr.ind = T) 
for (x in indices){
  b <- edge_age_betas_mat[x,][edge_age_pvals_mat[x,]<=0.001] 
  rowmax<-c(rowmax,b[!is.na(b)])
} 
#indices=which(colnames(edge_age_betas_mat)==set[2])
for (x in indices){
  b <- edge_age_betas_mat[,x][edge_age_pvals_mat[,x]<=0.001] 
  colmax<-c(colmax,b[!is.na(b)])
}
edge_effects_in_CT_areas <- c(colmax,rowmax)
distribution=list()
for (i in 1){
colmax=vector();rowmax=vector()
notindices <- sample(which(!parcel_CT_pvals_fdr[,2]<0.05, arr.ind = T), size=length(indices))
#notindices <- sample(which(is.na(ifelse(!parcel_SA_pvals[,1]<0.01 & parcel_SA_betas > 0, 1, NA))), size=length(indices))
for (x in notindices){
  b <- edge_age_betas_mat[x,][edge_age_pvals_mat[x,]<=0.001] 
  rowmax<-c(rowmax,b[!is.na(b)])
}
#indices=which(colnames(edge_age_betas_mat)==set[2])
for (x in notindices){
  b <- edge_age_betas_mat[,x][edge_age_pvals_mat[,x]<=0.001] 
  colmax<-c(colmax,b[!is.na(b)])
}
edge_effects_in_nonCT_areas <- c(colmax,rowmax)
distribution[[i]] <- edge_effects_in_nonCT_areas
}
hist(unlist(distribution)); hist(edge_effects_in_CT_areas)
print(t.test(edge_effects_in_CT_areas, edge_effects_in_nonCT_areas))
print(wilcox.test(edge_effects_in_CT_areas, edge_effects_in_nonCT_areas))
ks.test(edge_effects_in_CT_areas, ecdf(unlist(distribution)))
ecdf(unlist(distribution))

plt <- ggplot() + theme_classic()+
  geom_density(aes(x=edge_effects_in_CT_areas, ..scaled.. ),fill="purple", alpha=0.2) + 
  geom_density(aes(x=unlist(distribution),  ..scaled.. ),fill="red", alpha=0.2)+ ggtitle(paste0("Betas of age edge effects within areas showing sig \n age effects on CT at corrected p < 0.05")) +
  labs(y= "Values", x = "# of age-sig edges per parcel") 
print(plt)

pvalue=0.001
remove(dat);dat <- data.frame()
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400)
edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1];edge_age_pvals_mat[upper.tri(edge_age_pvals_mat)] <- t(edge_age_pvals_mat)[upper.tri(edge_age_pvals_mat)]
edge_age_betas_mat <- matrix(nrow = 400, ncol=400)
edge_age_betas_mat[lower.tri(edge_age_betas_mat, diag=FALSE)] <- edgewise_age_betas;edge_age_betas_mat[upper.tri( edge_age_betas_mat)] <- t(edge_age_betas_mat)[upper.tri( edge_age_betas_mat)]
#to do for only positive or only negative edges
links_to_show=edge_age_pvals_mat< 0.05 & edge_age_betas_mat > 0;edge_age_betas_mat[links_to_show==FALSE] <- NA
#threshold for a given pval?
indices <- which(parcel_CT_pvals_fdr[,2]<0.05 & parcel_CT_betas < 0, arr.ind = T) #indices of edges that have age effects  below a pval
l <- data.frame(table(indices)) #for each parcel, how many age-significant edges does it have at a given pval thresh
edges_within <- c(edge_age_betas_mat[as.numeric(as.character(l$indices)),]) #get CT betas at each age-sig parcel
edges_without<- c(edge_age_betas_mat[-as.numeric(as.character(l$indices)),]) 
dat<- data.frame(c(edges_within, edges_without));colnames(dat) <- "data"; 
dat$variable <- c(rep("Edges in age-sig", length(edges_within)), rep("Other edges", length((edges_without))))
longdata = dat %>% dplyr::group_by(variable) %>% mutate(med = median(data, na.rm = T))
g <- ggplot(data = longdata, aes(y = data, x = variable, fill=med)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
  geom_point(aes(y = data, color = data), position = position_jitter(width = .15), size = .3, alpha = 0.5) +
  geom_boxplot(width = .1, guides = FALSE, outlier.shape = NA, alpha = 0.5) +
  #expand_limits(x = 5.25) +
  guides(fill = FALSE) +
  guides(color = FALSE) +
  # scale_color_manual(values=c("#4669dc","pink","purple")) +
  scale_color_distiller(palette="Blues", direction = 1) +
  scale_fill_distiller(palette="Blues", direction = 1) +
  #scale_color_gradient2(low="#FFFFFF",mid= "#FB6A4A", high="#67000D", midpoint= 0.475, aesthetics = c("color", "fill")) +
  coord_flip() + ggtitle(paste0("Edge FC betas in areas showing sig CT thinning \n thresh at p < 0.05"))+
  theme_bw() +
  raincloud_theme
print(g)
  
print(t.test(edges_within, edges_without))
print(wilcox.test(edges_within, edges_without))
kruskal.test(data~variable, data = longdata)
summary(lm(data~variable, data = longdata))

plt <- ggplot() + theme_classic()+
  geom_density(aes(x=edges_within, ..scaled..),fill="purple", alpha=0.2) + 
  geom_density(aes(x=edges_without,..scaled..),fill="red", alpha=0.2)+ ggtitle(paste0("Edge FC betas in areas showing sig CT thinning \n thresh at p < 0.05")) +
  labs(y= "Values", x = "Beta")
print(plt)
```

### Negative only
```{r average beta for neg FC age effects within age-sig CT regions}
#load data above
pvalue=0.001
links_to_show=edge_age_betas_mat<= 0;edge_age_pvals_mat[links_to_show==FALSE] <- NA
colmax=vector();rowmax=vector()
#indices <- which(ifelse(parcel_SA_pvals[,1]<0.01 & parcel_SA_betas > 0, 1, NA)==1)
indices <- which(parcel_CT_pvals_fdr[,2]<0.05, arr.ind = T) 
for (x in indices){
  b <- edge_age_betas_mat[x,][edge_age_pvals_mat[x,]<=0.05] 
  rowmax<-c(rowmax,b[!is.na(b)])
} 
#indices=which(colnames(edge_age_betas_mat)==set[2])
for (x in indices){
  b <- edge_age_betas_mat[,x][edge_age_pvals_mat[,x]<=0.05] 
  colmax<-c(colmax,b[!is.na(b)])
}
edge_effects_in_CT_areas <- c(colmax,rowmax)
distribution=list()
for (i in 1:1000){
colmax=vector();rowmax=vector()
notindices <- sample(which(!parcel_CT_pvals_fdr[,2]<0.05, arr.ind = T), size=length(indices))
#notindices <- sample(which(is.na(ifelse(!parcel_SA_pvals[,1]<0.01 & parcel_SA_betas > 0, 1, NA))), size=length(indices))
for (x in notindices){
  b <- edge_age_betas_mat[x,][edge_age_pvals_mat[x,]<=0.05] 
  rowmax<-c(rowmax,b[!is.na(b)])
}
#indices=which(colnames(edge_age_betas_mat)==set[2])
for (x in notindices){
  b <- edge_age_betas_mat[,x][edge_age_pvals_mat[,x]<=0.05] 
  colmax<-c(colmax,b[!is.na(b)])
}
edge_effects_in_nonCT_areas <- c(colmax,rowmax)
distribution[[i]] <- edge_effects_in_nonCT_areas
}
hist(unlist(distribution)); hist(edge_effects_in_CT_areas)
print(t.test(edge_effects_in_CT_areas, edge_effects_in_nonCT_areas))
print(wilcox.test(edge_effects_in_CT_areas, edge_effects_in_nonCT_areas))
ks.test(edge_effects_in_CT_areas, unlist(distribution))
ecdf(unlist(distribution))

plt <- ggplot() + theme_classic()+
  geom_density(aes(x=edge_effects_in_CT_areas, ..scaled.. ),fill="purple", alpha=0.2) + 
  geom_density(aes(x=unlist(distribution),  ..scaled.. ),fill="red", alpha=0.2)+ ggtitle(paste0("Betas of age edge effects within areas showing sig \n age effects on CT at corrected p < 0.05")) +
  labs(y= "Values", x = "# of age-sig edges per parcel") 
print(plt)

pvalue=0.001
remove(dat);dat <- data.frame()
edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1]; edge_age_pvals_mat <- t(edge_age_pvals_mat)#copy lower triangle to upper triangle
edge_age_betas_mat[lower.tri(edge_age_betas_mat, diag=FALSE)] <- edgewise_age_betas; edge_age_betas_mat <- t(edge_age_betas_mat)#copy lower triangle to upper triangle
#to do for only positive or only negative edges
links_to_show=edge_age_pvals_mat< 0.05 & edge_age_betas_mat < 0;edge_age_betas_mat[links_to_show==FALSE] <- NA
#threshold for a given pval?
indices <- which(parcel_CT_pvals_fdr[,2]<0.05, arr.ind = T) #indices of edges that have age effects  below a pval
l <- data.frame(table(indices)) #for each parcel, how many age-significant edges does it have at a given pval thresh
edges_within <- c(edge_age_betas_mat[as.numeric(as.character(l$indices)),]) #get CT betas at each age-sig parcel
edges_without<- c(edge_age_betas_mat[-as.numeric(as.character(l$indices)),]) 
dat<- data.frame(c(edges_within, edges_without));colnames(dat) <- "data"; 
dat$variable <- c(rep("Edges in age-sig", length(edges_within)), rep("Other edges", length((edges_without))))
longdata = dat %>% dplyr::group_by(variable) %>% mutate(med = median(data, na.rm = T))
g <- ggplot(data = longdata, aes(y = data, x = variable, fill=med)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
  geom_point(aes(y = data, color = data), position = position_jitter(width = .15), size = .3, alpha = 0.5) +
  geom_boxplot(width = .1, guides = FALSE, outlier.shape = NA, alpha = 0.5) +
  #expand_limits(x = 5.25) +
  guides(fill = FALSE) +
  guides(color = FALSE) +
  # scale_color_manual(values=c("#4669dc","pink","purple")) +
  scale_color_distiller(palette="Blues", direction = 1) +
  scale_fill_distiller(palette="Blues", direction = 1) +
  #scale_color_gradient2(low="#FFFFFF",mid= "#FB6A4A", high="#67000D", midpoint= 0.475, aesthetics = c("color", "fill")) +
  coord_flip() + ggtitle(paste0("Edge FC betas in areas showing sig CT thinning \n thresh at p < 0.05"))+
  theme_bw() +
  raincloud_theme
print(g)
  
print(t.test(edges_within, edges_without))
print(wilcox.test(edges_within, edges_without))
kruskal.test(data~variable, data = longdata)
summary(lm(data~variable, data = longdata))

plt <- ggplot() + theme_classic()+
  geom_density(aes(x=edges_within, ..scaled..),fill="purple", alpha=0.2) + 
  geom_density(aes(x=edges_without,..scaled..),fill="red", alpha=0.2)+ ggtitle(paste0("Edge FC betas in areas showing sig CT thinning \n thresh at p < 0.05")) +
  labs(y= "Values", x = "Beta")
print(plt)
```

## Average edge FC age effect within areas that show significant CT effects by Freesurfer
```{r average beta for FC age effects within age-sig CT regions Freesurfer}
#read in centroids of the Schaefer400 parcels
lh_centroids <- as.matrix(read.csv("~/Documents/tools/parcellations/lh.Schaefer400_7Nets_fsaverage6.centroids.csv", header = F));rh_centroids <- as.matrix(read.csv("~/Documents/tools/parcellations/rh.Schaefer400_7Nets_fsaverage6.centroids.csv", header = F))
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/rotations_schaefer400_fsaverage6_10000x.Rdata")
#SHOULD BE MASKING OUT MEDIAL WALL? Assuming that is first centroid for each
lh_centroids <- lh_centroids[-1,];rh_centroids <- rh_centroids[-1,];
#load age on CT from FS
lh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/lh_thickness_agesext1rating_n89/lh-Avg-thickness-age_scan-Cor/cache.th23.abs.sig.masked.mgh") #voxel-wise corrected?
#load schaefer parcellation at fsaverage res and average by parcel
detach("package:plyr", unload=TRUE)
schaefer_lh <-subject.annot(subjects_dir = subjects_dir,subject_id =subject_id, hemi="lh", atlas = atlas)
d <- data.frame(lh, schaefer_lh$label_names) %>% rename(schaefer_atlas_region_names_lh=schaefer_lh.label_names) %>% group_by(schaefer_atlas_region_names_lh) %>% summarise(mean=mean(lh));
lh_parcels_CT <- left_join(data.frame(schaefer_atlas_region_names_lh),d, by= "schaefer_atlas_region_names_lh")
schaefer_rh <-subject.annot(subjects_dir = subjects_dir,subject_id =subject_id, hemi="rh", atlas = atlas)
rh <- read.fs.mgh("/cbica/projects/cbpd_main_data/CBPD_bids/derivatives/freesurfer_edits_t1/qdec/rh_thickness_agesext1rating_n89/rh-Avg-thickness-age_scan-Cor/cache.th23.abs.sig.masked.mgh")
d <- data.frame(rh, schaefer_rh$label_names) %>% rename(schaefer_atlas_region_names_rh=schaefer_rh.label_names) %>% group_by(schaefer_atlas_region_names_rh) %>% summarise(mean=mean(rh));rh_parcels_CT <- left_join(data.frame(schaefer_atlas_region_names_rh),d, by= "schaefer_atlas_region_names_rh")
CT_vector=c(lh_parcels_CT$mean,rh_parcels_CT$mean)[-c(1,202)]
#load back in edge age effects
load("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/edgewise_age_effects_all_cov_n92.Rdata")
#Different approach
edge_age_pvals_mat <- matrix(nrow = 400, ncol=400)
edge_age_pvals_mat[lower.tri(edge_age_pvals_mat, diag=FALSE)] <- edgewise_age_pvals_fdr[,1];edge_age_pvals_mat[upper.tri(edge_age_pvals_mat)] <- t(edge_age_pvals_mat)[upper.tri(edge_age_pvals_mat)]
edge_age_betas_mat <- matrix(nrow = 400, ncol=400)
edge_age_betas_mat[lower.tri(edge_age_betas_mat, diag=FALSE)] <- edgewise_age_betas;edge_age_betas_mat[upper.tri( edge_age_betas_mat)] <- t(edge_age_betas_mat)[upper.tri( edge_age_betas_mat)]
#to do for only positive or only negative edges
#links_to_show=edge_age_pvals_mat< 0.001 ;edge_age_betas_mat[links_to_show==FALSE] <- NA

indices <- which(CT_vector!=0, arr.ind = T) #indices of edges that have age effects  below a pval
l <- data.frame(table(indices)) #for each parcel, how many age-significant edges does it have at a given pval thresh
edges_within <- c(edge_age_betas_mat[as.numeric(as.character(l$indices)),]) #get CT betas at each age-sig parcel
edges_without<- c(edge_age_betas_mat[-as.numeric(as.character(l$indices)),]) 
dat<- data.frame(c(edges_within, edges_without));colnames(dat) <- "data"; 
dat$variable <- c(rep("Edges in age-sig", length(edges_within)), rep("Other edges", length((edges_without))))
longdata = dat %>% dplyr::group_by(variable) %>% mutate(med = median(data, na.rm = T))
g <- ggplot(data = longdata, aes(y = data, x = variable, fill=med)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
  geom_point(aes(y = data, color = data), position = position_jitter(width = .15), size = .3, alpha = 0.5) +
  geom_boxplot(width = .1, guides = FALSE, outlier.shape = NA, alpha = 0.5) +
  #expand_limits(x = 5.25) +
  guides(fill = FALSE) +
  guides(color = FALSE) +
  # scale_color_manual(values=c("#4669dc","pink","purple")) +
  scale_color_distiller(palette="Blues", direction = 1) +
  scale_fill_distiller(palette="Blues", direction = 1) +
  #scale_color_gradient2(low="#FFFFFF",mid= "#FB6A4A", high="#67000D", midpoint= 0.475, aesthetics = c("color", "fill")) +
  coord_flip() + ggtitle(paste0("Edge FC betas in areas showing sig CT thinning \n thresh at p < 0.05"))+
  theme_bw() +
  raincloud_theme
print(g)
  
print(t.test(edges_within, edges_without))
wilcox.test(edges_within, edges_without)
kruskal.test(data~variable, data = longdata)
summary(lm(data~variable, data = longdata))
ks.test(edges_within, edges_without)

plt <- ggplot() + theme_classic()+
  geom_density(aes(x=edges_within, ..scaled..),fill="purple", alpha=0.2) + 
  geom_density(aes(x=edges_without,..scaled..),fill="red", alpha=0.2)+ ggtitle(paste0("Edge FC betas in areas showing sig CT thinning \n thresh at p < 0.05")) +
  labs(y= "Values", x = "Beta")
print(plt)
```

## Structure-function coupling: CT

Look at whether the strength at a node is correlated with CT at a node. Examine whether the strength of coupling increases or decreases with age, where there are significant increases or decreases in coupling. Could also look at the whole matrix of FC predicted by CT (or SA)?

```{structure-function coupling-CT}
#get CT
n92_parcel_CT_only <- n92_parcel_CT_data %>%ungroup %>%  select(X7Networks_LH_Vis_1:X7Networks_RH_Default_pCunPCC_9) %>% as.matrix(.)
#get edge matrix, make average nodal strength
n92_all_edges<- readRDS("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/n92_all_edges.RData");n92_all_edges <- n92_all_edges[,-1]

#get nodal stregth for each node for each subject
n92_nodal_strength <- apply(n92_all_edges,1, function (x){
  goback <- matrix(nrow = 400, ncol=400)
goback[lower.tri(goback, diag=FALSE)] <-x
goback[upper.tri(goback)] <- t(goback)[upper.tri(goback)]
return(colMeans(goback, na.rm = T))
})
n92_nodal_strength <- t(n92_nodal_strength)

#for each subject, check correlation between the two
str_func_cor_subj <- vector()
str_func_spear_subj <- vector()
for (i in 1:dim(main_unique)[1]){
  str_func_cor_subj[i] <- cor(n92_parcel_CT_only[i,],n92_nodal_strength[i,])
  str_func_spear_subj[i] <- cor(n92_parcel_CT_only[i,],n92_nodal_strength[i,], method = "spearman")
}
#add to main data frame
str_func_dat <- data.frame(main_unique,str_func_cor_subj, str_func_spear_subj)

#plot the average structure-function coupling across subjects
parcel_wise_str_func <- vector()
for (i in 1:400){
  temp <- data.frame(n92_parcel_CT_only[,i],n92_nodal_strength[,i],n92_parcel_CT_data$age_scan) %>% na.omit()
  parcel_wise_str_func[i] <- ppcor::pcor.test(temp$n92_parcel_CT_only...i., temp$n92_nodal_strength...i., temp$n92_parcel_CT_data.age_scan)$estimate
}
#vect <- colMeans(n92_parcel_CT_only, na.rm = T)
num_of_sig_age_edges_lh=as.list(setNames(c(NA,parcel_wise_str_func[1:200]), schaefer_atlas_region_names_lh)) #this has the medial wall in it.
num_of_sig_age_edges_rh=as.list(setNames(c(NA,parcel_wise_str_func[201:400]), schaefer_atlas_region_names_rh))
#colormap
colFn_diverging =  colorRampPalette((RColorBrewer::brewer.pal(9, name="RdBu"), "darkblue"));makecmap_options=list('colFn'=colFn_diverging)
rglactions=list("snapshot_png"=paste0(output_image_directory,"average_fc-ct_coupling_controlled_age.png"),'shift_hemis_apart'=TRUE)
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  num_of_sig_age_edges_lh, 
                             num_of_sig_age_edges_rh, makecmap_options = makecmap_options, "inflated", views="t9", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)

#check for an age effect on the whole-brain average
summary(lm(str_func_spear_subj~age_scan+male+t1_rating_avg+fd_mean_avg+avgweight+totalSizet, data=str_func_dat))
#~age_scan+male+fd_mean_avg+avgweight+totalSizet
visreg(lm(str_func_cor_subj~age_scan+male+t1_rating_avg, data=str_func_dat), main= "CT-FC coupling")
exactRLRT(gamm(str_func_cor_subj~s(age_scan)+male+t1_rating_avg+fd_mean_avg+avgweight+totalSizet, data=str_func_dat, method = "REML")$lme)
visreg(gam(str_func_cor_subj~s(age_scan, k=4)+male+t1_rating_avg+fd_mean_avg+avgweight+totalSizet, data = main_unique, method = "REML"), main="CT-FC coupling")

```

```{structure-function coupling-SA}
#get CT
n92_parcel_SA_only <- n92_parcel_SA_data %>%ungroup %>%  select(lh_2_area:rh_201_area) %>% select(-rh_1_area)%>% as.matrix(.)
#get edge matrix, make average nodal strength
n92_all_edges<- readRDS("~/Documents/projects/in_progress/within_between_network_conn_CBPD/data/imageData/gsr_spkreg_fd0.5dvars1.75_drpvls/n92_all_edges.RData");n92_all_edges <- n92_all_edges[,-1]

#get nodal stregth for each node for each subject
n92_nodal_strength <- apply(n92_all_edges,1, function (x){
  goback <- matrix(nrow = 400, ncol=400)
goback[lower.tri(goback, diag=FALSE)] <-x
goback[upper.tri(goback)] <- t(goback)[upper.tri(goback)]
return(colMeans(goback, na.rm = T))
})
n92_nodal_strength <- t(n92_nodal_strength)

#for each subject, check correlation between the two
str_func_cor_subj <- vector()
str_func_spear_subj <- vector()
for (i in 1:dim(main_unique)[1]){
  str_func_cor_subj[i] <- cor(n92_parcel_SA_only[i,],n92_nodal_strength[i,])
  str_func_spear_subj[i] <- cor(n92_parcel_SA_only[i,],n92_nodal_strength[i,], method = "spearman")
}
#add to main data frame
str_func_dat <- data.frame(main_unique,str_func_cor_subj, str_func_spear_subj)

#plot the average structure-function coupling across subjects
parcel_wise_str_func <- vector()
for (i in 1:400){
  parcel_wise_str_func[i] <- cor(n92_parcel_SA_only[,i],n92_nodal_strength[,i], use = "pairwise.complete.obs")
}
#vect <- colMeans(n92_parcel_CT_only, na.rm = T)
num_of_sig_age_edges_lh=as.list(setNames(c(NA,parcel_wise_str_func[1:200]), schaefer_atlas_region_names_lh)) #this has the medial wall in it.
num_of_sig_age_edges_rh=as.list(setNames(c(NA,parcel_wise_str_func[201:400]), schaefer_atlas_region_names_rh))
#colormap
colFn_diverging =  colorRampPalette((RColorBrewer::brewer.pal(9, name="RdBu")));makecmap_options=list('colFn'=colFn_diverging)
rglactions=list("snapshot_png"=paste0(output_image_directory,"average_SA-FC_coupling.png"),'shift_hemis_apart'=TRUE)
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  num_of_sig_age_edges_lh, 
                             num_of_sig_age_edges_rh, makecmap_options = makecmap_options, "inflated", views="t9", draw_colorbar = T, rgloptions = rgloptions, rglactions = rglactions)

#check for an age effect on the whole-brain average
summary(lm(str_func_cor_subj~age_scan+male+t1_rating_avg+fd_mean_avg+avgweight+totalSizet, data=str_func_dat))
#~age_scan+male+fd_mean_avg+avgweight+totalSizet
visreg(lm(str_func_cor_subj~age_scan+male+t1_rating_avg+fd_mean_avg+avgweight+totalSizet, data=str_func_dat), main= "SA-FC coupling")
exactRLRT(gamm(str_func_cor_subj~s(age_scan)+male+t1_rating_avg+fd_mean_avg+avgweight+totalSizet, data=str_func_dat, method = "REML")$lme)
visreg(gam(str_func_cor_subj~s(age_scan, k=4)+male+t1_rating_avg+fd_mean_avg+avgweight+totalSizet, data = main_unique, method = "REML"), main="CT-FC coupling")

```

```{nodal strength age effects}
#add to main data frame
n92_nodal_strength_data <- data.frame(main_unique,n92_nodal_strength)

subjectwise_metric <- data.frame(n92_nodal_strength,rowMeans(n92_nodal_strength, na.rm = T)) %>% rename(global_mean_metric=rowMeans.n92_nodal_strength..na.rm...T.)
hist(subjectwise_metric$global_mean_metric)
#take out the 2 outliers
#subjectwise_metric <- subjectwise_metric %>% filter(.,global_mean_metric>1)
subjectwise_metric$ID <- main_unique$ID
subjectwise_metric<- left_join(main_unique,subjectwise_metric, by= "ID")
summary(lm(global_mean_metric~age_scan+male+fd_mean_avg+totalSizet, data=subjectwise_metric))
visreg(lm(global_mean_metric~age_scan+male+fd_mean_avg+avgweight+totalSizet, data=subjectwise_metric))
exactRLRT(gamm(global_mean_metric~s(age_scan)+male+fd_mean_avg+avgweight+totalSizet, data=subjectwise_metric, method = "REML")$lme)
visreg(gam(global_mean_metric~s(age_scan)+male+fd_mean_avg+avgweight+totalSizet, data=subjectwise_metric, method = "REML"))
# #take out rows with NAs/Inf at the parcel level
# subjectwise_metric %>% ungroup() %>%  select(V1:V100) %>% summary() mutate(global_mean_metric=rowMeans(as.matrix(.))) %>%  select(global_mean_metric)
# mutate(global_mean_metric=rowMedians(as.matrix(.),na.rm=T))
#parcelwise
parcel_sd_pvals<- lapply(names(subjectwise_metric[,1646:2045]), function(x) { summary(lm(as.formula(paste0(x,"~age_scan+male+fd_mean_avg+avgweight+totalSizet")), data=subjectwise_metric))$coef[2,4]})
parcel_sd_pvals <- unlist(parcel_sd_pvals)
parcel_sd_pvals_fdr <- cbind(parcel_sd_pvals,p.adjust(parcel_sd_pvals,method = "fdr"))
#get age betas
parcel_sd_betas<- lapply(names(subjectwise_metric[,1646:2045]), function(x) { lm.beta(lm(as.formula(paste0(x,"~age_scan+male+fd_mean_avg+avgweight+totalSizet")), data=subjectwise_metric))$standardized.coefficients[[2]]})
parcel_sd_betas <- unlist(parcel_sd_betas)
name="parcel_age_node_strength_pvals"
to_plot=parcel_sd_pvals_fdr[,1] #Change this to plot different things
to_plot=ifelse(parcel_sd_pvals_fdr[,2] <0.05,parcel_sd_betas,NA)

lh=as.list(setNames(c(NA,to_plot[1:200]), schaefer_atlas_region_names_lh)) #this has the medial wall in it.
rh=as.list(setNames(c(NA,to_plot[201:400]), schaefer_atlas_region_names_rh))
#colormap
#colFn_diverging = colorRampPalette(rev(c("white","white","pink","red")));makecmap_options=list('colFn'=colFn_diverging)
colFn_diverging = colorRampPalette(rev(RColorBrewer::brewer.pal(9, name="RdBu")));makecmap_options=list('colFn'=colFn_diverging, symm=T)
rglactions=list("snapshot_png"=paste0(output_image_directory,name,".png"), 'shift_hemis_apart'=TRUE)
vis.region.values.on.subject(subjects_dir, 'fsaverage6', 'Schaefer2018_400Parcels_7Networks_order',  lh, 
                             rh, makecmap_options = makecmap_options, "inflated", views="t9", draw_colorbar = T, rgloptions = rgloptions, rglactions = NULL)

```